\begin{glossarymc}[Cambridge 4]
    \begin{test}{TEST 1}
    \noindent
    \textbf{Part 1. Friends}
	
	\begin{qa}{Are your friends mostly your age or different ages? [Why?]}
	It depends. As I work in a \textbf{mixed-age} environment, I often \textbf{strike up a friendship} with those younger or older than I am. I also have some childhood friends and \textbf{classmates}. However, it's a long time since we last \textbf{palled around} as we are busy \textbf{making ends meet}.
	\end{qa}

	\begin{qa}{Do you usually see your friends during the week or at weekends? [Why?]}
	I often socialize with friends on weekdays only. In my mind, the weekend is \textbf{quality time} for my family so I seldom see any friends at weekends. They should also spend this precious amount of time on their own family to have a break from the \textbf{hustle and bustle} of their work as well as I do.
	\end{qa}

	\begin{qa}{The last time you saw your friends, what did you do together?}
	Well, I can \textbf{vividly recall} the last time I \textbf{hung out with} friends. After having \textbf{splurged on a lavish meal}, we went to the cinema to watch ``Avengers: Endgame''. We are kinda \textbf{die-hard Marvel fans} so this film was \textbf{on the top of our list} to have a look at.
	\end{qa}

	\begin{qa}{In what ways are your friends important to you?}
	Of course, my family \textbf{ranks first in the order of importance}, followed by friends. As I'm an introvert, I am quite \textbf{choosy about forging} any relationship with anyone. ``\textbf{A friend in need is a friend indeed}'' so finding an intimate friend who can \textbf{lend a sympathetic ear to me} when I'm \textbf{in hot water} is essential. There's no need to shape a relationship with too many friends, many of whom may be \textbf{fair-weather ones}.
	\end{qa}

	
        \begin{VocabExplain}[Part 1]
			\begin{ExplainCard}{mixed-age}[adj][B2]
			  \EN{Including people from different age groups (e.g., in one class/team).}
			  \SY{multi-age; mixed-generation}
			  \VI{Gồm nhiều lứa tuổi (cùng sinh hoạt/học tập).}
			  \EX{Our club is a \textit{mixed-age} group from first-years to alumni.}
			  \EX{The school pilots \textit{mixed-age} classes to promote peer learning.}
			  \CO{mixed-age class/group/team; a mixed-age workplace}
			\end{ExplainCard}

			\begin{ExplainCard}{strike up (a friendship)}[phr.v][B2]
			  \EN{To begin a friendly relationship, often with someone you have just met.}
			  \SY{start; initiate; form}
			  \VI{Bắt đầu/kết tình bạn.}
			  \EX{We \textit{struck up a friendship} on orientation day.}
			  \EX{Researchers \textit{struck up} rapport with participants before interviews.}
			  \CO{strike up a friendship/conversation/relationship; strike up rapport}
			\end{ExplainCard}

			\begin{ExplainCard}{pal around (with sb)}[phr.v][B2]
			  \EN{To spend a lot of time with someone as a friend.}
			  \SY{hang out (with); chum around (with)}
			  \VI{Đi chơi, qua lại thân thiết với ai.}
			  \EX{He's been \textit{palling around with} the new neighbors.}
			  \EX{Teen cohorts often \textit{pal around} with peers sharing hobbies.}
			  \CO{pal around with friends/classmates/colleagues}
			\end{ExplainCard}

			\begin{ExplainCard}{make ends meet}[idiom][B2]
			  \EN{To have just enough money to cover basic expenses.}
			  \SY{get by; scrape by}
			  \VI{Kiếm đủ tiền để trang trải cuộc sống.}
			  \EX{Many interns take side gigs to \textit{make ends meet}.}
			  \EX{Rising rents make it harder for low-income families to \textit{make ends meet}.}
			  \CO{struggle/barely manage to make ends meet}
			\end{ExplainCard}

			\begin{ExplainCard}{quality time}[phrase][B2]
			  \EN{Time spent giving loved ones full attention.}
			  \SY{dedicated time; meaningful time}
			  \VI{Thời gian chất lượng dành trọn cho gia đình/người thân.}
			  \EX{Sunday is \textit{quality time} with my parents.}
			  \EX{Employees are urged to carve out \textit{quality time} for childcare.}
			  \CO{spend quality time with; quality family time; carve out quality time}
			\end{ExplainCard}

			\begin{ExplainCard}{the hustle and bustle (of)}[idiom][B2]
			  \EN{Busy, noisy, frenetic activity, esp.\ of city life.}
			  \SY{commotion; bustle}
			  \VI{Sự náo nhiệt, tất bật (đặc biệt nơi đô thị).}
			  \EX{A short ride takes you away from \textit{the hustle and bustle} of downtown.}
			  \EX{Tourists often seek retreats from \textit{the hustle and bustle of} urban centers.}
			  \CO{the hustle and bustle of city life/streets/markets}
			\end{ExplainCard}

			\begin{ExplainCard}{vividly}[adv][B2]
			  \EN{In a way that is clear and detailed in the mind.}
			  \SY{clearly; distinctly}
			  \VI{Một cách sinh động, rõ nét.}
			  \EX{I \textit{vividly} remember our first meetup.}
			  \EX{The memoir \textit{vividly} depicts post-war Hanoi.}
			  \CO{vividly remember/recall/describe/depict}
			\end{ExplainCard}

			\begin{ExplainCard}{hang out (with)}[phr.v][B1]
			  \EN{To spend time relaxing or socializing.}
			  \SY{spend time; socialize}
			  \VI{Đi chơi, tụ tập.}
			  \EX{We \textit{hang out with} classmates after finals.}
			  \EX{Adolescents frequently \textit{hang out} at public spaces after school.}
			  \CO{hang out with friends; hang out at a café/park}
			\end{ExplainCard}

			\begin{ExplainCard}{splurge on}[phr.v][C1]
			  \EN{To spend a lot of money on something nonessential or luxurious.}
			  \SY{indulge in; splash out on}
			  \VI{Vung tiền/tiêu hoang vào.}
			  \EX{They \textit{splurged on} a tasting menu to celebrate.}
			  \EX{Consumers tend to \textit{splurge on} electronics during holiday sales.}
			  \CO{splurge on a meal/gadgets/clothes; an occasional splurge}
			\end{ExplainCard}

			\begin{ExplainCard}{lavish}[adj][C1]
			  \EN{Large in amount and impressively rich or expensive.}
			  \SY{luxurious; opulent; extravagant}
			  \VI{Xa hoa, tốn kém.}
			  \EX{They threw a \textit{lavish} party after graduation.}
			  \EX{A \textit{lavish} budget was allocated for the gala.}
			  \CO{a lavish meal/party/gift; lavish spending/lifestyle}
			\end{ExplainCard}

			\begin{ExplainCard}{die-hard fan}[n][C1]
			  \EN{An extremely loyal and enthusiastic supporter.}
			  \SY{hardcore fan; devoted fan}
			  \VI{Người hâm mộ cuồng nhiệt.}
			  \EX{She's a \textit{die-hard fan} of Marvel.}
			  \EX{\textit{Die-hard fans} kept attending despite poor results.}
			  \CO{a die-hard fan of; die-hard supporter/base}
			\end{ExplainCard}

			\begin{ExplainCard}{be at/on the top of sb's list}[idiom][B2]
			  \EN{To be someone's highest priority or first choice.}
			  \SY{top the list; be a top priority}
			  \VI{Là ưu tiên hàng đầu.}
			  \EX{Kyoto is \textit{at the top of my list}.}
			  \EX{Safety \textit{tops the list} of project priorities.}
			  \CO{be at the top of one's list; top the list of priorities/places}
			\end{ExplainCard}

			\begin{ExplainCard}{rank first in the order of importance}[phrase][C1]
			  \EN{To be considered the most important among several factors.}
			  \SY{take precedence; be paramount}
			  \VI{Đứng đầu về mức độ quan trọng.}
			  \EX{For me, family \textit{ranks first in the order of importance}.}
			  \EX{In the budget, safety \textit{ranks first}.}
			  \CO{rank first/second; rank high/low; rank first in importance}
			\end{ExplainCard}

			\begin{ExplainCard}{choosy}[adj][C1]
			  \EN{Very careful in choosing; hard to please.}
			  \SY{picky; selective; fastidious}
			  \VI{Kén chọn, khó chiều.}
			  \EX{He's \textit{choosy} about who he hangs out with.}
			  \EX{Recruiters are increasingly \textit{choosy} in a tight market.}
			  \CO{choosy about food/jobs/friends; a choosy customer}
			\end{ExplainCard}

			\begin{ExplainCard}{forge (a relationship)}[v][C1]
			  \EN{To create or develop something strong and lasting through effort.}
			  \SY{build; establish; cultivate}
			  \VI{Gây dựng/vun đắp (mối quan hệ/liên minh).}
			  \EX{Camp helped us \textit{forge} trust quickly.}
			  \EX{Universities \textit{forge} partnerships with industry.}
			  \CO{forge a friendship/relationship/alliance/consensus; forge closer ties}
			\end{ExplainCard}

			\begin{ExplainCard}{A friend in need is a friend indeed}[proverb][B2]
			  \EN{A true friend helps when you are in trouble.}
			  \SY{true friends show up in hard times}
			  \VI{Hoạn nạn mới biết bạn hiền.}
			  \EX{She stayed and helped—\textit{a friend in need is a friend indeed}.}
			  \EX{The crisis proved that \textit{a friend in need is a friend indeed}.}
			  \CO{prove (that) a friend in need is a friend indeed}
			\end{ExplainCard}

			\begin{ExplainCard}{lend a sympathetic ear (to)}[idiom][C1]
			  \EN{To listen to someone with understanding and compassion.}
			  \SY{listen compassionately; be a sounding board}
			  \VI{Lắng nghe và thấu cảm.}
			  \EX{My mentor \textit{lent a sympathetic ear} when I was stressed.}
			  \EX{Counselors \textit{offer a sympathetic ear} to students in distress.}
			  \CO{lend/offer a sympathetic ear to; find a sympathetic ear}
			\end{ExplainCard}

			\begin{ExplainCard}{in hot water}[idiom][B2]
			  \EN{In trouble, especially with authority or a superior.}
			  \SY{in trouble; in a bind}
			  \VI{Gặp rắc rối.}
			  \EX{I'm \textit{in hot water} for missing the deadline.}
			  \EX{The firm landed \textit{in hot water} over safety breaches.}
			  \CO{be/get/land in hot water (with); end up in hot water}
			\end{ExplainCard}

			\begin{ExplainCard}{fair-weather friend}[n][C1]
			  \EN{A person who is around only when things go well.}
			  \SY{fickle friend; inconstant companion}
			  \VI{Bạn đểu—chỉ chơi khi thuận lợi.}
			  \EX{When I got sick, some \textit{fair-weather friends} vanished.}
			  \EX{True loyalty is rare; many prove \textit{fair-weather friends}.}
			  \CO{prove (to be) a fair-weather friend; have only fair-weather friends}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
		\begin{qa}{Describe an interesting historic place}
		You should say:\\
		\textbullet\ What it is\\
		\textbullet\ Where it is located\\
		\textbullet\ What you can see there now\\
		\textbullet\ and explain why this place is interesting
		
	Even though Vietnam has loads of impressive historical places, I would like to recommend one of the most popular attractions in Hanoi. It is Hanoi Opera Theater. There is a rumor among tourists that it is a \textbf{must-visit place} when they pay a visit to Hanoi. Speaking of its location, it is situated \textbf{right in the heart of} Hanoi and surrounded by some ancient high-rise buildings. It only takes me 10 minutes to reach there by motorbike. \textbf{To the best of my knowledge}, it was also designed by one of the legendary figures in French architecture industry. It was erected by the French colonial administration between 1901 and 1911. The location chosen was a site in a \textbf{run-down district} which was ignored at that time. \textbf{From the top of my head}, all building materials were originally imported from France so it has certainly \textbf{stood the test of time}. Although it has undergone \textbf{refurbishment}, the architecture still remains \textbf{intact}. As people approach the entrance, they have to cross over a small bridge. People have a \textbf{sense of suspense} when they see the building from a distance, and then a close-up, and the initial impression is the shape of the building like a box. The auditorium seats 1500 people and the floor is supported by ten massive pads constructed from rubber, so they are able to absorb any vibrations from outside. The walls are made of several layers of honey-colored wood and curved to improve the acoustic properties of the auditorium and \textbf{amplify} the sound. The reason why I think this place is interesting is that it is one of the \textbf{architectural landmarks} of Hanoi. More importantly, it is the \textbf{venue} for important events such as film festivals or cultural exchange.
	\end{qa}


        \begin{VocabExplain}[Part 2]
					
			\begin{ExplainCard}{must-visit place}[n~phr][B2]
			  \EN{A place considered essential for visitors to see.}
			  \SY{top attraction; highlight}
			  \VI{Địa điểm nhất định phải ghé thăm.}
			  \EX{If you're in Hanoi, the Old Quarter is a \textit{must-visit place}.}
			  \EX{For first-time visitors, the citadel remains a \textit{must-visit place} for its heritage value.}
			  \EX{Travel guides consistently list Hội An as a \textit{must-visit place} for cultural tourism.}
			  \CO{a must-visit place/destination; a must-visit for tourists/first-timers}
			\end{ExplainCard}

			\begin{ExplainCard}{in the heart of}[idiom][B2]
			  \EN{Exactly in the central part of a city or area.}
			  \SY{right in the center; in the core of}
			  \VI{Ngay giữa trung tâm (thành phố/khu vực).}
			  \EX{The café sits \textit{in the heart of} the old town.}
			  \EX{The museum is located \textit{in the heart of} the capital's cultural district.}
			  \EX{Fieldwork was conducted \textit{in the heart of} the metropolitan area.}
			  \CO{right in the heart of the city/downtown/old quarter; nestled in the heart of}
			\end{ExplainCard}

			\begin{ExplainCard}{to the best of my knowledge}[phrase][C1]
			  \EN{As far as I know, based on the information I have.}
			  \SY{as far as I know; as I understand it}
			  \VI{Theo như tôi biết.}
			  \EX{\textit{To the best of my knowledge}, the guided tour starts at 9 a.m.}
			  \EX{\textit{To the best of my knowledge}, the opera house was completed in 1911.}
			  \EX{\textit{To the best of my knowledge}, no study has tested that claim in Vietnam.}
			  \CO{\textit{To the best of my knowledge}, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{run-down district}[n~phr][B2]
			  \EN{An urban area in poor condition due to neglect or lack of investment.}
			  \SY{deprived area; dilapidated neighborhood}
			  \VI{Khu phố xuống cấp, bị bỏ bê.}
			  \EX{They revived a theatre in a \textit{run-down district}.}
			  \EX{Recent grants target long-neglected, \textit{run-down districts}.}
			  \EX{Urban renewal often prioritizes \textit{run-down districts} with high vacancy rates.}
			  \CO{a run-down district/neighborhood/area; a run-down block}
			\end{ExplainCard}

			\begin{ExplainCard}{stand the test of time}[idiom][C1]
			  \EN{To prove durable and valuable after many years.}
			  \SY{endure; remain timeless}
			  \VI{Trường tồn với thời gian; bền bỉ qua năm tháng.}
			  \EX{The building's façade has \textit{stood the test of time}.}
			  \EX{Only thoughtful design truly \textit{stands the test of time}.}
			  \EX{The structure's original acoustics still \textit{stand the test of time}.}
			  \CO{\textit{stand the test of time}; prove/remain timeless}
			\end{ExplainCard}

			\begin{ExplainCard}{refurbishment}[n][C1]
			  \EN{Renovation and redecoration of a building to improve its condition.}
			  \SY{renovation; overhaul}
			  \VI{Sự cải tạo, trùng tu.}
			  \EX{The opera house is closed for \textit{refurbishment} this season.}
			  \EX{The city funded extensive \textit{refurbishment} of heritage sites.}
			  \EX{Post-project audits found the \textit{refurbishment} met conservation standards.}
			  \CO{undergo/complete refurbishment; extensive/major refurbishment; a refurbishment programme}
			\end{ExplainCard}

			\begin{ExplainCard}{intact}[adj][C1]
			  \EN{Undamaged and in its original condition.}
			  \SY{undisturbed; unspoiled}
			  \VI{Nguyên vẹn, không hư hại.}
			  \EX{Despite heavy traffic, the interior remains \textit{intact}.}
			  \EX{Most artifacts survived \textit{intact} after the restoration.}
			  \EX{The conservation plan aimed to keep key features \textit{intact}.}
			  \CO{remain/keep/leave intact; survive intact; preserve sth intact}
			\end{ExplainCard}

			\begin{ExplainCard}{a sense of suspense}[n~phr][B2]
			  \EN{A feeling of excited uncertainty about what will happen next.}
			  \SY{tension; anticipation}
			  \VI{Cảm giác hồi hộp, chờ đợi.}
			  \EX{The approach road builds \textit{a sense of suspense} before the reveal.}
			  \EX{Lighting and pacing create \textit{a sense of suspense} in the exhibit.}
			  \EX{Designers used staggered sightlines to heighten \textit{a sense of suspense}.}
			  \CO{build/create/heighten/maintain a sense of suspense}
			\end{ExplainCard}

			\begin{ExplainCard}{amplify}[v][C1]
			  \EN{(1) Make sound/signal louder or clearer. (2) Make an effect, feeling, or message stronger.}
			  \SY{boost; intensify; heighten; magnify}
			  \VI{(1) Khuếch đại (âm thanh/tín hiệu). (2) Làm tăng/nhấn mạnh (tác động/cảm xúc/thông điệp).}
			  \EX{(1) Hidden mics \textit{amplify} the soloist without echo.}
			  \EX{(2) Social media can \textit{amplify} small rumors into major scandals.}
			  \EX{(2) Policy shocks often \textit{amplify} existing inequalities (academic).}
			  \CO{amplify sound/signal/voice; amplify effect/impact/message; amplify concerns/inequalities}
			\end{ExplainCard}

			\begin{ExplainCard}{architectural landmark}[n][C1]
			  \EN{A building widely recognized for its design or cultural significance.}
			  \SY{iconic building; signature structure}
			  \VI{Công trình kiến trúc tiêu biểu/biểu tượng.}
			  \EX{It's regarded as an \textit{architectural landmark} of the capital.}
			  \EX{Scholars cite the theatre as an \textit{architectural landmark} of the colonial era.}
			  \EX{The registry designated several \textit{architectural landmarks} for protection.}
			  \CO{an architectural landmark/icon/gem; designate/preserve an architectural landmark}
			\end{ExplainCard}

			\begin{ExplainCard}{venue}[n][B2]
			  \EN{The place where a public event or meeting happens.}
			  \SY{site; location}
			  \VI{Địa điểm tổ chức sự kiện.}
			  \EX{The opera house doubles as a concert \textit{venue}.}
			  \EX{The city markets the theatre as a premier \textit{venue} for festivals.}
			  \EX{Researchers surveyed audience flow patterns across major \textit{venues}.}
			  \CO{concert/sports/event venue; a venue for conferences/festivals; book/secure a venue}
			\end{ExplainCard}

        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}

	\begin{qa}{How do people in your country feel about protecting historic buildings?}
	Generally speaking, \textbf{heritage preservation} \textbf{is of tremendous significance} to every country. In particular, monumental works like \textbf{mausoleums} or temples are not only \textbf{historic landmarks} but also treasured places housing various \textbf{artefacts} which provide us a tangible link with our ancestors. \textbf{Sad to say}, people in general are indifferent to \textbf{historic preservation}. This is partly due to the fact that many are \textbf{preoccupied} at their workplace and some may think the protection of historical urban areas are not their responsibilities.
	\end{qa}

	\begin{qa}{Do you think an area can benefit from having an interesting historic place locally? In what way?}
	You know, \textbf{from an economic perspective}, the locals can \textbf{reap enormous benefits} from \textbf{heritage sites} because these places will draw millions of \textbf{outbound tourists} annually, which \textbf{yields} massive profits especially for those working in the tourism industry. \textbf{From a cultural perspective}, the uniqueness of historical sites will be an ideal place for scientists who want to \textbf{dig into the past}.
	\end{qa}

	\begin{qa}{What do you think will happen to historic places or buildings in the future? Why?}
	As I am saying, because of some \textbf{undeniable} advantages of historic spots, these places will be explored at an ever-increasing rate. So, the \textbf{degradation} of the historic sites can \textbf{be anticipated}, especially for the ancient buildings. If the authorities and every single person do not join hands to preserve these sites, \textbf{irreversible} losses of historic sites are \textbf{looming} on the horizon.
	\end{qa}

	\begin{qa}{How were you taught history when you were at school?}
	To be honest, I am not a fan of history, so this subject really \textbf{went over my head} during my junior years. To be frank, instead of being \textbf{whipped into a patriotic fervour}, I was merely given a huge number of national events with different time periods which I had to learn \textbf{by rote}. For an absent-minded person like me, I struggled to learn and repeat lessons \textbf{parrot-fashion}. Having said that, I have to admit that all historical stuff that I was taught are \textbf{comprehensive}. The subject covers a majority of \textbf{milestones} that our \textbf{forefathers} had achieved as well as the \textbf{hardships} they went through to gain our independence.
	\end{qa}

	\begin{qa}{Are there other ways people can learn about history, apart from at school? How?}
	Of course, there are plenty of ways to \textbf{acquire knowledge} about history, not just through academic lessons. For one, participating in historical clubs is an option for individuals to learn and awake their historical passion. The other thing might sound \textbf{appealing} to travelling lovers. In particular, being well-traveled, especially in foreign countries, is a fantastic way to be directly \textbf{exposed to} the \textbf{indigenous} history and gain \textbf{first-hand} experience.
	\end{qa}

	\begin{qa}{Do you think history will still be a school subject in the future? Why?}
	Definitely, even though there might be some students, myself included, who do not have a keen interest in history, I strongly believe the subject still \textbf{plays an indispensable part} in school curriculum. This is simply because history educates young people, lessons about the past and \textbf{cultivates a sense of patriotism}. However, the way history is imparted should be altered to \textbf{arouse} students' interests by integrating technology into teaching.
	\end{qa}

        \begin{VocabExplain}[Part 3]
			\begin{ExplainCard}{heritage preservation}[n~phr][C1]
			  \EN{The protection and maintenance of cultural heritage (tangible and intangible) so its value endures.}
			  \SY{conservation; safeguarding}
			  \VI{Bảo tồn di sản (vật thể \& phi vật thể) để giá trị còn mãi.}
			  \EX{Our town funds \textit{heritage preservation} through community grants.}
			  \EX{Effective \textit{heritage preservation} balances access with conservation.}
			  \EX{Policy frameworks now integrate \textit{heritage preservation} into urban planning.}
			  \CO{heritage preservation/conservation; a heritage-preservation plan/policy; invest in heritage preservation}
			\end{ExplainCard}

			\begin{ExplainCard}{of tremendous significance}[phr][C1]
			  \EN{Extremely important in impact or meaning.}
			  \SY{highly significant; of great consequence}
			  \VI{Có tầm quan trọng đặc biệt lớn.}
			  \EX{For locals, the shrine is \textit{of tremendous significance}.}
			  \EX{The ruling is \textit{of tremendous significance} for cultural policy.}
			  \EX{Findings \textit{of tremendous significance} reshape the field.}
			  \CO{be of tremendous significance to/for; a matter of tremendous significance}
			\end{ExplainCard}

			\begin{ExplainCard}{monumental}[adj][C1]
			  \EN{(1) Extremely important or influential. (2) Very large or impressive in scale.}
			  \SY{(1) momentous; seminal \quad (2) massive; grand}
			  \VI{(1) Có ý nghĩa cực kỳ quan trọng. (2) Đồ sộ, hoành tráng.}
			  \EX{(1) It was a \textit{monumental} decision for the city's identity.}
			  \EX{(2) The project delivered a \textit{monumental} archway at the entrance.}
			  \EX{(1) Scholars regard the reform as \textit{monumental} in heritage law.}
			  \CO{a monumental decision/achievement; a monumental building/arch/statue}
			\end{ExplainCard}

			\begin{ExplainCard}{mausoleum}[n][C1]
			  \EN{A grand building housing the remains of a person or family.}
			  \SY{tomb; burial chamber}
			  \VI{Lăng mộ (công trình lớn chứa hài cốt).}
			  \EX{We visited a royal \textit{mausoleum} at sunset.}
			  \EX{The \textit{mausoleum} forms the focal point of the complex.}
			  \EX{Conservation works stabilized the \textit{mausoleum}'s stone vaults.}
			  \CO{a royal/state mausoleum; build/visit a mausoleum; mausoleum complex}
			\end{ExplainCard}

			\begin{ExplainCard}{landmark}[n][B2]
			  \EN{(1) A prominent feature/building used for orientation. (2) An event or decision marking a critical stage.}
			  \SY{(1) beacon; marker \quad (2) milestone; watershed}
			  \VI{(1) Công trình nổi bật để định vị. (2) Cột mốc quan trọng.}
			  \EX{(1) The opera house is a riverside \textit{landmark}.}
			  \EX{(2) The act was a \textit{landmark} in heritage protection.}
			  \EX{(2) Courts hailed the ruling as a \textit{landmark} case.}
			  \CO{city/architectural landmark; a landmark case/decision/ruling}
			\end{ExplainCard}

			\begin{ExplainCard}{artefact (BrE) / artifact (AmE)}[n][C1]
			  \EN{An object made by humans, typically of historical or cultural interest.}
			  \SY{antiquity; relic}
			  \VI{Hiện vật/di vật do con người tạo ra mang giá trị lịch sử–văn hoá.}
			  \EX{The museum displays bronze-age \textit{artefacts}.}
			  \EX{Curators catalogued thousands of excavated \textit{artefacts}.}
			  \EX{Provenance checks authenticate high-value \textit{artefacts}.}
			  \CO{ancient/ceramic artefacts; excavate/catalogue/preserve artefacts}
			\end{ExplainCard}

			\begin{ExplainCard}{sad to say}[idiom][B2]
			  \EN{Regrettably; used to introduce unwelcome news.}
			  \SY{regrettably; unfortunately}
			  \VI{Đáng tiếc là; thật buồn là.}
			  \EX{\textit{Sad to say}, the murals were demolished.}
			  \EX{\textit{Sad to say}, funding hasn't materialized this year.}
			  \EX{\textit{Sad to say}, longitudinal data remain scarce.}
			  \CO{\textit{Sad to say}, + clause; it is sad to say that + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{historic preservation}[n~phr][C1]
			  \EN{The practice of protecting historic buildings, districts, and sites for their cultural value.}
			  \SY{building conservation; heritage conservation}
			  \VI{Bảo tồn công trình/khu phố/sít lịch sử.}
			  \EX{Training in \textit{historic preservation} is now offered locally.}
			  \EX{\textit{Historic preservation} guides informed the façade repair.}
			  \EX{Zoning integrates \textit{historic preservation} with development.}
			  \CO{historic preservation policy/ordinance; a preservation district; preservation guidelines}
			\end{ExplainCard}

			\begin{ExplainCard}{preoccupied (with)}[adj][C1]
			  \EN{So absorbed in thought or tasks that you are not fully attentive to other things.}
			  \SY{engrossed; absorbed; wrapped up}
			  \VI{Mải mê/bận tâm (đến mức xao lãng điều khác).}
			  \EX{People are \textit{preoccupied with} work and deadlines.}
			  \EX{Residents were \textit{preoccupied} by economic concerns.}
			  \EX{Participants appeared \textit{preoccupied} during site visits.}
			  \CO{preoccupied with worries/work; look/seem preoccupied; mentally preoccupied}
			\end{ExplainCard}

			\begin{ExplainCard}{(from) an economic perspective}[n~phr][B2]
			  \EN{Viewed through the lens of costs, incentives, and outcomes.}
			  \SY{from an economic standpoint; economically speaking}
			  \VI{Từ góc độ kinh tế.}
			  \EX{\textit{From an economic perspective}, heritage boosts local demand.}
			  \EX{The project is viable \textit{from an economic perspective}.}
			  \EX{Analyses \textit{from an economic perspective} highlight spillovers.}
			  \CO{from an economic perspective/standpoint; economic lens/analysis}
			\end{ExplainCard}

			\begin{ExplainCard}{reap enormous benefits}[v~phr][C1]
			  \EN{To gain very large advantages or returns.}
			  \SY{derive major benefits; garner substantial gains}
			  \VI{Thu về lợi ích rất lớn.}
			  \EX{Local vendors \textit{reap enormous benefits} during festivals.}
			  \EX{Regions \textit{reap enormous benefits} from heritage tourism.}
			  \EX{Firms \textit{reap} productivity gains from clustering.}
			  \CO{reap benefits/gains/dividends; reap enormous/substantial benefits}
			\end{ExplainCard}

			\begin{ExplainCard}{heritage site}[n~phr][B2]
			  \EN{A location officially protected for its cultural or historical value.}
			  \SY{cultural site; protected site}
			  \VI{Địa điểm di sản được bảo vệ.}
			  \EX{This \textit{heritage site} draws families at weekends.}
			  \EX{Two \textit{heritage sites} were upgraded this year.}
			  \EX{Listing a \textit{heritage site} can attract conservation funding.}
			  \CO{designate/list a heritage site; UNESCO/World Heritage Site; visit a heritage site}
			\end{ExplainCard}

			\begin{ExplainCard}{outbound tourists}[n~phr][C1]
			  \EN{Travellers leaving their home country to visit others.}
			  \SY{overseas travellers; outbound travellers}
			  \VI{Khách du lịch ra nước ngoài.}
			  \EX{\textit{Outbound tourists} rose after visa simplifications.}
			  \EX{Spending by \textit{outbound tourists} surged last quarter.}
			  \EX{Data on \textit{outbound tourists} inform balance-of-payments stats.}
			  \CO{growth in outbound tourists; spend by outbound tourists; outbound tourism market}
			\end{ExplainCard}

			\begin{ExplainCard}{yield}[v][C1]
			  \EN{To produce or provide (profits, results, or information).}
			  \SY{generate; produce; deliver}
			  \VI{Tạo ra (lợi nhuận/kết quả/thông tin).}
			  \EX{Heritage trails \textit{yield} steady income for locals.}
			  \EX{The survey \textit{yielded} robust, comparable results.}
			  \EX{Adaptive reuse can \textit{yield} significant carbon savings.}
			  \CO{yield results/profits/insights; high-yield strategy; yield measurable outcomes}
			\end{ExplainCard}

			\begin{ExplainCard}{(from) a cultural perspective}[n~phr][B2]
			  \EN{Viewed in terms of beliefs, practices, and identity.}
			  \SY{from a cultural standpoint; culturally speaking}
			  \VI{Từ góc độ văn hoá.}
			  \EX{\textit{From a cultural perspective}, festivals sustain community bonds.}
			  \EX{The decision is defensible \textit{from a cultural perspective}.}
			  \EX{Comparisons \textit{from a cultural perspective} reveal shared motifs.}
			  \CO{from a cultural perspective/standpoint; cultural lens/analysis}
			\end{ExplainCard}

			\begin{ExplainCard}{dig into the past}[v~phr][C1]
			  \EN{To investigate earlier periods to uncover facts or context.}
			  \SY{delve into; probe}
			  \VI{Lần tìm/đào sâu quá khứ để hiểu rõ hơn.}
			  \EX{Archivists \textit{dig into the past} to verify the claim.}
			  \EX{We \textit{dug into the past} of the site before designing.}
			  \EX{Scholars \textit{dig into the past} to reconstruct trade routes.}
			  \CO{dig/delve into the past; dig into archives/records}
			\end{ExplainCard}

			\begin{ExplainCard}{undeniable}[adj][B2]
			  \EN{Impossible to dispute; clearly true.}
			  \SY{indisputable; irrefutable}
			  \VI{Không thể phủ nhận.}
			  \EX{Its tourism value is \textit{undeniable}.}
			  \EX{Data show an \textit{undeniable} uptick in arrivals.}
			  \EX{There is \textit{undeniable} evidence of deterioration.}
			  \CO{an undeniable fact/benefit/evidence; be undeniable that + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{degradation}[n][C1]
			  \EN{The process by which something deteriorates or is damaged.}
			  \SY{deterioration; decline}
			  \VI{Sự xuống cấp, hư hại.}
			  \EX{Traffic causes façade \textit{degradation}.}
			  \EX{Monitoring tracks material \textit{degradation} over time.}
			  \EX{Policy gaps accelerated ecological \textit{degradation}.}
			  \CO{environmental/material degradation; prevent/mitigate degradation}
			\end{ExplainCard}

			\begin{ExplainCard}{anticipated}[adj][B2]
			  \EN{Expected or predicted to occur.}
			  \SY{expected; projected; forecast}
			  \VI{Được dự đoán/đợi chờ.}
			  \EX{The \textit{anticipated} reopening drew large crowds.}
			  \EX{Costs exceeded \textit{anticipated} levels.}
			  \EX{The \textit{anticipated} benefits include job creation.}
			  \CO{anticipated costs/benefits/outcomes; widely anticipated event}
			\end{ExplainCard}

			\begin{ExplainCard}{irreversible}[adj][C1]
			  \EN{Impossible to undo or restore to the original state.}
			  \SY{irreparable; irrevocable}
			  \VI{Không thể đảo ngược/khôi phục.}
			  \EX{Water damage can be \textit{irreversible}.}
			  \EX{Demolition is \textit{irreversible} and should be a last resort.}
			  \EX{Ecologists warn of \textit{irreversible} habitat loss.}
			  \CO{cause/avoid irreversible damage; irreversible change/loss}
			\end{ExplainCard}

			\begin{ExplainCard}{go over my head}[idiom][B2]
			  \EN{To be too difficult for me to understand.}
			  \SY{baffle me; be beyond me}
			  \VI{Vượt quá tầm hiểu biết của tôi.}
			  \EX{The architectural jargon \textit{went over my head}.}
			  \EX{That equation \textit{goes over my head}—explain it simply.}
			  \EX{For many visitors, the legal terms \textit{go over their heads}.}
			  \CO{go/went over my head; completely over my head}
			\end{ExplainCard}

			\begin{ExplainCard}{junior}[adj][B2]
			  \EN{(1) Lower in rank. (2) Belonging to earlier/younger school years.}
			  \SY{(1) subordinate \quad (2) lower-grade; underclass}
			  \VI{(1) Cấp dưới. (2) Bậc học/lớp dưới, năm đầu.}
			  \EX{(1) She started in a \textit{junior} role and advanced quickly.}
			  \EX{(2) During my \textit{junior} years, history bored me.}
			  \EX{(2) \textit{Junior} curricula often simplify complex topics.}
			  \CO{junior staff/position; junior years/students; junior curriculum}
			\end{ExplainCard}

			\begin{ExplainCard}{be whipped into (a state)}[phr.v~passive][C1]
			  \EN{To be stirred up into an intense emotion or condition.}
			  \SY{be roused to; be worked up into}
			  \VI{Bị khơi dậy/đẩy lên (một trạng thái cảm xúc mạnh).}
			  \EX{Crowds were \textit{whipped into} excitement by the anthem.}
			  \EX{Students were \textit{whipped into} debate over the plan.}
			  \EX{Propaganda \textit{whipped} audiences \textit{into} fervour.}
			  \CO{whip sb into a frenzy/fervour/excitement; be whipped into + state}
			\end{ExplainCard}

			\begin{ExplainCard}{patriotic fervour}[n][C1]
			  \EN{Intense enthusiasm and pride for one's country.}
			  \SY{patriotism; national zeal}
			  \VI{Lòng nhiệt huyết yêu nước.}
			  \EX{The parade stirred \textit{patriotic fervour}.}
			  \EX{\textit{Patriotic fervour} peaked during the centenary.}
			  \EX{Texts trace cycles of \textit{patriotic fervour} in wartime.}
			  \CO{stir/whip up patriotic fervour; a wave/surge of patriotic fervour}
			\end{ExplainCard}

			\begin{ExplainCard}{learn (sth) by rote}[idiom][B2]
			  \EN{To memorize mechanically without deep understanding.}
			  \SY{memorize mechanically; rote-learn}
			  \VI{Học vẹt (thuộc lòng mà không hiểu sâu).}
			  \EX{We \textit{learned by rote} for the exam.}
			  \EX{Rote drills help with dates but not analysis.}
			  \EX{Policies discourage \textit{rote learning} in history courses.}
			  \CO{learn by rote; rote learning/memorisation; rote drills}
			\end{ExplainCard}

			\begin{ExplainCard}{parrot-fashion}[idiom][C1]
			  \EN{In a way that repeats words exactly without thinking about meaning.}
			  \SY{mechanically; mindlessly}
			  \VI{Lặp lại máy móc, học vẹt.}
			  \EX{He answered \textit{parrot-fashion} and missed the point.}
			  \EX{Students recited laws \textit{parrot-fashion}.}
			  \EX{Avoid \textit{parrot-fashion} summaries in essays.}
			  \CO{repeat/recite parrot-fashion; learn sth parrot-fashion}
			\end{ExplainCard}

			\begin{ExplainCard}{comprehensive}[adj][C1]
			  \EN{Covering almost all relevant items or details; thorough.}
			  \SY{exhaustive; thorough; all-inclusive}
			  \VI{Toàn diện, bao quát.}
			  \EX{The syllabus is \textit{comprehensive} but readable.}
			  \EX{They produced a \textit{comprehensive} survey of temples.}
			  \EX{A \textit{comprehensive} audit identified conservation gaps.}
			  \CO{comprehensive review/plan/survey; comprehensive coverage}
			\end{ExplainCard}

			\begin{ExplainCard}{milestone}[n][B2]
			  \EN{A very important stage or event in a development.}
			  \SY{landmark; turning point}
			  \VI{Cột mốc quan trọng.}
			  \EX{Winning the grant was a \textit{milestone} for the project.}
			  \EX{The listing marked a \textit{milestone} in preservation.}
			  \EX{Publication in a top journal is a career \textit{milestone}.}
			  \CO{a major/key milestone; reach/mark/pass a milestone}
			\end{ExplainCard}

			\begin{ExplainCard}{forefathers}[n][B2]
			  \EN{Ancestors from many generations ago.}
			  \SY{ancestors; forebears}
			  \VI{Ông cha, tổ tiên.}
			  \EX{We honour our \textit{forefathers} at this temple.}
			  \EX{Customs from our \textit{forefathers} still guide rituals.}
			  \EX{Texts attribute the craft to village \textit{forefathers}.}
			  \CO{honour/remember one's forefathers; the wisdom of our forefathers}
			\end{ExplainCard}

			\begin{ExplainCard}{hardships}[n][B2]
			  \EN{Difficult conditions such as poverty or deprivation.}
			  \SY{adversities; privations; difficulties}
			  \VI{Khó khăn, gian khổ.}
			  \EX{Families endured wartime \textit{hardships}.}
			  \EX{Migrants faced acute economic \textit{hardships}.}
			  \EX{Stipends alleviate student \textit{hardships}.}
			  \CO{face/experience/endure hardships; economic/financial hardships}
			\end{ExplainCard}

			\begin{ExplainCard}{independence}[n][B2]
			  \EN{Freedom from control by another country.}
			  \SY{sovereignty; self-rule}
			  \VI{Nền độc lập.}
			  \EX{They fought for national \textit{independence}.}
			  \EX{Museums recount the road to \textit{independence}.}
			  \EX{Archives detail the \textit{independence} movement.}
			  \CO{gain/declare/achieve independence; struggle for independence}
			\end{ExplainCard}

			\begin{ExplainCard}{acquire knowledge}[v~phr][B2]
			  \EN{To gain understanding or information through study or experience.}
			  \SY{gain knowledge; build understanding}
			  \VI{Tiếp thu/thu nhận kiến thức.}
			  \EX{You \textit{acquire knowledge} fastest by teaching others.}
			  \EX{Fieldwork helps students \textit{acquire knowledge} first-hand.}
			  \EX{Programs aim to help workers \textit{acquire} new skills.}
			  \CO{acquire knowledge/skills/competence; actively/systematically acquire}
			\end{ExplainCard}

			\begin{ExplainCard}{appealing}[adj][B2]
			  \EN{Attractive or interesting; likely to draw attention.}
			  \SY{engaging; inviting; attractive}
			  \VI{Hấp dẫn, lôi cuốn.}
			  \EX{Night tours sound \textit{appealing} to visitors.}
			  \EX{The design is simple yet \textit{appealing}.}
			  \EX{An \textit{appealing} narrative broadens audience reach.}
			  \CO{find sth appealing; visually/commercially appealing; make sth more appealing}
			\end{ExplainCard}

			\begin{ExplainCard}{expose}[v][C1]
			  \EN{(1) To make something hidden visible. (2) To give someone experience of something.}
			  \SY{(1) reveal; uncover \quad (2) acquaint; introduce}
			  \VI{(1) Phơi bày/cho thấy. (2) Cho ai tiếp xúc/trải nghiệm.}
			  \EX{(1) The audit \textit{exposed} safety flaws.}
			  \EX{(2) Travel \textit{exposes} students to indigenous history.}
			  \EX{(2) Workshops \textit{expose} youths to conservation skills.}
			  \CO{expose corruption/weaknesses; expose sb to ideas/risks/cultures}
			\end{ExplainCard}

			\begin{ExplainCard}{indigenous history}[n~phr][C1]
			  \EN{The history of peoples native to a place, not originating elsewhere.}
			  \SY{native history; local heritage}
			  \VI{Lịch sử bản địa (của cư dân gốc).}
			  \EX{Tours highlight \textit{indigenous history} along the river.}
			  \EX{Courses integrate \textit{indigenous history} and language.}
			  \EX{Exhibits centre \textit{indigenous history} and stewardship.}
			  \CO{study/centre indigenous history; indigenous history and culture}
			\end{ExplainCard}

			\begin{ExplainCard}{first-hand}[adj][B2]
			  \EN{Obtained or experienced directly, not through others.}
			  \SY{direct; immediate}
			  \VI{Trực tiếp, tận mắt.}
			  \EX{Guides share \textit{first-hand} stories from restorations.}
			  \EX{We gathered \textit{first-hand} observations on site.}
			  \EX{Visitors gain \textit{first-hand} insight into craft methods.}
			  \CO{first-hand experience/evidence/accounts; gain/offer first-hand insight}
			\end{ExplainCard}

			\begin{ExplainCard}{play an indispensable part}[v~phr][C1]
			  \EN{To be essential to the success or functioning of something.}
			  \SY{be integral; be vital; be pivotal}
			  \VI{Đóng vai trò không thể thiếu.}
			  \EX{Volunteers \textit{play an indispensable part} in preservation.}
			  \EX{Community buy-in \textit{plays an indispensable part} in policy uptake.}
			  \EX{Craft masters \textit{play an indispensable part} in training.}
			  \CO{play an indispensable/essential/vital part/role}
			\end{ExplainCard}

			\begin{ExplainCard}{invaluable}[adj][C1]
			  \EN{Extremely useful; too valuable to measure in money.}
			  \SY{priceless; of inestimable value}
			  \VI{Vô giá, cực kỳ hữu ích.}
			  \EX{Local knowledge proved \textit{invaluable}.}
			  \EX{The archive offers \textit{invaluable} primary sources.}
			  \EX{Community partners were \textit{invaluable} during fieldwork.}
			  \CO{prove/become invaluable; invaluable resource/ally/insight}
			\end{ExplainCard}

			\begin{ExplainCard}{cultivate}[v][C1]
			  \EN{To develop or foster a quality, relationship, or skill over time.}
			  \SY{foster; nurture; build}
			  \VI{Nuôi dưỡng, gây dựng, phát triển.}
			  \EX{Programs \textit{cultivate} pride in local heritage.}
			  \EX{Museums \textit{cultivate} long-term partnerships with schools.}
			  \EX{Workshops \textit{cultivate} conservation competencies.}
			  \CO{cultivate trust/relationships/skills; cultivate interest/pride}
			\end{ExplainCard}

			\begin{ExplainCard}{a sense of patriotism}[n~phr][B2]
			  \EN{A feeling of love and loyalty toward one's country.}
			  \SY{patriotic sentiment; national pride}
			  \VI{Tinh thần yêu nước.}
			  \EX{Stories of sacrifice build \textit{a sense of patriotism}.}
			  \EX{Education can strengthen \textit{a sense of patriotism}.}
			  \EX{Ceremonies nurture \textit{a sense of patriotism} among youths.}
			  \CO{foster/nurture a sense of patriotism; a deep/renewed sense of patriotism}
			\end{ExplainCard}

			\begin{ExplainCard}{arouse}[v][C1]
			  \EN{To stimulate a feeling, interest, or action.}
			  \SY{stir; kindle; spark}
			  \VI{Khơi dậy, kích thích.}
			  \EX{The narrative \textit{aroused} public interest.}
			  \EX{Exhibits \textit{arouse} curiosity about the site's past.}
			  \EX{Campaigns \textit{aroused} support for preservation funding.}
			  \CO{arouse interest/curiosity/emotion; arouse public support}
			\end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
		\VH{mixed-age}{(adj) involving a lot of age groups}{(tính từ) nhiều lứa tuổi}
		\VH{to strike up (a friendship)}{(phr.v) to initiate, instigate, or begin (a friendship)}{(cụm động từ) bắt đầu 1 tình bạn}
		\VH{to pal around (with somebody)}{(phr.v) to spend time with somebody as a friend}{(cụm động từ) dành thời gian cho bạn bè}
		\VH{to make ends meet}{(idiom) to earn just enough money to pay one's bills}{(thành ngữ) kiếm đủ tiền để sống}
		\VH{quality time}{(phrase) time spent with family}{(cụm từ) thời gian dành cho gia đình}
		\VH{the hustle and bustle of}{(idiom) busy and frenetic activity or excitement}{(thành ngữ) sự náo nhiệt, bận rộn}
		\VH{vividly}{(adv) in a way that is very clear, powerful, and detailed in your mind}{(trạng từ) rõ rệt}
		\VH{to hang out with}{(phr.v) spend time relaxing or enjoying oneself}{(cụm động từ) đi chơi}
		\VH{to splurge on}{(phr.v) to spend a lot of money on something that you do not really need}{(cụm động từ) tiêu hoang phí}
		\VH{lavish}{(adj) large in amount, or impressive, and usually costing a lot of money}{(tính từ) hoang phí, tốn kém}
		\VH{die-hard fan}{(phrase) somebody who is completely 100\% obsessed with their favorite game, band, movie, etc}{(cụm từ) người hâm mộ cuồng nhiệt}
		\VH{to be on the top of somebody's list}{(idiom) something is the first and most important thing that one needs to do}{(thành ngữ) một trong những điều phải làm ngay}
		\VH{to rank first in the order of importance}{(phrase) to be the most important}{(cụm từ) là quan trọng nhất}
		\VH{choosy}{(adj) careful in choosing; difficult to please}{(tính từ) kén cá chọn canh, khó chiều}
		\VH{to forge}{(v) to put a lot of effort into making something successful or strong so that it will last}{(động từ) lập nên}
		\VH{a friend in need is a friend indeed}{(proverb) a person who helps at a difficult time is a truly reliable person}{(tục ngữ) trong hoạn nạn mới biết ai là bạn tốt}
		\VH{to lend a sympathetic ear to}{(idiom) to listen to someone, especially someone who is upset}{(thành ngữ) lắng nghe ai}
		\VH{in hot water}{(idiom) in trouble}{(thành ngữ) gặp rắc rối}
		\VH{fair-weather friends}{(phrase) a person who stops being a friend in times of difficulty}{(cụm từ) bạn đểu}

		\VH{must-visit place}{(idiom) a place considered essential to visit or see}{(thành ngữ) nơi nhất định phải đến}
		\VH{in the heart of}{(idiom) in the center of}{(thành ngữ) trung tâm}
		\VH{to the best of my knowledge}{(phrase) as far as i'm concerned}{(cụm từ) theo như tôi biết}
		\VH{a run-down district}{(phrase) a place in bad condition}{(cụm từ) 1 vùng tồi tàn}
		\VH{to stand the test of time}{(phrase) it is still in existence over time}{(cụm từ) trường tồn với thời gian}
		\VH{refurbishment}{(noun) the renovation and redecoration of something, especially a building}{(danh từ) sự cải tạo, trùng tu}
		\VH{intact}{(adj) undamaged, unbroken or in good condition}{(tính từ) nguyên vẹn}
		\VH{a sense of suspense}{(phrase) a feeling of excited waiting}{(cụm từ) cảm giác hồi hộp}
		\VH{to amplify}{(v) to increase the size or effect of something}{(động từ) khuếch đại}
		\VH{architectural landmarks}{(phrase) a structure that has significant architectural meaning}{(cụm từ) tòa nhà quan trọng có kiến trúc độc đáo trong thành phố}
		\VH{venue}{(n) the place where a public event or meeting happens}{(danh từ) địa điểm tổ chức}

		\VH{heritage preservation}{(phrase) the act of keeping the history traditions and qualities in its original state or in good condition}{(cụm từ) bảo tồn di sản}
		\VH{of tremendous significance}{(phrase) great importance}{(cụm từ) có tầm quan trọng lớn}
		\VH{monumental}{(adj) very important and having a great influence, especially as the result of years of work}{(tính từ) vĩ đại, có ý nghĩa quan trọng}
		\VH{mausoleums}{(n) a special building made to hold the dead body of an important person or the dead bodies of a family}{(danh từ) lăng mộ}
		\VH{landmark}{(n) something, such as a large building, that you can see clearly from a distance and that will help you to know where you are}{(danh từ) tòa nhà biểu tượng}
		\VH{artefact}{(n) an object that is made by a person, especially something of historical or cultural interest}{(danh từ) di vật}
		\VH{Sad to say}{(idiom) regrettable}{(thành ngữ) đáng tiếc là, thật đáng buồn là}
		\VH{historic preservation}{(phrase) the practice of protecting and preserving sites, structures or districts which reflect elements of local or national cultural, social, economic, political, archaeological or architectural history}{(cụm từ) sự bảo tồn địa danh lịch sử}
		\VH{preoccupied}{(adj) busy}{(tính từ) bận rộn}
		\VH{an economic perspective}{(phrase) a particular attitude towards financial; a way of thinking about financial}{(cụm từ) tư góc độ kinh tế}
		\VH{to reap enormous benefits}{(phrase) to get great advantages}{(cụm từ) thu được nhiều lợi ích lớn từ cái gì đó}
		\VH{heritage sites}{(phrase) an official location where pieces of political, military, cultural, or social history have been preserved due to their cultural history value}{(cụm từ) địa điểm di sản}
		\VH{outbound tourists}{(phrase) people who are travelling away from a particular point}{(cụm từ) du khách nước ngoài}
		\VH{to yield}{(v) to produce or provide something, for example a profit, result or crop}{(động từ) tạo ra (năng suất, lợi nhuận)}
		\VH{a cultural perspective}{(phrase) a particular attitude towards culture; a way of thinking about culture}{(cụm từ) tư góc độ văn hóa}
		\VH{to dig into the past}{(phrase) to try to find out about something unknown or secret in the past}{(cụm từ) tìm hiểu quá khứ}
		\VH{undeniable}{(adj) true or certain; that cannot be denied}{(tính từ) không thể phủ nhận}
		\VH{degradation}{(n) the process of something being damaged or made worse}{(danh từ) sự xuống cấp, phá hủy}
		\VH{anticipated}{(p2) to be expected}{(phần từ 2) được dự đoán, dự tính trước}
		\VH{irreversible}{(adj) that cannot be changed back to what it was before}{(tính từ) không thể thay đổi, quay lại như trước}
		\VH{to go over my head}{(idiom) too difficult or strange for you to understand or remember}{(thành ngữ) nước đổ đầu vịt}
		\VH{junior}{(adj) having a low rank in an organization or a profession}{(tính từ) trung học}
		\VH{to be whipped into}{(p2) to become something}{(phần từ 2) được trở thành}
		\VH{a patriotic fervour}{(n) very strong feeling or enthusiasm}{(danh từ) lòng yêu nước, nhiệt huyết}
		\VH{to learn something by rote}{(idiom) learn something in order to be able to repeat it from memory, rather than in order to understand it}{(thành ngữ) học vẹt}
		\VH{to learn something parrot-fashion}{(idiom) do it without thinking about it or understanding what it means}{(thành ngữ) học vẹt}
		\VH{comprehensive}{(adj) including all, or almost all, the items, details, facts, information, etc., that may be concerned}{(tính từ) toàn diện}
		\VH{milestones}{(n) very important stages or events in the development of something}{(danh từ) các cột mốc quan trọng}
		\VH{forefathers}{(n) people in a family who lived a long time ago}{(danh từ) ông cha (tổ tiên)}
		\VH{hardships}{(n) a situation that is difficult and unpleasant because you do not have enough money, food, clothes, etc}{(danh từ) khó khăn, gian khổ}
		\VH{independence}{(n) freedom from political control by other countries}{(danh từ) sự độc lập}
		\VH{to acquire knowledge}{(phrase) to get an insight in to something}{(cụm từ) học tập để thu được kiến thức}
		\VH{appealing}{(adj) attractive or interesting}{(tính từ) thu hút, hấp dẫn}
		\VH{to expose}{(v) to show something that is usually hidden}{(động từ) tiếp xúc}
		\VH{indigenous history}{(phrase) history naturally existing in a place or country rather than arriving from another place}{(cụm từ) lịch sử bản địa}
		\VH{first-hand}{(adj) obtained or experienced yourself}{(tính từ) trải nghiệm thực tế của bản thân}
		\VH{to play an indispensable part}{(phrase) play an important role}{(cụm từ) đóng vai trò quan trọng, không thể thiếu}
		\VH{invaluable}{(adj) extremely useful}{(tính từ) có giá trị cao; vô giá}
		\VH{to cultivate}{(v) to nurture, develop}{(động từ) nuôi dưỡng, phát triển}
		\VH{a sense of patriotism}{(phrase) the feeling of love, devotion and sense of attachment to a homeland}{(cụm từ) tinh thần yêu nước}
		\VH{to arouse}{(verb) to make somebody feel more active and want to start doing something}{(động từ) khơi dậy}
	\end{VocabHighlights}
    \end{test}

    \begin{test}{TEST 2}
    \noindent
    \textbf{Part 1. Food and Cooking}
	\begin{qa}{What kinds of food do you like to eat?}
	Well, \textbf{there's no accounting for taste}. I am into Vietnamese cuisine, especially something made from rice and filled with \textbf{broth} such as ``pho bo'' or ``bun bo Hue'' (Hue chilly pork vermicelli). They are generally \textbf{piping hot} and a \textbf{steaming} bowl of ``pho bo'' or ``bun bo Hue'' looks so \textbf{appetizing}.
	\end{qa}

	\begin{qa}{What kind of new food would you like to try? [Why?]}
	If possible, I'd love to \textbf{take a whack at} some Thai foods such as Tom Yum Goong (Spicy Shrimp Soup) and Pad Thai (Thai style Fried Noodles). I've never tried them so far but the looks of it besides its ingredients like \textbf{succulent} fresh prawns, \textbf{crunchy} bean sprouts, etc. have already \textbf{whetted my appetite}.
	\end{qa}

	\begin{qa}{Do you like cooking? [Why/Why not?]}
	Yes, definitely. I first learned how to cook to \textbf{fend for myself} when I was in the U.K to pursue my Master degree. At first, cooking seems to have \textbf{bored me stiff} but then, I gradually felt \textbf{a sense of achievement} upon cooking something \textbf{lip-smacking} \textbf{to go round}. Later, when I returned to Vietnam, I also had to continue cooking to \textbf{cater to} my wife who \textbf{was with child}. Looking at how she \textbf{dined to her heart's content} delighted me.
	\end{qa}

	\begin{qa}{What was the last meal you cooked?}
	\textbf{To the best of my recollection}, I was responsible for a three-course meal. The staple was rice, of course this is \textbf{indispensable} in any Vietnamese meal. Then, I made \textbf{sweet and sour pork ribs stir-fry} alongside \textbf{boiled water morning glory}. My heart \textbf{swelled with delight} because there was hardly any \textbf{leftover} after this meal. I believe I am \textbf{a dab hand} at making pork ribs.
	\end{qa}

	\begin{qa}{Do you prefer home-cooked food or food from restaurants? [Why?]}
	It depends on each day. On weekdays, \textbf{home-made} foods are prioritized but at weekends, I often \textbf{treat my family to} a \textbf{sumptuous} meal at some \textbf{eateries} nearby \textbf{for a change of pace}.
	\end{qa}

        \begin{VocabExplain}[Part 1]
			\begin{ExplainCard}{There's no accounting for taste}[proverb][B2]
			  \EN{People like different things and there's no simple explanation for it.}
			  \SY{tastes differ; to each their own}
			  \VI{Gu mỗi người mỗi khác; khó mà giải thích vì sao.}
			  \EX{You love durian? Well, \textit{there's no accounting for taste}.}
			  \EX{As the reviews sharply disagreed, the editor shrugged—\textit{there's no accounting for taste}.}
			  \CO{\textit{there's no accounting for taste}}
			\end{ExplainCard}

			\begin{ExplainCard}{broth}[n][B2]
			  \EN{A clear savoury liquid made by simmering meat/bones or vegetables in water.}
			  \SY{stock; bouillon}
			  \VI{Nước dùng trong, ninh từ xương/thịt hoặc rau củ.}
			  \EX{Pho \textit{broth} should be clear yet full-bodied.}
			  \EX{The recipe starts with a chicken \textit{broth} reduced for 30 minutes.}
			  \CO{chicken/beef/vegetable broth; rich/clear broth; simmer/strain broth}
			\end{ExplainCard}

			\begin{ExplainCard}{piping hot}[adj~phr][B2]
			  \EN{Very hot (about food or drink).}
			  \SY{scalding; steaming hot}
			  \VI{Nóng hổi; vừa thổi vừa ăn.}
			  \EX{Serve the noodles \textit{piping hot}.}
			  \EX{The dumplings arrived \textit{piping hot} and fragrant.}
			  \CO{serve/eat/drink sth piping hot; piping hot soup/tea}
			\end{ExplainCard}

			\begin{ExplainCard}{steaming}[adj][B2]
			  \EN{(in this context) Giving off visible vapour; \textit{steaming}.}
			  \SY{steaming; billowing (with steam)}
			  \VI{Bốc hơi nghi ngút (tỏa khói).}
			  \EX{A \textit{streaming} bowl of pho brightened the cold morning.}
			  \EX{We queued for \textit{streaming} cups of cocoa.}
			  \CO{a streaming bowl/mug; streaming hot noodles}
			\end{ExplainCard}

			\begin{ExplainCard}{appetizing}[adj][B2]
			  \EN{Smelling or looking likely to taste good.}
			  \SY{mouth-watering; tempting}
			  \VI{Nhìn/thơm ngon, kích thích vị giác.}
			  \EX{The broth looked \textit{appetizing} with herbs on top.}
			  \EX{An \textit{appetizing} aroma greeted diners at the door.}
			  \CO{an appetizing dish/aroma/appearance; look/smell appetizing}
			\end{ExplainCard}

			\begin{ExplainCard}{take a whack at}[idiom][B2]
			  \EN{To try or attempt something.}
			  \SY{give (sth) a try; have a go at}
			  \VI{Thử làm; thử sức.}
			  \EX{I'd love to \textit{take a whack at} cooking Pad Thai.}
			  \EX{She \textit{took a whack at} sourdough during lockdown.}
			  \CO{take a whack at cooking/baking/learning sth}
			\end{ExplainCard}

			\begin{ExplainCard}{succulent}[adj][B2]
			  \EN{Juicy and tender (about food, esp.\ meat or fruit).}
			  \SY{juicy; tender}
			  \VI{Mọng nước, mềm ngọt.}
			  \EX{The prawns were \textit{succulent} and sweet.}
			  \EX{A \textit{succulent} cut of roast pork anchored the meal.}
			  \CO{succulent prawns/steak/peaches; wonderfully/remarkably succulent}
			\end{ExplainCard}

			\begin{ExplainCard}{crunchy}[adj][B2]
			  \EN{Firm and crisp, making a sharp sound when bitten.}
			  \SY{crisp; crisp-textured}
			  \VI{Giòn rụm, cắn phát ra tiếng.}
			  \EX{Top the noodles with \textit{crunchy} bean sprouts.}
			  \EX{The salad adds a \textit{crunchy} contrast to the stew.}
			  \CO{crunchy texture/veg/topping; deliciously/pleasantly crunchy}
			\end{ExplainCard}

			\begin{ExplainCard}{whet one's appetite (for)}[v~phr][C1]
			  \EN{To increase someone's desire for food or for more of something.}
			  \SY{stimulate; pique}
			  \VI{Kích thích vị giác/ham muốn trải nghiệm thêm.}
			  \EX{The aroma \textit{whetted my appetite}.}
			  \EX{A teaser trailer \textit{whetted audiences' appetite for} the series.}
			  \CO{whet sb's appetite; whet appetite for more/for sth}
			\end{ExplainCard}

			\begin{ExplainCard}{fend for oneself}[v~phr][C1]
			  \EN{To look after yourself without help from others.}
			  \SY{manage on one's own; look after oneself}
			  \VI{Tự lo liệu, tự lực cánh sinh.}
			  \EX{Living abroad taught me to \textit{fend for myself}.}
			  \EX{New graduates often \textit{fend for themselves} in big cities.}
			  \CO{learn to fend for oneself; have to fend for yourself}
			\end{ExplainCard}

			\begin{ExplainCard}{bore (sb) stiff}[v~phr][C1]
			  \EN{To make someone extremely bored.}
			  \SY{bore to death; send sb to sleep}
			  \VI{Làm ai chán ngán đến phát ngán.}
			  \EX{Overcooked lectures \textit{bore students stiff}.}
			  \EX{He \textit{bored me stiff} with minutiae about pans.}
			  \CO{bore sb stiff/to death; utterly/completely bored stiff}
			\end{ExplainCard}

			\begin{ExplainCard}{a sense of achievement}[n~phr][B2]
			  \EN{A proud feeling after doing something challenging and worthwhile.}
			  \SY{feeling of accomplishment; pride}
			  \VI{Cảm giác đạt được thành tựu.}
			  \EX{Nailing the recipe gave me \textit{a sense of achievement}.}
			  \EX{Volunteers reported \textit{a strong sense of achievement}.}
			  \CO{feel/experience/give sb a sense of achievement}
			\end{ExplainCard}

			\begin{ExplainCard}{lip-smacking}[adj][B2]
			  \EN{Extremely tasty; making you want to smack your lips.}
			  \SY{delicious; mouth-watering}
			  \VI{Cực ngon; ngon “nhai ngấu nghiến”.}
			  \EX{We shared a \textit{lip-smacking} bowl of noodles.}
			  \EX{A \textit{lip-smacking} sauce tied the dish together.}
			  \CO{lip-smacking noodles/sauce/meal}
			\end{ExplainCard}

			\begin{ExplainCard}{go round}[phr.v][B2]
			  \EN{(BrE) To be enough for everyone to have some.}
			  \SY{be sufficient; go around (AmE)}
			  \VI{Đủ để chia cho mọi người.}
			  \EX{There wasn't enough cake to \textit{go round}.}
			  \EX{Cook extra so the servings will \textit{go round}.}
			  \CO{enough/plenty to go round; make it go round}
			\end{ExplainCard}

			\begin{ExplainCard}{be with child}[idiom][C1]
			  \EN{To be pregnant (formal/old-fashioned).}
			  \SY{be pregnant; be expecting}
			  \VI{Đang mang thai (trang trọng, cổ).}
			  \EX{She discovered she was \textit{with child} in spring.}
			  \EX{Historical diaries note women “\textit{with child}” during shortages.}
			  \CO{be/fall with child}
			\end{ExplainCard}

			\begin{ExplainCard}{to one's heart's content}[idiom][B2]
			  \EN{As much as one wants; to the full.}
			  \SY{to your fill; as much as you like}
			  \VI{Thoả thích; hết mình theo ý muốn.}
			  \EX{At the buffet, we ate \textit{to our heart's content}.}
			  \EX{Visitors can photograph \textit{to their heart's content}.}
			  \CO{eat/shop/rest to one's heart's content}
			\end{ExplainCard}

			\begin{ExplainCard}{to the best of my recollection}[phrase][C1]
			  \EN{If I remember correctly.}
			  \SY{as far as I recall; to the best of my memory}
			  \VI{Nếu tôi nhớ không lầm.}
			  \EX{\textit{To the best of my recollection}, I added fish sauce last.}
			  \EX{\textit{To the best of my recollection}, the café opened in 2019.}
			  \CO{\textit{to the best of my recollection}, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{sweet and sour pork ribs stir-fry}[n~phr][B2]
			  \EN{Pork ribs stir-fried in a tangy sweet-and-sour sauce.}
			  \SY{sweet-and-sour ribs (dish)}
			  \VI{Món sườn xào chua ngọt.}
			  \EX{Her \textit{sweet and sour pork ribs stir-fry} is a family favourite.}
			  \EX{We served \textit{sweet-and-sour ribs} with jasmine rice.}
			  \CO{make/serve/order sweet-and-sour (pork) ribs}
			\end{ExplainCard}

			\begin{ExplainCard}{boiled water morning glory (water spinach)}[n~phr][B2]
			  \EN{Water spinach blanched/boiled and served simply.}
			  \SY{boiled water spinach; blanched water spinach}
			  \VI{Rau muống luộc.}
			  \EX{A plate of \textit{boiled water spinach} balanced the rich meat.}
			  \EX{They blanched \textit{water morning glory} and dipped it in garlic sauce.}
			  \CO{boil/blanch water spinach; a side of boiled water spinach}
			\end{ExplainCard}

			\begin{ExplainCard}{swell with (emotion)}[v~phr][B2]
			  \EN{To be filled with a strong feeling.}
			  \SY{brim with; be filled with}
			  \VI{Ngập tràn (cảm xúc).}
			  \EX{I \textit{swelled with} delight when the dish turned out.}
			  \EX{Parents \textit{swell with} pride at graduation.}
			  \CO{swell with pride/delight/joy}
			\end{ExplainCard}

			\begin{ExplainCard}{leftover}[n][B2]
			  \EN{Food remaining uneaten after a meal.}
			  \SY{remains; leftovers (pl.)}
			  \VI{Đồ ăn thừa sau bữa.}
			  \EX{We packed the \textit{leftovers} for lunch.}
			  \EX{\textit{Leftover} rice makes great fried rice.}
			  \CO{eat/save/reheat leftovers; leftover rice/chicken}
			\end{ExplainCard}

			\begin{ExplainCard}{a dab hand at}[n~phr][C1]
			  \EN{A person who is very skilled at something.}
			  \SY{expert; whiz; ace}
			  \VI{Người rất thạo/rất giỏi việc gì.}
			  \EX{She's \textit{a dab hand at} grilling seafood.}
			  \EX{He proved \textit{a dab hand at} knife work.}
			  \CO{a dab hand at cooking/DIY/baking}
			\end{ExplainCard}

			\begin{ExplainCard}{home-made}[adj][B2]
			  \EN{Made at home rather than bought ready-made.}
			  \SY{homemade; home-cooked}
			  \VI{Nhà làm; nấu tại nhà.}
			  \EX{I prefer \textit{home-made} yogurt.}
			  \EX{\textit{Home-made} meals cut costs and salt.}
			  \CO{home-made bread/jam/meals; deliciously home-made}
			\end{ExplainCard}

			\begin{ExplainCard}{treat (sb) to}[v][B2]
			  \EN{To pay for something enjoyable for someone.}
			  \SY{take sb out for; buy (sb) (sth)}
			  \VI{Chiêu đãi; bao ai một bữa/đi chơi.}
			  \EX{We \textit{treated} our parents \textit{to} a seafood dinner.}
			  \EX{The firm \textit{treated staff to} a year-end banquet.}
			  \CO{treat sb to dinner/a meal/a show}
			\end{ExplainCard}

			\begin{ExplainCard}{sumptuous}[adj][C1]
			  \EN{Impressively rich and expensive-looking (esp.\ food/setting).}
			  \SY{lavish; opulent}
			  \VI{Xa hoa, hoành tráng.}
			  \EX{They hosted a \textit{sumptuous} New Year feast.}
			  \EX{A \textit{sumptuous} banquet welcomed the delegates.}
			  \CO{a sumptuous meal/banquet/feast; sumptuous spread}
			\end{ExplainCard}

			\begin{ExplainCard}{eatery}[n][B2]
			  \EN{A small restaurant or place to eat.}
			  \SY{restaurant; bistro; diner}
			  \VI{Quán ăn/nhà hàng nhỏ.}
			  \EX{We found a cosy \textit{eatery} near campus.}
			  \EX{Street \textit{eateries} stay open late on weekends.}
			  \CO{local/street eatery; popular neighbourhood eatery}
			\end{ExplainCard}

			\begin{ExplainCard}{(for) a change of pace}[idiom][B2]
			  \EN{A switch from the usual routine to keep things fresh.}
			  \SY{for a change; to break the routine}
			  \VI{Đổi gió; thay đổi nhịp quen thuộc.}
			  \EX{We dine out \textit{for a change of pace} on Saturdays.}
			  \EX{The chef rotates menus \textit{for a change of pace}.}
			  \CO{go/try sth for a change of pace; need a change of pace}
			\end{ExplainCard}
		\end{VocabExplain}

    \noindent
    \textbf{Part 2.}
	
	\begin{qa}{Describe an interest or hobby that you enjoy}
	You should say:\\
	\textbullet\ How you became interested in it\\
	\textbullet\ How long you have been doing it\\
	\textbullet\ Why you enjoy it\\
	\textbullet\ and explain what benefits you get from this interest or hobby

	To be honest, I am a big fan of sports, and to be exact, I \textbf{get a kick out of} dancing. So today, I would like to talk about my journey to this hobby. I \textbf{took it up} roughly 3 years ago. \textbf{At that time}, there was a competition called ``Dancing with the stars'' aired on TV. This competition attracted much attention from the public because it was produced with an aim of helping people to \textbf{get into shape}. I also \textbf{went in for} this contest, and fortunately, I seized an opportunity to have a one-week training session with \textbf{leading experts}. They were the people that \textbf{engendered my enthusiasm} for dancing. Although I could not go further in the contest, I \textbf{reaped} a lot of benefits. Dancing creates \textbf{favorable conditions} for me to \textbf{unleash my potential and build my confidence}. In the past, I never thought that dancing was \textbf{my strong suit}, but right now, I can dance to the rhythm and dance with the flow. On top of that, I can \textbf{get the groove on}. I should not forget to mention that dancing is \textbf{an escape for me}. As a \textbf{time-crunched} teacher, I had to cope with stress on a daily basis and dancing allows me to \textbf{achieve a balance between work and rest}. More importantly, without dancing, I could not have a chance to expand my social network with \textbf{like-minded people}.
	\end{qa}

        \begin{VocabExplain}[Part 2]
			\begin{ExplainCard}{get a kick out of}[idiom][B2]
			  \EN{To greatly enjoy something.}
			  \SY{enjoy; take pleasure in; get a thrill from}
			  \VI{Rất thích thú, thấy “khoái” điều gì.}
			  \EX{I \textit{get a kick out of} learning new choreographies.}
			  \EX{Many adults \textit{get a kick out of} dance classes after work (formal).}
			  \CO{get a kick out of music/dancing/trying sth new}
			\end{ExplainCard}

			\begin{ExplainCard}{take (sth) up}[phr.v][B2]
			  \EN{To start a hobby, sport, or regular activity.}
			  \SY{start; pick up; begin}
			  \VI{Bắt đầu (một sở thích/môn học).}
			  \EX{I \textit{took up} dancing three years ago.}
			  \EX{More office workers \textit{take up} exercise to reduce stress (academic).}
			  \CO{take up dancing/yoga/a hobby; recently/seriously take sth up}
			\end{ExplainCard}

			\begin{ExplainCard}{at that time}[phrase][B1]
			  \EN{Then; during the period being mentioned.}
			  \SY{back then; at the time}
			  \VI{Khi đó; vào thời điểm ấy.}
			  \EX{\textit{At that time}, a TV contest made dancing popular.}
			  \EX{The school had no studio \textit{at that time}.}
			  \CO{at that time/in those days; at the time + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{get into shape}[v~phr][B2]
			  \EN{To become physically fit through exercise.}
			  \SY{get fit; get in shape; improve fitness}
			  \VI{Lấy lại/đạt được thể lực tốt; vào form.}
			  \EX{He started jogging to \textit{get into shape}.}
			  \EX{Community programmes help seniors \textit{get into shape} (formal).}
			  \CO{get/stay/keep in shape; try/work to get into shape}
			\end{ExplainCard}

			\begin{ExplainCard}{go in for}[phr.v][C1]
			  \EN{(1) Enter a competition or exam. (2) Be keen on or regularly do something.}
			  \SY{(1) enter \quad (2) be into; be keen on}
			  \VI{(1) Tham gia (kỳ thi/cuộc thi). (2) Thích, thường làm.}
			  \EX{(1) I \textit{went in for} the TV contest.}
			  \EX{(2) Not everyone \textit{goes in for} reality shows.}
			  \EX{(1) Thousands \textit{go in for} national dance trials each year (academic).}
			  \CO{go in for a contest/exam; go in for team sports/outdoor activities}
			\end{ExplainCard}

			\begin{ExplainCard}{leading (expert)}[adj][C1]
			  \EN{Most respected or most important in a particular field.}
			  \SY{top; foremost; eminent}
			  \VI{Hàng đầu; đầu ngành.}
			  \EX{We trained with \textit{leading experts}.}
			  \EX{\textit{Leading} researchers endorse dance for mental health (formal).}
			  \CO{a leading expert/figure/researcher; leading role/authority}
			\end{ExplainCard}

			\begin{ExplainCard}{engender}[v][C1]
			  \EN{To cause or give rise to a feeling or situation.}
			  \SY{spark; generate; foster}
			  \VI{Gây ra/khơi dậy (cảm xúc, tình cảm).}
			  \EX{Their passion \textit{engendered} my enthusiasm for dance.}
			  \EX{Supportive feedback \textit{engenders} persistence in beginners (academic).}
			  \CO{engender enthusiasm/trust/loyalty/interest}
			\end{ExplainCard}

			\begin{ExplainCard}{reap (benefits)}[v][C1]
			  \EN{To obtain advantages as a result of one's effort or situation.}
			  \SY{derive; gain; garner}
			  \VI{Gặt hái/thu được (lợi ích).}
			  \EX{Even without a medal, I \textit{reaped} many benefits.}
			  \EX{Participants \textit{reap} health gains from regular dance (formal).}
			  \CO{reap benefits/rewards/dividends; reap the fruits of}
			\end{ExplainCard}

			\begin{ExplainCard}{favorable conditions}[n~phr][C1]
			  \EN{Circumstances that help something succeed.}
			  \SY{conducive environment; supportive conditions}
			  \VI{Điều kiện thuận lợi.}
			  \EX{The studio created \textit{favorable conditions} for newbies.}
			  \EX{Scholarships provide \textit{favorable conditions} for talent development (academic).}
			  \CO{create/provide/enjoy favorable conditions for sth}
			\end{ExplainCard}

			\begin{ExplainCard}{unleash one's potential}[v~phr][C1]
			  \EN{To allow someone's abilities to be fully expressed.}
			  \SY{unlock potential; fulfil one's potential}
			  \VI{Khai mở/phát huy hết tiềm năng.}
			  \EX{Guidance helped me \textit{unleash my potential}.}
			  \EX{Mentoring programmes \textit{unleash} youth potential (formal).}
			  \CO{unleash/realise/fulfil one's potential; unlock potential}
			\end{ExplainCard}

			\begin{ExplainCard}{build one's confidence}[v~phr][B2]
			  \EN{To increase how sure someone feels about their abilities.}
			  \SY{boost confidence; strengthen self-belief}
			  \VI{Xây dựng/tăng sự tự tin.}
			  \EX{Small wins \textit{built my confidence} on stage.}
			  \EX{Feedback loops \textit{build} learners' \textit{confidence} (academic).}
			  \CO{build/boost confidence; confidence-building activities}
			\end{ExplainCard}

			\begin{ExplainCard}{strong suit}[n~phr][B2]
			  \EN{Something you are especially good at.}
			  \SY{strength; forte; strong point}
			  \VI{Thế mạnh; sở trường.}
			  \EX{I never thought dancing was my \textit{strong suit}.}
			  \EX{Public speaking is his \textit{strong suit} in interviews (formal).}
			  \CO{one's strong suit/point; not be one's strong suit}
			\end{ExplainCard}

			\begin{ExplainCard}{get (one's) groove on}[idiom][B2]
			  \EN{To start dancing or get into a lively rhythm.}
			  \SY{get into the groove; cut loose}
			  \VI{Vào nhịp/“quẩy”; bắt đầu nhảy hứng khởi.}
			  \EX{The DJ dropped the beat and we \textit{got our groove on}.}
			  \EX{Workshops help shy learners \textit{get their groove on} (formal).}
			  \CO{get your groove on; be in the groove; get into the groove}
			\end{ExplainCard}

			\begin{ExplainCard}{escape (for sb)}[n][B2]
			  \EN{A pleasant activity that allows someone to forget stress or problems.}
			  \SY{outlet; release}
			  \VI{Lối thoát/tạm quên áp lực; “điểm tựa” tinh thần.}
			  \EX{Dancing is an \textit{escape for me} after classes.}
			  \EX{Creative hobbies provide an \textit{escape} from burnout (academic).}
			  \CO{an escape from work/stress; find/seek an escape in sth}
			\end{ExplainCard}

			\begin{ExplainCard}{time-crunched}[adj][C1]
			  \EN{Having very little free time; under heavy time pressure.}
			  \SY{time-pressed; time-poor; time-starved}
			  \VI{Thiếu thời gian; bị áp lực thời gian.}
			  \EX{As a \textit{time-crunched} teacher, I plan short sessions.}
			  \EX{\textit{Time-crunched} adults benefit from micro-workouts (academic).}
			  \CO{time-crunched workers/students; a time-crunched schedule}
			\end{ExplainCard}

			\begin{ExplainCard}{achieve/strike a balance between A and B}[v~phr][B2]
			  \EN{To reach a healthy middle point between two competing needs.}
			  \SY{strike a balance; maintain balance}
			  \VI{Đạt được/cân bằng giữa hai nhu cầu.}
			  \EX{Dance helps me \textit{achieve a balance between work and rest}.}
			  \EX{Policies aim to \textit{strike a balance} between growth and wellbeing (formal).}
			  \CO{achieve/strike/maintain a balance between work and life/study and rest}
			\end{ExplainCard}

			\begin{ExplainCard}{like-minded (people)}[adj][B2]
			  \EN{Having similar interests, opinions, or goals.}
			  \SY{of the same mind; kindred; compatible}
			  \VI{Cùng chí hướng/sở thích; hợp gu.}
			  \EX{Classes helped me meet \textit{like-minded people}.}
			  \EX{Networks of \textit{like-minded} creators collaborate online (academic).}
			  \CO{like-minded people/friends/peers; find/build a like-minded community}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
	\begin{qa}{Do you think having a hobby is good for people's social life? In what way?}
	Given the fact that life is getting more \textbf{hectic}, and people are under constant stress, pursuing a personal hobby can really \textbf{do wonders} for people's health. This will enable people to \textbf{blow off some steam} and recharge energy after \textbf{eight solid hours} at their \textbf{nine-to-five jobs}. Moreover, people who have similar interests can \textbf{expand their circle of friends} and build their \textbf{network of contacts}.
	\end{qa}

	\begin{qa}{Are there any negative effects of a person spending too much time on their hobby? What are they?}
	Oh, yes. Enjoying a \textbf{pastime} can have both \textbf{pros and cons}. In terms of the \textbf{downsides}, \textbf{excessive} amounts of time spent on leisure activities can have \textbf{detrimental effects} on people's life. They \textbf{might end up being} deprived of time for other \textbf{priorities} such as their family and friends. Besides, some \textbf{recreational} activities like playing video games and \textbf{boozing} are not really healthy. \textbf{Overindulgence} in the virtual world and alcohol might be \textbf{catalysts} for other problems \textbf{down the line}, for instance, obesity or liver cancer.
	\end{qa}

	\begin{qa}{Why do you think people need to have an interest or hobby?}
	Well, for the most part, developing an interest or hobby is \textbf{a must} to life. One \textbf{compelling} reason is that this may act as a source of pleasure and help to \textbf{alleviate intense stress}. Spending time for hobbies seems endless fun so it may help them \textbf{recover} their energy. Another \textbf{justification} is that leisure pursuits are effective ways for people to identify themselves \textbf{prodigious} talents such as singing or dancing. What I mean here is that people can discover their innate talents thanks to their \textbf{devoting time} to a hobby.
	\end{qa}

	\begin{qa}{In your country, how much time do people spend on work and in leisure? Is this a good balance, do you think?}
	There is \textbf{no-size-fits-all} answer to this question because it is dependent on different factors, according to my \textbf{time budget} I presume. Judging from my own experience, people are \textbf{inclined to have a blast} on the weekends or on holidays. That is pretty \textbf{reasonable} because everyone is \textbf{entitled} to have short breaks to \textbf{revitalize} their energy after \textbf{keeping their nose to the grindstone}. More importantly, once people's health is in good condition, they would feel more \textbf{productive} and this would lead to increased productivity.
	\end{qa}

	\begin{qa}{Would you say the amount of free time has changed much in the last fifty years?}
	I would say yes, and this can be attributed to technological \textbf{strides}. Over half a century, a boom in technological innovations has \textbf{revolutionized} our lives in overall. \textbf{Energy-efficient appliances} like dishwashers and washing machines have made household chores become \textbf{a piece of cake}. Digital shopping and \textbf{teleworking} are another two breakthroughs that \textbf{cut the time for commuting}. So, compared to the past, people nowadays can save more time for themselves, so they have more \textbf{me time}.
	\end{qa}

	\begin{qa}{Do you think people will have more or less free time in the future? Why?}
	Undoubtedly, with the rapid change of science and technology, \textbf{automation} will \textbf{marginalize human involvement little by little} in daily tasks such as carrying out \textbf{domestic tasks} or \textbf{running errands}. It might sound ambitious but still \textbf{justifiable}, and people will enjoy more free time than ever before, I suppose.
	\end{qa}

        \begin{VocabExplain}[Part 3]
			\begin{ExplainCard}{hectic}[adj][B2]
			  \EN{Very busy and full of activity.}
			  \SY{frantic; jam-packed; frenetic}
			  \VI{Bận rộn dồn dập.}
			  \EX{Weekdays are \textit{hectic}, so I unwind at the weekend.}
			  \EX{Urban schedules grow more \textit{hectic} during peak seasons.}
			  \CO{a hectic day/schedule/life; get hectic}
			\end{ExplainCard}

			\begin{ExplainCard}{do wonders (for)}[idiom][B2]
			  \EN{Have a very good effect on something.}
			  \SY{work miracles; do a world of good}
			  \VI{Tác dụng tuyệt vời; rất có ích.}
			  \EX{A short walk can \textit{do wonders for} your mood.}
			  \EX{Regular leisure time \textit{does wonders for} well-being.}
			  \CO{do wonders for health/skin/productivity}
			\end{ExplainCard}

			\begin{ExplainCard}{blow off (some) steam}[idiom][B2]
			  \EN{Release stress or strong feelings.}
			  \SY{let off steam; unwind}
			  \VI{Xả stress; giải toả bực dọc.}
			  \EX{We play badminton to \textit{blow off steam}.}
			  \EX{After exams, students \textit{blow off steam} with club events.}
			  \CO{blow/let off steam by V-ing}
			\end{ExplainCard}

			\begin{ExplainCard}{X solid hours}[n~phr][B2]
			  \EN{A continuous, uninterrupted period of X hours.}
			  \SY{straight; uninterrupted}
			  \VI{Liền mạch X giờ không ngắt quãng.}
			  \EX{He studied for \textit{eight solid hours}.}
			  \EX{We drove \textit{four solid hours} before stopping.}
			  \CO{work/study for \# solid hours/days}
			\end{ExplainCard}

			\begin{ExplainCard}{nine-to-five job}[n~phr][B1]
			  \EN{A regular office job with standard daytime hours.}
			  \SY{desk job; regular office job}
			  \VI{Công việc giờ hành chính.}
			  \EX{I left my \textit{nine-to-five job} to freelance.}
			  \EX{Many \textit{nine-to-five jobs} now allow hybrid work.}
			  \CO{a typical/steady nine-to-five; work a nine-to-five}
			\end{ExplainCard}

			\begin{ExplainCard}{expand one's circle of friends}[v~phr][B2]
			  \EN{Increase the number of friends you socialize with.}
			  \SY{broaden your social circle; make new friends}
			  \VI{Mở rộng vòng bạn bè.}
			  \EX{Joining a choir helped me \textit{expand my circle of friends}.}
			  \EX{Clubs enable newcomers to \textit{expand their circle}.}
			  \CO{expand/widen/broaden one's circle (of friends)}
			\end{ExplainCard}

			\begin{ExplainCard}{network of contacts}[n][C1]
			  \EN{A group of people you know and can reach for support or opportunities.}
			  \SY{professional network; connections}
			  \VI{Mạng lưới quan hệ.}
			  \EX{Volunteering grew my \textit{network of contacts}.}
			  \EX{Graduates build a \textit{network of contacts} through internships.}
			  \CO{build/maintain/expand a network of contacts}
			\end{ExplainCard}

			\begin{ExplainCard}{pastime}[n][B2]
			  \EN{An activity done regularly for enjoyment.}
			  \SY{hobby; leisure activity}
			  \VI{Sở thích; thú tiêu khiển.}
			  \EX{Reading is my favourite \textit{pastime}.}
			  \EX{Popular \textit{pastimes} shift with technology.}
			  \CO{favourite/common pastime; engage in a pastime}
			\end{ExplainCard}

			\begin{ExplainCard}{pros and cons}[n~pl][B2]
			  \EN{The advantages and disadvantages of something.}
			  \SY{upsides and downsides; merits and drawbacks}
			  \VI{Ưu và nhược điểm.}
			  \EX{We weighed the \textit{pros and cons} of night classes.}
			  \EX{Policies list \textit{pros and cons} for transparency.}
			  \CO{weigh/list/balance the pros and cons}
			\end{ExplainCard}

			\begin{ExplainCard}{downside}[n][B2]
			  \EN{A disadvantage or negative aspect.}
			  \SY{drawback; disadvantage}
			  \VI{Điểm bất lợi; hạn chế.}
			  \EX{The \textit{downside} of streaming is distraction.}
			  \EX{A key \textit{downside} is higher maintenance costs.}
			  \CO{a major/key downside; the downside is that + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{excessive}[adj][C1]
			  \EN{More than is necessary or reasonable.}
			  \SY{undue; disproportionate; overmuch}
			  \VI{Quá mức; quá đà.}
			  \EX{\textit{Excessive} screen time hurts sleep.}
			  \EX{\textit{Excessive} workloads undermine morale.}
			  \CO{excessive use/consumption/noise/force}
			\end{ExplainCard}

			\begin{ExplainCard}{detrimental effects}[n~phr][C1]
			  \EN{Harmful impacts or outcomes.}
			  \SY{adverse effects; damaging effects}
			  \VI{Tác hại; ảnh hưởng tiêu cực.}
			  \EX{Late-night gaming has \textit{detrimental effects} on focus.}
			  \EX{Noise shows \textit{detrimental effects} on learning.}
			  \CO{have/show/pose detrimental effects on}
			\end{ExplainCard}

			\begin{ExplainCard}{might end up (being/doing)}[v~phr][B2]
			  \EN{To eventually become or result in something, often unintentionally.}
			  \SY{wind up; turn out}
			  \VI{Rốt cuộc trở thành/dẫn đến.}
			  \EX{Spend too long online and you \textit{might end up} isolated.}
			  \EX{Poor pacing \textit{ends up} reducing overall output.}
			  \CO{end up V-ing/Adj/N}
			\end{ExplainCard}

			\begin{ExplainCard}{priority}[n][B2]
			  \EN{Something considered more important than others.}
			  \SY{chief concern; main focus}
			  \VI{Ưu tiên hàng đầu.}
			  \EX{Family time is my \textit{priority}.}
			  \EX{Safety remains the top \textit{priority}.}
			  \CO{set/define/shift priorities; top/high priority}
			\end{ExplainCard}

			\begin{ExplainCard}{recreational}[adj][B2]
			  \EN{Related to leisure and enjoyment, not work.}
			  \SY{leisure; non-work}
			  \VI{Thuộc giải trí.}
			  \EX{\textit{Recreational} sports reduce stress.}
			  \EX{\textit{Recreational} facilities attract residents.}
			  \CO{recreational activities/areas/drugs}
			\end{ExplainCard}

			\begin{ExplainCard}{boozing}[n][C1]
			  \EN{Informal: drinking alcohol, often heavily.}
			  \SY{drinking; binge drinking}
			  \VI{Uống rượu bia (thường quá đà).}
			  \EX{Cut down the \textit{boozing} on weeknights.}
			  \EX{\textit{Boozing} is linked to sleep disruption.}
			  \CO{late-night boozing; curb/avoid boozing}
			\end{ExplainCard}

			\begin{ExplainCard}{overindulgence}[n][C1]
			  \EN{Consuming or doing something too much.}
			  \SY{excess; overconsumption}
			  \VI{Quá đà; sa đà.}
			  \EX{\textit{Overindulgence} in games harms grades.}
			  \EX{Holiday \textit{overindulgence} raises health risks.}
			  \CO{overindulgence in alcohol/sugar/social media}
			\end{ExplainCard}

			\begin{ExplainCard}{catalyst (for)}[n][C1]
			  \EN{A person or thing that quickly causes change.}
			  \SY{trigger; spark}
			  \VI{Chất xúc tác; tác nhân kích hoạt.}
			  \EX{Stress can be a \textit{catalyst for} burnout.}
			  \EX{A good mentor is a \textit{catalyst} for growth.}
			  \CO{a catalyst for change/problems/growth}
			\end{ExplainCard}

			\begin{ExplainCard}{down the line}[idiom][B2]
			  \EN{Later in the future; eventually.}
			  \SY{down the road; in the long run}
			  \VI{Về sau; sau này.}
			  \EX{Tiny habits pay off \textit{down the line}.}
			  \EX{Overuse causes issues \textit{down the line}.}
			  \CO{problems/benefits down the line}
			\end{ExplainCard}

			\begin{ExplainCard}{a must}[n][B2]
			  \EN{Something essential or strongly recommended.}
			  \SY{essential; necessity}
			  \VI{Điều bắt buộc/phải có.}
			  \EX{For me, a hobby is \textit{a must}.}
			  \EX{Safety training is \textit{a must} for lab work.}
			  \CO{a must for sb; an absolute must}
			\end{ExplainCard}

			\begin{ExplainCard}{compelling}[adj][C1]
			  \EN{Powerfully convincing or very interesting.}
			  \SY{persuasive; cogent; forceful}
			  \VI{Thuyết phục; hấp dẫn mạnh.}
			  \EX{She gave a \textit{compelling} reason to join.}
			  \EX{Data present a \textit{compelling} case for reform.}
			  \CO{a compelling case/argument/story}
			\end{ExplainCard}

			\begin{ExplainCard}{alleviate (intense) stress}[v~phr][C1]
			  \EN{Reduce the severity of stress.}
			  \SY{ease; mitigate; lessen}
			  \VI{Giảm bớt căng thẳng.}
			  \EX{Breathing drills \textit{alleviate stress}.}
			  \EX{Green spaces \textit{alleviate} urban stressors.}
			  \CO{alleviate stress/anxiety/burden}
			\end{ExplainCard}

			\begin{ExplainCard}{recover (energy)}[v][B2]
			  \EN{Regain strength or energy after effort.}
			  \SY{bounce back; recuperate}
			  \VI{Hồi phục sức/động lực.}
			  \EX{A short nap helps me \textit{recover}.}
			  \EX{Athletes \textit{recover} faster with proper sleep.}
			  \CO{recover energy/health; recovery period}
			\end{ExplainCard}

			\begin{ExplainCard}{justification}[n][C1]
			  \EN{A good reason or explanation for something.}
			  \SY{rationale; grounds}
			  \VI{Lý do chính đáng; cơ sở.}
			  \EX{What's the \textit{justification} for the fee?}
			  \EX{The study offers clear \textit{justification} for action.}
			  \CO{provide/offer a justification for; lack justification}
			\end{ExplainCard}

			\begin{ExplainCard}{prodigious (talent)}[adj][C1]
			  \EN{Remarkably great or impressive in ability or size.}
			  \SY{exceptional; outstanding; remarkable}
			  \VI{Phi thường; xuất chúng.}
			  \EX{She showed \textit{prodigious} rhythm at 10.}
			  \EX{\textit{Prodigious} talent benefits from early support.}
			  \CO{prodigious talent/ability/memory}
			\end{ExplainCard}

			\begin{ExplainCard}{devote time (to)}[v~phr][B2]
			  \EN{Give a lot of time and effort to something.}
			  \SY{dedicate; allocate; commit (time)}
			  \VI{Dành thời gian (cho).}
			  \EX{I \textit{devote time to} practice nightly.}
			  \EX{Students should \textit{devote time} to rest as well.}
			  \CO{devote time/energy/attention to}
			\end{ExplainCard}

			\begin{ExplainCard}{no one-size-fits-all}[idiom][B2]
			  \EN{No single solution works for everyone.}
			  \SY{case-by-case; tailored approach}
			  \VI{Không có công thức chung cho tất cả.}
			  \EX{Work–life balance is \textit{no one-size-fits-all}.}
			  \EX{Policies need \textit{no one-size-fits-all} humility.}
			  \CO{a one-size-fits-all solution/approach (often negated)}
			\end{ExplainCard}

			\begin{ExplainCard}{time budget}[n][C1]
			  \EN{A planned allocation of one's available time.}
			  \SY{time allocation; schedule}
			  \VI{Ngân sách thời gian; phân bổ thời gian.}
			  \EX{Track tasks to manage your \textit{time budget}.}
			  \EX{Teams set a weekly \textit{time budget} for meetings.}
			  \CO{set/plan/adjust a time budget}
			\end{ExplainCard}

			\begin{ExplainCard}{be inclined to have a blast}[idiom][B2]
			  \EN{Tend to have a lot of fun.}
			  \SY{tend to enjoy; be likely to have fun}
			  \VI{Thường “quẩy”/vui chơi hết mình.}
			  \EX{Students are \textit{inclined to have a blast} after exams.}
			  \EX{Festival-goers \textit{are inclined to have a blast} on weekends.}
			  \CO{have a blast at/with; be inclined to V}
			\end{ExplainCard}

			\begin{ExplainCard}{reasonable}[adj][B2]
			  \EN{Fair and sensible; logical.}
			  \SY{fair; sensible; rational}
			  \VI{Hợp lý.}
			  \EX{It's \textit{reasonable} to take breaks.}
			  \EX{\textit{Reasonable} limits protect staff well-being.}
			  \CO{a reasonable request/price/assumption}
			\end{ExplainCard}

			\begin{ExplainCard}{entitled (to)}[adj][C1]
			  \EN{Having the right to do or have something.}
			  \SY{authorized; eligible}
			  \VI{Có quyền; được hưởng.}
			  \EX{Employees are \textit{entitled to} annual leave.}
			  \EX{Citizens are \textit{entitled} to access public data.}
			  \CO{be entitled to benefits/leave/compensation}
			\end{ExplainCard}

			\begin{ExplainCard}{revitalize}[v][C1]
			  \EN{Give new energy or life to something.}
			  \SY{reenergize; reinvigorate; refresh}
			  \VI{Hồi sinh; tiếp sức.}
			  \EX{A short run \textit{revitalized} me.}
			  \EX{Parks can \textit{revitalize} city centres.}
			  \CO{revitalize energy/spaces/communities; revitalization}
			\end{ExplainCard}

			\begin{ExplainCard}{keep one's nose to the grindstone}[idiom][C1]
			  \EN{Work very hard for a long time.}
			  \SY{toil away; slog away}
			  \VI{Cặm cụi làm việc không ngơi.}
			  \EX{She \textit{kept her nose to the grindstone} all term.}
			  \EX{After months \textit{at the grindstone}, take a break.}
			  \CO{keep/put one's nose to the grindstone}
			\end{ExplainCard}

			\begin{ExplainCard}{productive}[adj][B2]
			  \EN{Producing good results; efficient.}
			  \SY{efficient; fruitful}
			  \VI{Năng suất; hiệu quả.}
			  \EX{I'm most \textit{productive} before noon.}
			  \EX{Quiet hours boost \textit{productive} work.}
			  \CO{highly/less productive; a productive day/session}
			\end{ExplainCard}

			\begin{ExplainCard}{(make) strides}[n~pl][C1]
			  \EN{Significant progress or advances.}
			  \SY{advances; breakthroughs; progress}
			  \VI{Bước tiến lớn.}
			  \EX{Tech has made huge \textit{strides}.}
			  \EX{Cities are making \textit{strides} in transit.}
			  \CO{make/mark/record major strides}
			\end{ExplainCard}

			\begin{ExplainCard}{revolutionize}[v][C1]
			  \EN{To change something completely and fundamentally.}
			  \SY{transform; overhaul}
			  \VI{Cách mạng hoá; thay đổi tận gốc.}
			  \EX{Smartphones \textit{revolutionized} habits.}
			  \EX{AI could \textit{revolutionize} healthcare delivery.}
			  \CO{revolutionize industry/education/workflows}
			\end{ExplainCard}

			\begin{ExplainCard}{energy-efficient appliances}[n~phr][B2]
			  \EN{Devices that perform tasks using less energy.}
			  \SY{energy-saving devices; efficient machines}
			  \VI{Thiết bị tiết kiệm năng lượng.}
			  \EX{\textit{Energy-efficient appliances} cut bills.}
			  \EX{Standards promote \textit{energy-efficient appliances}.}
			  \CO{buy/use/install energy-efficient appliances}
			\end{ExplainCard}

			\begin{ExplainCard}{a piece of cake}[idiom][B1]
			  \EN{Very easy to do.}
			  \SY{a breeze; easy as pie}
			  \VI{Dễ như chơi.}
			  \EX{With a mixer, kneading is \textit{a piece of cake}.}
			  \EX{Online renewal is now \textit{a piece of cake}.}
			  \CO{be/feel like a piece of cake}
			\end{ExplainCard}

			\begin{ExplainCard}{teleworking}[n][B2]
			  \EN{Working remotely using digital communication tools.}
			  \SY{remote work; telecommuting}
			  \VI{Làm việc từ xa.}
			  \EX{\textit{Teleworking} saves commute time.}
			  \EX{Many firms expand \textit{teleworking} options.}
			  \CO{shift to/enable teleworking; teleworking policy}
			\end{ExplainCard}

			\begin{ExplainCard}{cut the time for commuting}[v~phr][B2]
			  \EN{Reduce the time spent traveling to work.}
			  \SY{shorten commute time; reduce commuting}
			  \VI{Rút ngắn thời gian đi lại.}
			  \EX{Flexible hours \textit{cut commute time}.}
			  \EX{Transit upgrades \textit{cut the time for commuting}.}
			  \CO{cut/reduce commute time by \# minutes}
			\end{ExplainCard}

			\begin{ExplainCard}{me time}[n][B2]
			  \EN{Time reserved for oneself to relax or pursue personal interests.}
			  \SY{personal time; downtime}
			  \VI{Thời gian cho riêng mình.}
			  \EX{I block Sunday morning as \textit{me time}.}
			  \EX{Planners help people protect \textit{me time}.}
			  \CO{have/need/protect me time; carve out me time}
			\end{ExplainCard}

			\begin{ExplainCard}{automation}[n][C1]
			  \EN{Using machines or software to perform tasks with little human input.}
			  \SY{mechanization; computerization}
			  \VI{Tự động hoá.}
			  \EX{\textit{Automation} handles routine billing.}
			  \EX{\textit{Automation} reshapes entry-level jobs.}
			  \CO{process/office automation; automation of tasks}
			\end{ExplainCard}

			\begin{ExplainCard}{marginalize human involvement little by little}[v~phr][C1]
			  \EN{Gradually reduce the role or need for people in a process.}
			  \SY{displace; phase out; reduce reliance on humans}
			  \VI{Từng bước thu hẹp vai trò con người.}
			  \EX{Smart checkouts \textit{marginalize human involvement} in retail.}
			  \EX{Algorithms \textit{little by little} replace manual screening.}
			  \CO{marginalize human roles/input; happen little by little}
			\end{ExplainCard}

			\begin{ExplainCard}{domestic tasks}[n~phr][B2]
			  \EN{Household chores and home-related duties.}
			  \SY{household chores; housework}
			  \VI{Việc nhà; công việc nội trợ.}
			  \EX{Robots assist with \textit{domestic tasks}.}
			  \EX{Time-use data track unpaid \textit{domestic tasks}.}
			  \CO{share/split domestic tasks; routine domestic tasks}
			\end{ExplainCard}

			\begin{ExplainCard}{run errands}[v~phr][B2]
			  \EN{Make short trips to do small tasks (e.g., buy items, post mail).}
			  \SY{do errands; pop out for errands}
			  \VI{Chạy việc lặt vặt.}
			  \EX{I \textit{run errands} on Saturday mornings.}
			  \EX{Apps help seniors \textit{run errands} efficiently.}
			  \CO{run daily/quick errands; errand-running}
			\end{ExplainCard}

			\begin{ExplainCard}{justifiable}[adj][C1]
			  \EN{Able to be defended as reasonable or valid.}
			  \SY{defensible; reasonable}
			  \VI{Chính đáng; hợp lẽ.}
			  \EX{The fee increase is \textit{justifiable} with better service.}
			  \EX{Overtime is \textit{justifiable} during emergencies.}
			  \CO{a justifiable reason/cost; be justifiable on grounds of}
			\end{ExplainCard}
        \end{VocabExplain}
		\begin{VocabHighlights}
		\VH{There's no accounting for taste}{(proverb) it is impossible to explain why different people like different things}{(tục ngữ) mỗi người có 1 sở thích khác nhau}
		\VH{broth}{(n) thick soup made by boiling meat or fish and vegetables in water}{(danh từ) nước dùng}
		\VH{to be piping hot}{(phrase) to be very hot}{(cụm từ) rất nóng}
		\VH{streaming}{(adj) vaporizing}{(tính từ) bốc hơi nghi ngút}
		\VH{to be appetizing}{(adj) to be delicious}{(tính từ) ngon}
		\VH{to take a whack at}{(idiom) to try}{(thành ngữ) thử}
		\VH{succulent}{(adj) containing a lot of juice and tasting good}{(tính từ) mọng nước}
		\VH{crunchy}{(adj) firm and crisp and making a sharp sound when you bite or crush it}{(tính từ) cứng và giòn}
		\VH{to whet one's appetite}{(phrase) to make one hungry}{(cụm từ) làm ai thèm thuồng}
		\VH{to fend for oneself}{(phrase) look after and provide for oneself, without any help from others}{(cụm từ) tự lực cánh sinh}
		\VH{to bore somebody stiff}{(phrase) to make somebody feel exceedingly dull and uninterested}{(cụm từ) làm ai phát ngán ngẩm}
		\VH{a sense of achievement}{(phrase) a proud feeling of having done something difficult and worthwhile}{(cụm từ) cảm giác đạt được thành tựu}
		\VH{lip-smacking}{(adj) tasting extremely good}{(tính từ) cực ngon}
		\VH{to go round}{(phr. v) to be enough for everyone to have one or some}{(cụm động từ) đủ để phân phát}
		\VH{to be with child}{(idiom) to be pregnant}{(thành ngữ) có thai}
		\VH{to one's hearts' content}{(idiom) do it as much as you want}{(thành ngữ) tận hưởng nhiều nhất có thể}
		\VH{to the best of my recollection}{(phrase) if i remember correctly}{(cụm từ) nếu tôi nhớ đúng thì}
		\VH{sweet and sour pork ribs stir-fry}{(phrase) stir-fried pork ribs that have the sweet and sour flavors}{(cụm từ) sườn xào chua ngọt}
		\VH{boiled water morning glory}{(phrase) water morning glory is boiled for eating}{(cụm từ) rau muống luộc}
		\VH{to swell with}{(idiom) to become filled with some emotion}{(thành ngữ) ngập tràn cảm xúc}
		\VH{leftover}{(n) food that has not been eaten at the end of a meal}{(danh từ) thức ăn thừa}
		\VH{a dab hand at}{(n) a person who is an expert at a particular activity}{(danh từ) người giỏi, khéo làm gì}
		\VH{home-made}{(adj) made at home, rather than produced in a factory and bought in a shop/store}{(tính từ) đồ nhà tự làm}
		\VH{to treat somebody to}{(v) to pay for something that somebody/you will enjoy and that you do not usually have or do}{(động từ) chiêu đãi}
		\VH{sumptuous}{(adj) (food) looking impressive and expensive}{(tính từ) (chỉ món ăn) trông có vẻ nhiều và đắt}
		\VH{eatery}{(n) restaurant}{(danh từ) nhà hàng}
		\VH{(for) a change of pace}{(idiom) a change from what one is used to}{(thành ngữ) đổi gió}
		\VH{to get a kick out of}{(idiom) to get a sense of enjoyment, amusement or excitement from something}{(thành ngữ) hứng thú, yêu thích công việc gì đó}
		\VH{to take up (a hobby)}{(phr.v) start to follow something as a hobby}{(cụm động từ) theo đuổi đam mê}
		\VH{to get into shape}{(phrase) to become physically fitter by exercise}{(thành ngữ) giữ dáng}
		\VH{to go in for}{(phr.v) take part in}{(cụm động từ) tham gia}
		\VH{to engender}{(v) make people have a particular feeling or make a situation start to exist}{(động từ) gây ra}
		\VH{to reap}{(v) gain something}{(động từ) thu được}
		\VH{favorable conditions}{(phrase) conditions are good for something to happen}{(cụm từ) điều kiện thuận lợi}
		\VH{to unleash my potential}{(phrase) to achieve the standard that you are capable of}{(cụm từ) giải phóng tiềm năng}
		\VH{to build my confidence}{(phrase) help improve or boost your confidence levels}{(cụm từ) xây dựng sự tự tin vào bản thân}
		\VH{my strong suit}{(idiom) a particular skill or ability that I have}{(thành ngữ) điểm mạnh}
		\VH{to get the groove on}{(idiom) to let loose and enjoy}{(thành ngữ) thả lỏng và thư giãn}
		\VH{an escape}{(n) the act of getting free from something, or to avoid something}{(danh từ) sự trốn khỏi}
		\VH{time-crunched}{(adj) short of time}{(tính từ) thiếu thời gian}
		\VH{to achieve a balance between work and rest}{(phrase) to keep a balance between job and life}{(cụm từ) cân bằng công việc và cuộc sống}
		\VH{like-minded people}{(idiom) having the same opinions}{(thành ngữ) người cùng chí hướng}
		\VH{hectic}{(adj) full of activity, or very busy and fast}{(tính từ) bận rộn}
		\VH{to do wonders for}{(idiom) to cause improvements or have a very good effect}{(thành ngữ) có lợi cho}
		\VH{blow off (some) steam}{(idiom) to do or say something that helps you to get rid of strong feelings or energy}{(thành ngữ) xả stress}
		\VH{eight solid hours}{(phrase) the amount of time you work at the office}{(cụm từ) 8 giờ làm việc}
		\VH{nine-to-five jobs}{(phrase) a normal and routine job}{(cụm từ) một công việc hành chính}
		\VH{to expand social circle}{(phrase) to expand their social circle}{(cụm từ) mở rộng mối quan hệ xã hội}
		\VH{network of contacts}{(phrase) the relationships of every single person}{(cụm từ) các mối quan hệ xã hội}
		\VH{a pastime}{(n) an activity that is done for enjoyment}{(danh từ) trò tiêu khiển}
		\VH{pros and cons}{(phrase) advantages and disadvantages}{(cụm từ) ưu điểm và nhược điểm}
		\VH{downside}{(n) a disadvantage of a situation}{(danh từ) bất lợi, nhược điểm}
		\VH{excessive}{(adj) too much}{(tính từ) quá nhiều, vượt quá mức thông thường}
		\VH{detrimental}{(adj) harmful}{(tính từ) có hại}
		\VH{to end up}{(phrasal verb) to finally be in a particular place or situation}{(cụm động từ) kết cục là}
		\VH{priorities}{(n) things that are very important and must be dealt with before other things}{(danh từ) các ưu tiên}
		\VH{recreational}{(adj) connected with activities that people do for enjoyment when they are not working}{(tính từ) có tính giải trí}
		\VH{to booze}{(v) drink alcohol, especially in large quantities}{(động từ) uống nhiều rượu bia}
		\VH{overindulgence}{(n) the action or fact of having too much of something enjoyable}{(danh từ) sự nuông chiều}
		\VH{catalyst}{(n) a person or thing that causes a change}{(danh từ) nguyên nhân}
		\VH{down the line}{(idiom) later, after an activity or situation has been continuing for a period of time}{(thành ngữ) về sau này}
		\VH{a must}{(n) something that you must see or do}{(danh từ) điều bắt buộc}
		\VH{compelling}{(adj) that makes you pay attention to it because it is so interesting and exciting}{(tính từ) hấp dẫn}
		\VH{to alleviate}{(v) to make something less severe}{(động từ) làm dịu, giảm bớt}
		\VH{to intense}{(adj) very great, very strong}{(tính từ) rất mạnh, nhiều}
		\VH{justification}{(n) a good reason why something exists or is done}{(danh từ) sự lý lẽ, biện luận}
		\VH{prodigious}{(adj) marvelous natural abilities to do something well}{(tính từ) thuộc về tài năng thiên tài}
		\VH{reasonable}{(adj) fair, practical and sensible}{(tính từ) hợp lý}
		\VH{to be inclined to V-inf}{(p2) to tend to think or behave in a particular way; to make somebody do this}{(phần từ 2) có xu hướng làm gì}
		\VH{to have a blast}{(idiom) to have a very fun or exciting time}{(thành ngữ) có khoảng thời gian rất vui}
		\VH{to be entitled to V-inf}{(p2) feeling that you have a right to the good things in life without necessarily having to work for them}{(phần từ 2) được quyền (làm gì…)}
		\VH{to revitalize}{(v) to make something stronger, more active and healthy}{(động từ) làm phục hồi, khỏe mạnh hơn}
		\VH{to keep/put one's nose to the grindstone}{(idom) to work hard and continuously}{(thành ngữ) làm việc chăm chỉ liên tục}
		\VH{productive}{(adj) doing or achieving a lot}{(tính từ) năng suất, hiệu quả}
		\VH{to revolutionize}{(v) to completely change the way that something is done}{(động từ) thay đổi, cách mạng hóa}
		\VH{energy-efficient appliances}{(phrase) household machines and devices that help to save energy}{(cụm từ) thiết bị tiết kiệm năng lượng}
		\VH{a piece of cake}{(idom) a thing that is very easy to do}{(thành ngữ) dễ dàng}
		\VH{teleworking}{(n) the practice of working from home, communicating with your office and customers by phones or emails, etc}{(danh từ) làm việc từ xa}
		\VH{me time}{(phrase) the time a person has for their own enjoyment to schedule relaxing appointments or activities}{(cụm từ) thời gian dành cho hoạt động vui chơi giải trí cá nhân}
		\VH{automation}{(n) the use of machines to do work that is previously done by people}{(danh từ) sự tự động hóa}
		\VH{little by little}{(idiom) gradually}{(thành ngữ) dần dần}
		\VH{to marginalize}{(v) to make somebody feel as if they are not important and cannot influence decisions or events; to put somebody in a position in which they have no power}{(động từ) hạ thấp vai trò của cái gì đó}
		\VH{human involvement}{(phrase) human participation}{(cụm từ) sự tham gia của con người}
		\VH{domestic tasks}{(noun) a piece of work belonging or relating to the home, house, or family}{(danh từ) việc nhà}
		\VH{running errands}{(phrase) to go out to buy or do something}{(cụm từ) chạy việc vặt}
		\VH{justifiable}{(adj) existing or done for a good reason, and therefore acceptable}{(tính từ) hợp lý, chính đáng}
    \end{VocabHighlights}

    \end{test}

    \begin{test}{TEST 3}
    \noindent
    \textbf{Part 1. Leisure}
	\begin{qa}{Do you have any hobbies or interests? [What are they?]}
	Yes of course. I have a number of hobbies and interests that are \textbf{like no other}. Firstly, I have \textbf{a liking for} football, especially Manchester United, one of the biggest football clubs worldwide. I have been supporting this club for almost \textbf{a quarter of the century}. Secondly, I have \textbf{a fondness for} reading comic books, Japanese manga in particular. This interest of mine \textbf{dates back to} over 20 years ago when I was at primary school. Last but not least, I am a hardcore metal fan. I can listen to emphatic beats, aggressive rhythms and \textbf{amplified distortion} of such international bands as Linkin Park, Metallica, X Japan or Vietnamese bands like Buc Tuong and Microwave tirelessly.
	\end{qa}

	\begin{qa}{How did you become interested in (whatever hobby/interest the candidate mentions)?}
	Three of my \textbf{aforementioned} interests reflect mixed origins. The first interest was \textbf{ignited} when I first watched Manchester United in their \textbf{heyday} with David Beckham on their right wing crossing and delivering free-kicks with \textbf{unerring} accuracy. The second one was \textbf{kindled} after I found numerous underlying moral lessons about love, friendship, etc.\ in each chapter of a manga. In addition, the last one was drawn after I \textbf{overheard} a metal song “Tâm hồn của đá” or “The Soul of Rock” by Bức Tường. I was pleasantly \textbf{taken aback} that the loudness of this music genre could help me \textbf{go into raptures} after a hard-working day at school a long time ago.
	\end{qa}

	\begin{qa}{What is there to do in your free time (in candidate's hometown/village)?}
	When I have time to spare, say, I often \textbf{hit the sack} quite late to watch live football matches which are frequently broadcast at night due to different time zones. I also \textbf{chill out} by \textbf{binge reading} manga books. Besides, I also \textbf{kick back} by setting the music volume at max level on the loudspeaker and singing along. Moreover, I often drive my family to malls nearby for a \textbf{shopping spree} monthly.
	\end{qa}

	\begin{qa}{How do you usually spend your holidays?}
	As \textbf{all and sundry is inclined} to leave the city on short holiday breaks, I also \textbf{keep up with the Joneses} by booking at resorts located throughout Vietnam to enjoy our time \textbf{off duty}. I \textbf{take great delight in} taking my family with me to different destinations for \textbf{a chance of pace}. Another activity I \textbf{engage in} is \textbf{dropping in on} my extended family as well as distant relatives to \textbf{cement} our family relationship.
	\end{qa}

	\begin{qa}{Is there anywhere you would particularly like to visit? [Why?]}
	Indeed there are. \textbf{Granted}, I have taken my family to different places of interests across Vietnam but I have not been able to go on vacation with them in foreign countries. A place that is \textbf{worthy of} our visit is Singapore-based Universal Studio, a theme park featuring \textbf{cutting-edge} roller coaster rides, extraordinary shows, and endless attractions based on \textbf{blockbuster films} and television series, including “Puss In Boots”, “Transformers”, and “Jurassic Park”, etc.
	\end{qa}

        \begin{VocabExplain}[Part 1]
			\begin{ExplainCard}{like no other}[idiom][B2]
			  \EN{Unique; unlike anything else.}
			  \SY{unparalleled; one-of-a-kind}
			  \VI{Độc nhất vô nhị.}
			  \EX{That stadium atmosphere is \textit{like no other}.}
			  \EX{Her voice has a warmth \textit{like no other}.}
			  \CO{an experience/product/team like no other}
			\end{ExplainCard}

			\begin{ExplainCard}{a liking for}[n~phr][B2]
			  \EN{A steady preference or enjoyment of something.}
			  \SY{fondness; taste}
			  \VI{Sự ưa thích; có cảm tình với.}
			  \EX{He has \textit{a liking for} classic kits.}
			  \EX{I've developed \textit{a liking for} graphic novels.}
			  \CO{have/develop a liking for sth}
			\end{ExplainCard}

			\begin{ExplainCard}{a quarter of a century}[n~phr][B2]
			  \EN{A period of 25 years.}
			  \SY{twenty-five years}
			  \VI{Một phần tư thế kỷ (25 năm).}
			  \EX{She's supported the club for \textit{a quarter of a century}.}
			  \EX{The series has run for \textit{a quarter of a century}.}
			  \CO{over/for nearly a quarter of a century}
			\end{ExplainCard}

			\begin{ExplainCard}{a fondness for}[n~phr][B2]
			  \EN{A gentle liking or affection toward something.}
			  \SY{affection; partiality}
			  \VI{Sự yêu thích; mê.}
			  \EX{I have \textit{a fondness for} manga.}
			  \EX{He shows \textit{a fondness for} 1990s rock.}
			  \CO{have/show a fondness for}
			\end{ExplainCard}

			\begin{ExplainCard}{date back to}[phr.v][B2]
			  \EN{To have existed since a particular time in the past.}
			  \SY{go back to; originate in}
			  \VI{Có từ; bắt nguồn từ (thời điểm).}
			  \EX{My hobby \textit{dates back to} primary school.}
			  \EX{The tradition \textit{dates back to} the 19th century.}
			  \CO{date back to the 1990s/childhood/ancient times}
			\end{ExplainCard}

			\begin{ExplainCard}{amplified distortion}[n~phr][C1]
			  \EN{A strong, overdriven guitar/amp sound where the signal is boosted to create a gritty tone.}
			  \SY{overdrive; fuzz}
			  \VI{Âm thanh guitar \textit{distortion} được khuếch đại mạnh.}
			  \EX{Metal relies on \textit{amplified distortion} and tight rhythms.}
			  \EX{They layered vocals over \textit{amplified distortion}.}
			  \CO{heavy/clean vs. amplified distortion; distorted guitar tone}
			\end{ExplainCard}

			\begin{ExplainCard}{aforementioned}[adj][C1]
			  \EN{Mentioned earlier in the same text or talk.}
			  \SY{above-mentioned; previously noted}
			  \VI{Kể trên; vừa nêu.}
			  \EX{The \textit{aforementioned} bands shaped my taste.}
			  \EX{See the \textit{aforementioned} reasons for detail.}
			  \CO{the aforementioned + noun}
			\end{ExplainCard}

			\begin{ExplainCard}{ignite (interest)}[v][C1]
			  \EN{To trigger or spark a strong feeling of interest.}
			  \SY{spark; arouse; kindle}
			  \VI{Khơi dậy; châm ngòi.}
			  \EX{The match \textit{ignited} my love of football.}
			  \EX{A great teacher can \textit{ignite} curiosity.}
			  \CO{ignite interest/passion/curiosity}
			\end{ExplainCard}

			\begin{ExplainCard}{heyday}[n][C1]
			  \EN{The period of greatest success, popularity, or power.}
			  \SY{prime; peak}
			  \VI{Thời hoàng kim.}
			  \EX{United were dominant in Beckham's \textit{heyday}.}
			  \EX{Manga sales peaked in their \textit{heyday}.}
			  \CO{in sb's/its heyday}
			\end{ExplainCard}

			\begin{ExplainCard}{unerring}[adj][C1]
			  \EN{Always accurate and certain; not making mistakes.}
			  \SY{faultless; infallible; precise}
			  \VI{Chuẩn xác; không chệch.}
			  \EX{His crosses had \textit{unerring} accuracy.}
			  \EX{\textit{Unerring} timing is crucial in dance.}
			  \CO{unerring accuracy/instinct/eye}
			\end{ExplainCard}

			\begin{ExplainCard}{kindle (interest)}[v][C1]
			  \EN{To arouse or inspire (a feeling or interest).}
			  \SY{stir; foster; awaken}
			  \VI{Nhen nhóm; khơi gợi.}
			  \EX{Moral themes \textit{kindled} my love of manga.}
			  \EX{Workshops \textit{kindle} students' curiosity.}
			  \CO{kindle interest/enthusiasm/hope}
			\end{ExplainCard}

			\begin{ExplainCard}{overhear}[v][B2]
			  \EN{To hear something by chance, without intending to.}
			  \SY{catch (by chance); pick up}
			  \VI{Tình cờ nghe được.}
			  \EX{I \textit{overheard} a metal song at a café.}
			  \EX{Tourists \textit{overheard} locals debating the match.}
			  \CO{overhear a conversation/remark/song}
			\end{ExplainCard}

			\begin{ExplainCard}{(be) taken aback}[idiom][B2]
			  \EN{Be very surprised or shocked.}
			  \SY{be startled; be stunned}
			  \VI{Bất ngờ; sững sờ.}
			  \EX{I was \textit{taken aback} by how loud it was.}
			  \EX{The result left fans \textit{taken aback}.}
			  \CO{be taken aback by/at sth}
			\end{ExplainCard}

			\begin{ExplainCard}{go into raptures (about/over)}[idiom][C1]
			  \EN{Express great delight and enthusiasm.}
			  \SY{rave about; be ecstatic over}
			  \VI{Say mê, ngây ngất khen ngợi.}
			  \EX{Fans \textit{went into raptures over} the solo.}
			  \EX{She \textit{went into raptures about} the new album.}
			  \CO{go into raptures about/over sth}
			\end{ExplainCard}

			\begin{ExplainCard}{hit the sack}[idiom][B2]
			  \EN{Go to bed (informal).}
			  \SY{turn in; crash}
			  \VI{Đi ngủ.}
			  \EX{I \textit{hit the sack} after the late match.}
			  \EX{We'll \textit{hit the sack} early before the trip.}
			  \CO{be ready to hit the sack}
			\end{ExplainCard}

			\begin{ExplainCard}{chill out}[phr.v][B2]
			  \EN{Relax and be calm.}
			  \SY{unwind; relax}
			  \VI{Thư giãn; xả hơi.}
			  \EX{I \textit{chill out} with lo-fi playlists.}
			  \EX{Let's \textit{chill out} after the game.}
			  \CO{chill out at home/with friends}
			\end{ExplainCard}

			\begin{ExplainCard}{binge reading}[n~phr][B2]
			  \EN{Reading a lot in one sitting, often continuously.}
			  \SY{marathon reading; read in one go}
			  \VI{Đọc “cày” liên tục.}
			  \EX{Weekend \textit{binge reading} keeps me sane.}
			  \EX{I went on a \textit{binge read} of that series.}
			  \CO{go on a binge reading session; binge-read novels/manga}
			\end{ExplainCard}

			\begin{ExplainCard}{kick back}[phr.v][B2]
			  \EN{Relax, often by reclining or stopping work.}
			  \SY{put your feet up; unwind}
			  \VI{Ngả lưng thư giãn; xả hơi.}
			  \EX{I \textit{kick back} with loud music and sing along.}
			  \EX{After exams, we \textit{kicked back} at the beach.}
			  \CO{kick back after work/at the weekend}
			\end{ExplainCard}

			\begin{ExplainCard}{shopping spree}[n~phr][B2]
			  \EN{A short period of spending a lot of money on shopping.}
			  \SY{splurge; buying binge}
			  \VI{Cuộc mua sắm “xả láng”.}
			  \EX{We go on a \textit{shopping spree} once a month.}
			  \EX{Holiday bonuses often trigger \textit{shopping sprees}.}
			  \CO{go on a shopping spree; post-exam/holiday shopping spree}
			\end{ExplainCard}

			\begin{ExplainCard}{all and sundry}[idiom][C1]
			  \EN{Everyone; all kinds of people.}
			  \SY{everyone; anybody and everybody}
			  \VI{Mọi người; ai ai.}
			  \EX{\textit{All and sundry} head for the beach on holidays.}
			  \EX{The news shocked \textit{all and sundry}.}
			  \CO{invite/affect all and sundry}
			\end{ExplainCard}

			\begin{ExplainCard}{be inclined to (do sth)}[v~phr][B2]
			  \EN{Tend to behave or think in a particular way.}
			  \SY{tend to; be prone to}
			  \VI{Có xu hướng; thiên về.}
			  \EX{People \textit{are inclined to} travel on long weekends.}
			  \EX{Fans \textit{are inclined to} book early.}
			  \CO{be inclined to believe/agree/travel}
			\end{ExplainCard}

			\begin{ExplainCard}{keep up with the Joneses}[idiom][C1]
			  \EN{Try to match others' lifestyle or status.}
			  \SY{follow the crowd; compete socially}
			  \VI{Đua đòi theo người khác.}
			  \EX{He \textit{keeps up with the Joneses} on gadgets.}
			  \EX{Resort trips can be a way to \textit{keep up with the Joneses}.}
			  \CO{try/compete to keep up with the Joneses}
			\end{ExplainCard}

			\begin{ExplainCard}{off duty}[adj/adv][B2]
			  \EN{Not working; outside official work hours.}
			  \SY{off work; off-shift}
			  \VI{Ngoài giờ làm; không trực.}
			  \EX{We're \textit{off duty} this weekend.}
			  \EX{Guards \textit{off duty} joined the picnic.}
			  \CO{be off duty; time off duty}
			\end{ExplainCard}

			\begin{ExplainCard}{take great delight in}[v~phr][C1]
			  \EN{Enjoy something very much.}
			  \SY{relish; take pleasure in}
			  \VI{Rất thích thú khi làm điều gì.}
			  \EX{I \textit{take great delight in} planning family trips.}
			  \EX{Kids \textit{take great delight in} water rides.}
			  \CO{take (great) delight in V-ing}
			\end{ExplainCard}

			\begin{ExplainCard}{a change of pace}[n~phr][B2]
			  \EN{Something different that makes things feel fresh.}
			  \SY{switch-up; break from routine}
			  \VI{Đổi gió; thay đổi nhịp độ.}
			  \EX{Weekend road trips are \textit{a change of pace}.}
			  \EX{Try a new genre for \textit{a change of pace}.}
			  \CO{for a change of pace; seek/offer a change of pace}
			\end{ExplainCard}

			\begin{ExplainCard}{engage in}[phr.v][B2]
			  \EN{Take part in an activity.}
			  \SY{participate in; involve oneself in}
			  \VI{Tham gia; dấn thân vào.}
			  \EX{We \textit{engage in} family activities on holidays.}
			  \EX{Teens \textit{engage in} community projects.}
			  \CO{engage in dialogue/sport/volunteering}
			\end{ExplainCard}

			\begin{ExplainCard}{drop in on}[phr.v][B2]
			  \EN{Visit someone briefly and unexpectedly.}
			  \SY{pop in on; stop by}
			  \VI{Tạt qua thăm; ghé nhanh.}
			  \EX{We \textit{drop in on} relatives during Tet.}
			  \EX{I \textit{dropped in on} an old coach last week.}
			  \CO{drop in on friends/relatives/colleagues}
			\end{ExplainCard}

			\begin{ExplainCard}{cement (a relationship)}[v][C1]
			  \EN{Make a relationship stronger and more lasting.}
			  \SY{strengthen; solidify; consolidate}
			  \VI{Củng cố; gắn kết bền chặt.}
			  \EX{Shared trips \textit{cement} family ties.}
			  \EX{Regular calls \textit{cemented} our friendship.}
			  \CO{cement ties/alliances/partnerships}
			\end{ExplainCard}

			\begin{ExplainCard}{Granted, ...}[adv][C1]
			  \EN{Admittedly; used to concede a point before contrasting it.}
			  \SY{admittedly; true, ... but}
			  \VI{Công nhận là…, tuy nhiên.}
			  \EX{\textit{Granted}, travel is pricey, but it's worth it.}
			  \EX{\textit{Granted}, we've been busy—still, we should plan.}
			  \CO{Granted, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{worthy of}[adj~phr][B2]
			  \EN{Deserving of something (attention, praise, visit).}
			  \SY{deserving of; meriting}
			  \VI{Xứng đáng (được làm/nhận).}
			  \EX{The park is \textit{worthy of} a family trip.}
			  \EX{His record is \textit{worthy of} respect.}
			  \CO{be worthy of note/attention/visit}
			\end{ExplainCard}

			\begin{ExplainCard}{cutting-edge}[adj][C1]
			  \EN{Extremely modern and advanced.}
			  \SY{state-of-the-art; leading-edge}
			  \VI{Tối tân; tiên tiến hàng đầu.}
			  \EX{\textit{Cutting-edge} rides draw thrill-seekers.}
			  \EX{\textit{Cutting-edge} tech powers the park.}
			  \CO{cutting-edge technology/design/research}
			\end{ExplainCard}

			\begin{ExplainCard}{blockbuster film}[n][B2]
			  \EN{A very popular, high-grossing movie.}
			  \SY{smash hit; big-budget hit}
			  \VI{Phim bom tấn.}
			  \EX{The park features \textit{blockbuster films} like \textit{Jurassic Park}.}
			  \EX{Studios bank on summer \textit{blockbusters}.}
			  \CO{summer/blockbuster franchise; release a blockbuster}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
	\begin{qa}{Describe a river, lake or sea which you like}
		You should say:\\
		\textbullet\ What the river, lake or sea is called\\
		\textbullet\ Where it is\\
		\textbullet\ What the land near it is like\\
		\textbullet\ and explain why you like this river, lake or sea.

		My country, Vietnam, \textbf{is blessed with} a large number of lakes and rivers, so if I have to describe my favorite one, I think Red River will be my priority. \textbf{As its name suggests}, this lake is well-known for red water some time in a year, mostly from May to August. \textbf{To the best of my knowledge}, a fisherman named it Red Lake because of its unique water color. Speaking of its location, it is situated \textbf{in the heart of} my hometown, so \textbf{rumor has it} among tourists that it is a \textbf{must-visit place}. It is easily accessible because buses now link \textbf{virtually} every part of the town, while the \textbf{fares} are much lower than they were a couple of years ago.

		Red River has been primarily for entertainment since a nearby park was erected ten years ago. There are \textbf{myriads} of activities to do there. On the weekends, several races take place along its banks, which attracts many visitors to \textbf{flock to}. One of the most interesting races is duck race where all the ducks are \textbf{launched} into the river and they will be pushed to float along the river for 500 meters. The first duck in the race to arrive at the \textbf{finishing line} wins its owner free tickets for a concert of symphony. As for the elderly, it is also a place for social gathering and relaxation. Some dancing and yoga clubs are organized on a daily basis to \textbf{promote health} and have better social life.

		Although there are \textbf{tons of} exciting activities, the primary reason why I am fascinated with this lake is that it's also surrounded by lots of \textbf{breathtaking scenery}, with \textbf{stunning views} of trees. \textbf{During the dog days} of the summer, it is also an ideal place to escape the \textbf{relentless} heat and \textbf{commune} with nature to \textbf{chill out}.
	\end{qa}

        \begin{VocabExplain}[Part 2]
			\begin{ExplainCard}{be blessed with}[v~phr][B2]
			  \EN{To have or be endowed with something good or desirable.}
			  \SY{be endowed with; enjoy}
			  \VI{Được ưu đãi/ban tặng (điều tốt).}
			  \EX{The region is \textit{blessed with} abundant freshwater.}
			  \EX{Our city is \textit{blessed with} green spaces along the river.}
			  \CO{be blessed with talent/natural beauty/resources}
			\end{ExplainCard}

			\begin{ExplainCard}{as its name suggests}[phrase][B2]
			  \EN{Used to introduce an explanation that matches the name.}
			  \SY{as the name implies; as the name indicates}
			  \VI{đúng như tên gọi.}
			  \EX{\textit{As its name suggests}, Red Lake turns crimson in summer.}
			  \EX{\textit{As the name suggests}, Riverwalk is perfect for strolls.}
			  \CO{as the/its name suggests, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{to the best of my knowledge}[phrase][C1]
			  \EN{As far as I know; based on what I believe to be true.}
			  \SY{as far as I know; to my knowledge}
			  \VI{theo như tôi biết.}
			  \EX{\textit{To the best of my knowledge}, the lake is man-made.}
			  \EX{\textit{To my knowledge}, no tours run at night.}
			  \CO{\textit{to the best of my knowledge}, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{in the heart of}[idiom][B2]
			  \EN{Exactly in the center of a place.}
			  \SY{in the center of; at the core of}
			  \VI{ngay trung tâm (thành phố/khu vực).}
			  \EX{The lake sits \textit{in the heart of} my hometown.}
			  \EX{A park \textit{in the heart of} downtown draws joggers.}
			  \CO{in the heart of the city/district/valley}
			\end{ExplainCard}

			\begin{ExplainCard}{rumor has it (that)}[idiom][C1]
			  \EN{People say; it is widely believed (without official proof).}
			  \SY{word has it; it's said that}
			  \VI{nghe đồn rằng.}
			  \EX{\textit{Rumor has it} that a festival will move to the lakefront.}
			  \EX{\textit{Rumour has it} the bridge will reopen next month.}
			  \CO{rumor/rumour has it that + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{must-visit place}[n~phr][B2]
			  \EN{A destination considered essential to see.}
			  \SY{must-see; unmissable spot}
			  \VI{điểm đến “nhất định phải ghé”.}
			  \EX{The promenade is a \textit{must-visit place} for sunset views.}
			  \EX{For birders, this wetland is a \textit{must-visit}.}
			  \CO{a must-visit for tourists/photographers/foodies}
			\end{ExplainCard}

			\begin{ExplainCard}{virtually}[adv][C1]
			  \EN{Almost; nearly; in effect.}
			  \SY{practically; nearly}
			  \VI{gần như, hầu như.}
			  \EX{Buses now reach \textit{virtually} every neighborhood.}
			  \EX{The lake is \textit{virtually} crowd-free on weekdays.}
			  \CO{virtually every/all/none; virtually impossible/identical}
			\end{ExplainCard}

			\begin{ExplainCard}{fare}[n][B2]
			  \EN{The price paid for travel on public transport.}
			  \SY{ticket price; charge}
			  \VI{giá vé (xe buýt, tàu, v.v.).}
			  \EX{Bus \textit{fares} dropped after the new routes opened.}
			  \EX{Off-peak \textit{fares} are cheaper for commuters.}
			  \CO{bus/train/air fare; fare increase/reduction}
			\end{ExplainCard}

			\begin{ExplainCard}{myriads (of)}[n~pl][C1]
			  \EN{A very large number; countless.}
			  \SY{countless; innumerable}
			  \VI{vô số; hằng hà sa số.}
			  \EX{There are \textit{myriads of} activities along the banks.}
			  \EX{Researchers face \textit{myriads of} small logistical issues.}
			  \CO{myriads of options/choices/species}
			\end{ExplainCard}

			\begin{ExplainCard}{flock to}[phr.v][B2]
			  \EN{Go to a place in large numbers.}
			  \SY{pour into; throng}
			  \VI{đổ xô kéo đến.}
			  \EX{Tourists \textit{flock to} the riverside on weekends.}
			  \EX{Fans \textit{flocked to} the regatta despite the heat.}
			  \CO{crowds/tourists/visitors flock to}
			\end{ExplainCard}

			\begin{ExplainCard}{launch (into)}[v][C1]
			  \EN{To send or set in motion (a boat/object) onto water or into movement.}
			  \SY{set afloat; send off}
			  \VI{thả/đưa (xuống nước); phóng.}
			  \EX{Ducks were \textit{launched into} the river for the race.}
			  \EX{They \textit{launched} canoes from the wooden slipway.}
			  \CO{launch a boat/kayak; launch into the water}
			\end{ExplainCard}

			\begin{ExplainCard}{finishing line}[n~phr][B2]
			  \EN{The end point of a race.}
			  \SY{finish line; tape}
			  \VI{vạch đích.}
			  \EX{The first duck to the \textit{finishing line} wins.}
			  \EX{She crossed the \textit{finish line} in record time.}
			  \CO{reach/cross/break the finishing line}
			\end{ExplainCard}

			\begin{ExplainCard}{promote health}[v~phr][B2]
			  \EN{To help improve people's physical or mental well-being.}
			  \SY{boost health; foster well-being}
			  \VI{tăng cường sức khỏe.}
			  \EX{Morning tai chi clubs \textit{promote health} for seniors.}
			  \EX{Trails and bike lanes \textit{promote} community \textit{health}.}
			  \CO{promote health and wellbeing; health-promoting activity}
			\end{ExplainCard}

			\begin{ExplainCard}{tons of}[quant~informal][B2]
			  \EN{A very large amount/number of something.}
			  \SY{loads of; a lot of}
			  \VI{rất nhiều; cả đống.}
			  \EX{There are \textit{tons of} weekend events by the lake.}
			  \EX{\textit{Tons of} families picnic under the trees.}
			  \CO{tons of activities/choices/people}
			\end{ExplainCard}

			\begin{ExplainCard}{breathtaking scenery}[n~phr][B2]
			  \EN{Landscape that is extremely beautiful or impressive.}
			  \SY{spectacular landscape; magnificent vistas}
			  \VI{phong cảnh ngoạn mục.}
			  \EX{We stopped to admire the \textit{breathtaking scenery}.}
			  \EX{The ridge offers \textit{breathtaking} river \textit{scenery}.}
			  \CO{breathtaking scenery/views/vistas}
			\end{ExplainCard}

			\begin{ExplainCard}{stunning views (of)}[n~phr][B2]
			  \EN{Exceptionally attractive or impressive views.}
			  \SY{panoramic views; magnificent views}
			  \VI{quang cảnh tuyệt đẹp.}
			  \EX{The boardwalk has \textit{stunning views of} the wetlands.}
			  \EX{Our room looked out on \textit{stunning views}.}
			  \CO{stunning views of/over/across}
			\end{ExplainCard}

			\begin{ExplainCard}{the dog days (of summer)}[idiom][C1]
			  \EN{The hottest, most sultry period of summer.}
			  \SY{peak summer; midsummer heat}
			  \VI{những ngày hè nóng nực nhất.}
			  \EX{\textit{During the dog days}, the riverside stays breezy.}
			  \EX{Power demand spikes in the \textit{dog days of summer}.}
			  \CO{during/in the dog days (of summer)}
			\end{ExplainCard}

			\begin{ExplainCard}{relentless (heat)}[adj][C1]
			  \EN{Severe and continuing without stopping.}
			  \SY{unremitting; incessant; harsh}
			  \VI{khắc nghiệt, không ngớt.}
			  \EX{Trees offer shade from the \textit{relentless} sun.}
			  \EX{\textit{Relentless} heatwaves strain the grid.}
			  \CO{relentless heat/pressure/pursuit/rain}
			\end{ExplainCard}

			\begin{ExplainCard}{commune (with nature)}[v~phr][C1]
			  \EN{To feel a deep, peaceful connection with nature.}
			  \SY{connect with; be at one with}
			  \VI{giao hòa/đắm mình với thiên nhiên.}
			  \EX{Visitors \textit{commune with nature} on quiet trails.}
			  \EX{She \textit{communes with} the forest at dawn.}
			  \CO{commune with nature/one's thoughts/spirits}
			\end{ExplainCard}

			\begin{ExplainCard}{chill out}[phr.v][B2]
			  \EN{Relax; calm down and rest.}
			  \SY{unwind; decompress}
			  \VI{thư giãn; xả hơi.}
			  \EX{Locals \textit{chill out} by the lakeside after work.}
			  \EX{Bring a book and \textit{chill out} under the willows.}
			  \CO{chill out at the park/with friends/after work}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
	\begin{qa}{What do people enjoy doing when they visit rivers, lakes or the sea? Why do you think these activities are popular?}
	Well, the question really \textbf{puts me on the spot}. You know, as a \textbf{rule of thumb}, people in my country pay a visit to water-related bodies like rivers or seas on their holidays. I mean, going to these places seems very \textbf{tranquil} and create \textbf{a sense of vitality}. While some may go there for swimming, others, myself included, just want to \textbf{go for a dip} and escape from my \textbf{daily routines}.
	\end{qa}

	\begin{qa}{What benefits do you think people get from the activities they enjoy in the water?}
	I \textbf{reckon} you are going to talk about water sports like \textbf{scuba diving} and \textbf{water skiing}. If that is the case, I think these sports, just like other sports, are \textbf{instrumental} in aiding people to keep fit and \textbf{unwind}. But, regardless of underwater activities they are going to \textbf{revel in}, they had better be \textbf{equipped with} swimming skills, just in case of emergency.
	\end{qa}

	\begin{qa}{What are the different advantages of going to the sea or to a swimming pool to enjoy yourself? What do you think the disadvantages are?}
	To begin with, each has its own \textbf{perks}. Basically, travelling to the beach appears more refreshing with \textbf{azure} waters, beautiful sight, and \textbf{serene ambience}, but the preparation needs to be \textbf{elaborated} and it is quite \textbf{time-consuming}. Meanwhile, going to a swimming pool is not a bad idea as it just takes a short drive and no booking reservations are needed. Nonetheless, this option is not \textbf{optimum} when a family want to experience a long vacation.
	\end{qa}

	\begin{qa}{How does water transport, like boats and ships, compare with other kinds? Are there any advantages/ disadvantages of water transport?}
	Historically, sea transportation is one of the oldest means of transport, along with road transport. Back in the early days of water transport, this was used to deliver \textbf{bulky cargoes} \textbf{transcontinentally}, and this is still true nowadays. Even though this means of transport is not as speedy as others such as air transport, it still plays a \textbf{pivotal} role in \textbf{commerce}. It is not \textbf{highway robbery} compared to air transportation to ship a container of goods from place to place. Accordingly, the price the end customer pays for a product may be more reasonable compared to it being shipped by air.
	\end{qa}

	\begin{qa}{How important is it for a town or city to be located near a river or the sea? Why?}
	Obviously, a \textbf{coastal city} could gain \textbf{competitive advantages} over non-coastal ones. Because located by the sea can give the city a convenient sea trade route, this means boats and ships can easily \textbf{navigate} and find places to \textbf{dock}. In fact, \textbf{port cities} like Hong Kong is considered one of the \textbf{prosperous} countries in the world thanks to maritime trade.
	\end{qa}

	\begin{qa}{Have there been any changes in the number of jobs available in fishing and water transport industries, do you think? Why do you think this is?}
	\textbf{Fishery is deemed} one of key sectors in many parts of the world, so the growth of this industry still lies in top government priorities. This is \textbf{synonymous with} increased \textbf{job opportunities} not in traditional careers such as fishermen, but also in \textbf{follow-up services} like logistics or sales. In the long run, it is expected more employees will \textbf{opt for} the fishing industry.
	\end{qa}

        \begin{VocabExplain}[Part 3]
			\begin{ExplainCard}{put sb on the spot}[idiom][C1]
			  \EN{To make someone feel pressured by asking a difficult question or demanding an immediate answer.}
			  \SY{corner; put sb under pressure}
			  \VI{Đẩy ai vào thế khó, hỏi “bí” tại chỗ.}
			  \EX{That question \textit{put me on the spot} in the interview.}
			  \EX{Reporters \textit{put the minister on the spot} about delays.}
			  \CO{put/feel on the spot; be put on the spot with/by}
			\end{ExplainCard}

			\begin{ExplainCard}{rule of thumb}[idiom][B2]
			  \EN{A practical and approximate way of judging or doing something.}
			  \SY{guideline; rough rule}
			  \VI{Kinh nghiệm ngón tay cái; quy tắc ước chừng.}
			  \EX{A good \textit{rule of thumb} is to rest one day per week.}
			  \EX{By \textit{rule of thumb}, allow 10 minutes per kilometre.}
			  \CO{as a rule of thumb; general/rough rule of thumb}
			\end{ExplainCard}

			\begin{ExplainCard}{tranquil}[adj][C1]
			  \EN{Calm and peaceful, with little movement or noise.}
			  \SY{serene; placid}
			  \VI{Yên bình, tĩnh lặng.}
			  \EX{We chose a \textit{tranquil} spot by the lake.}
			  \EX{A \textit{tranquil} atmosphere helps reduce stress.}
			  \CO{tranquil water/setting/village; remain/feel tranquil}
			\end{ExplainCard}

			\begin{ExplainCard}{a sense of vitality}[n~phr][C1]
			  \EN{A feeling of energy and aliveness.}
			  \SY{vigor; liveliness}
			  \VI{Cảm giác tràn đầy sinh khí.}
			  \EX{Sea air gives me \textit{a sense of vitality}.}
			  \EX{Regular exercise restores \textit{vitality}.}
			  \CO{boost/restore vitality; a renewed sense of vitality}
			\end{ExplainCard}

			\begin{ExplainCard}{go for a dip}[idiom][B2]
			  \EN{To have a short swim, especially for refreshment.}
			  \SY{take a dip; have a quick swim}
			  \VI{Tắm/nhúng mình một lát.}
			  \EX{Let's \textit{go for a dip} before dinner.}
			  \EX{Hikers \textit{took a dip} in the river to cool off.}
			  \CO{go/take/have a dip in the sea/pool}
			\end{ExplainCard}

			\begin{ExplainCard}{daily routines}[n~phr][B1]
			  \EN{Regular, everyday activities and habits.}
			  \SY{day-to-day schedule; everyday habits}
			  \VI{Nếp sinh hoạt hằng ngày.}
			  \EX{A walk breaks my \textit{daily routine}.}
			  \EX{Try reshaping \textit{daily routines} for better sleep.}
			  \CO{break/settle into/change your daily routine}
			\end{ExplainCard}

			\begin{ExplainCard}{reckon}[v][B2]
			  \EN{To think or suppose; to believe something is true.}
			  \SY{guess; suppose; believe}
			  \VI{Cho rằng, đoán là.}
			  \EX{I \textit{reckon} it'll rain later.}
			  \EX{Analysts \textit{reckon} demand will rise.}
			  \CO{reckon (that) ...; be reckoned to be}
			\end{ExplainCard}

			\begin{ExplainCard}{scuba diving}[n][B2]
			  \EN{Underwater swimming using a self-contained breathing apparatus.}
			  \SY{open-water diving}
			  \VI{Lặn biển có bình dưỡng khí.}
			  \EX{We tried \textit{scuba diving} on Phu Quoc.}
			  \EX{Courses certify beginners for \textit{open-water} dives.}
			  \CO{go/try/learn scuba diving; scuba-diving course/gear}
			\end{ExplainCard}

			\begin{ExplainCard}{water skiing}[n][B2]
			  \EN{Being towed behind a boat on skis across the water.}
			  \SY{—}
			  \VI{Trượt nước kéo bằng thuyền.}
			  \EX{She learned \textit{water skiing} last summer.}
			  \EX{Calm lakes are ideal for \textit{water-skiing}.}
			  \CO{go water skiing; water-skiing lesson/equipment}
			\end{ExplainCard}

			\begin{ExplainCard}{instrumental (in)}[adj][C1]
			  \EN{Very important in causing something to happen.}
			  \SY{crucial; key; pivotal}
			  \VI{Đóng vai trò then chốt (trong việc).}
			  \EX{Swimming was \textit{instrumental in} my recovery.}
			  \EX{Local clubs were \textit{instrumental in} the event's success.}
			  \CO{be instrumental in doing sth}
			\end{ExplainCard}

			\begin{ExplainCard}{unwind}[v][B2]
			  \EN{To relax after stress or effort.}
			  \SY{decompress; chill out}
			  \VI{Thư giãn, xả hơi.}
			  \EX{A quick swim helps me \textit{unwind}.}
			  \EX{People \textit{unwind} with evening walks by the river.}
			  \CO{unwind after work/exams; time to unwind}
			\end{ExplainCard}

			\begin{ExplainCard}{revel in}[phr.v][C1]
			  \EN{To take great pleasure in something.}
			  \SY{delight in; relish}
			  \VI{Thích thú, khoái chí với.}
			  \EX{Kids \textit{revel in} splashing in the shallows.}
			  \EX{She \textit{revels in} challenging workouts.}
			  \CO{revel in the moment/attention/freedom}
			\end{ExplainCard}

			\begin{ExplainCard}{be equipped with}[v~phr][B2]
			  \EN{To have the necessary tools, skills, or features.}
			  \SY{be furnished with; be supplied with}
			  \VI{Được trang bị (kỹ năng/thiết bị).}
			  \EX{Lifeguards \textit{are equipped with} rescue gear.}
			  \EX{Students should be \textit{equipped with} water-safety skills.}
			  \CO{be well/fully equipped with}
			\end{ExplainCard}

			\begin{ExplainCard}{perks}[n~pl][B2]
			  \EN{Special benefits or advantages, especially of a job or choice.}
			  \SY{benefits; pluses}
			  \VI{Quyền lợi, lợi ích thêm.}
			  \EX{One of the \textit{perks} of the beach is fresh seafood.}
			  \EX{Membership \textit{perks} include pool access.}
			  \CO{perks of the job/membership; enjoy/offer perks}
			\end{ExplainCard}

			\begin{ExplainCard}{azure (waters)}[adj][C1]
			  \EN{Bright blue in colour, like a clear sky or sea.}
			  \SY{cerulean; sky-blue}
			  \VI{Xanh biếc (biển/trời).}
			  \EX{We swam in \textit{azure} waters at noon.}
			  \EX{The bay's \textit{azure} hue is unforgettable.}
			  \CO{azure sea/sky/waters}
			\end{ExplainCard}

			\begin{ExplainCard}{serene ambience}[n~phr][C1]
			  \EN{A calm and peaceful atmosphere.}
			  \SY{tranquil atmosphere; placid setting}
			  \VI{Không khí tĩnh lặng, an yên.}
			  \EX{The spa's \textit{serene ambience} encourages rest.}
			  \EX{Gardens create a \textit{serene ambience} by the lake.}
			  \CO{create/maintain a serene ambience}
			\end{ExplainCard}

			\begin{ExplainCard}{elaborate (prep)}[adj][C1]
			  \EN{Detailed and carefully arranged; requiring many steps.}
			  \SY{complex; detailed}
			  \VI{Cầu kỳ, nhiều công đoạn/chi tiết.}
			  \EX{Beach trips need more \textit{elaborate} preparation.}
			  \EX{An \textit{elaborate} packing list saves time later.}
			  \CO{elaborate plan/preparation/setup}
			\end{ExplainCard}

			\begin{ExplainCard}{time-consuming}[adj][B2]
			  \EN{Taking a lot of time to do.}
			  \SY{laborious; lengthy}
			  \VI{Tốn thời gian.}
			  \EX{Booking ferries can be \textit{time-consuming}.}
			  \EX{The permit process proved \textit{time-consuming}.}
			  \CO{a time-consuming task/process}
			\end{ExplainCard}

			\begin{ExplainCard}{optimum}[adj][C1]
			  \EN{Best or most favourable under the circumstances.}
			  \SY{optimal; ideal; best}
			  \VI{Tối ưu, thuận lợi nhất.}
			  \EX{A pool isn't the \textit{optimum} choice for long vacations.}
			  \EX{Find the \textit{optimum} balance between cost and time.}
			  \CO{optimum solution/condition/level}
			\end{ExplainCard}

			\begin{ExplainCard}{bulky cargo(es)}[n~phr][C1]
			  \EN{Large, heavy goods that are difficult to move.}
			  \SY{heavy freight; outsize loads}
			  \VI{Hàng cồng kềnh, nặng.}
			  \EX{Ships carry \textit{bulky cargoes} like timber and ore.}
			  \EX{Rail is efficient for \textit{bulky cargo}.}
			  \CO{transport/ship bulky cargoes; handle bulky freight}
			\end{ExplainCard}

			\begin{ExplainCard}{transcontinentally}[adv][C1]
			  \EN{Across or between continents.}
			  \SY{intercontinentally}
			  \VI{Xuyên lục địa.}
			  \EX{Goods were shipped \textit{transcontinentally} by sea.}
			  \EX{Cables now connect data \textit{transcontinentally}.}
			  \CO{ship/fly/trade transcontinentally}
			\end{ExplainCard}

			\begin{ExplainCard}{pivotal}[adj][C1]
			  \EN{Of crucial importance in relation to the success of something.}
			  \SY{crucial; key; central}
			  \VI{Mang tính then chốt.}
			  \EX{Ports play a \textit{pivotal} role in trade.}
			  \EX{Logistics is \textit{pivotal} to exports.}
			  \CO{play a pivotal role in; be pivotal to}
			\end{ExplainCard}

			\begin{ExplainCard}{commerce}[n][B2]
			  \EN{The activity of buying and selling, especially on a large scale.}
			  \SY{trade; business}
			  \VI{Thương mại.}
			  \EX{Rivers historically enabled inland \textit{commerce}.}
			  \EX{E-\textit{commerce} expands market access.}
			  \CO{domestic/international commerce; facilitate/stimulate commerce}
			\end{ExplainCard}

			\begin{ExplainCard}{highway robbery}[idiom][C1]
			  \EN{Something outrageously expensive or unfairly priced.}
			  \SY{rip-off; daylight robbery}
			  \VI{Đắt cắt cổ; “chém đẹp”.}
			  \EX{Air freight felt like \textit{highway robbery}.}
			  \EX{Those holiday prices are \textit{daylight robbery}.}
			  \CO{be/feel like highway robbery; call sth highway robbery}
			\end{ExplainCard}

			\begin{ExplainCard}{coastal city}[n~phr][B2]
			  \EN{A city located on or near a coast.}
			  \SY{seaside city; port city (if with harbor)}
			  \VI{Thành phố ven biển.}
			  \EX{A \textit{coastal city} attracts cruise tourism.}
			  \EX{\textit{Coastal cities} face rising-sea challenges.}
			  \CO{major/southern coastal city; coastal urban areas}
			\end{ExplainCard}

			\begin{ExplainCard}{competitive advantage}[n~phr][C1]
			  \EN{A condition that puts a company/place in a superior business position.}
			  \SY{edge; superiority}
			  \VI{Lợi thế cạnh tranh.}
			  \EX{Deep-water ports give \textit{competitive advantages}.}
			  \EX{Skilled labour is a key \textit{advantage}.}
			  \CO{gain/hold/maintain a competitive advantage}
			\end{ExplainCard}

			\begin{ExplainCard}{navigate}[v][B2]
			  \EN{To find a way through/over water; to steer a vessel.}
			  \SY{steer; pilot; manoeuvre}
			  \VI{Điều hướng, lái tàu thuyền.}
			  \EX{Boats \textit{navigate} the channel at low tide.}
			  \EX{Captains \textit{navigated} safely into harbour.}
			  \CO{navigate a river/channel/harbour}
			\end{ExplainCard}

			\begin{ExplainCard}{dock}[v][B2]
			  \EN{To bring a ship into a dock and secure it.}
			  \SY{moor; berth}
			  \VI{Cặp bến, neo đậu.}
			  \EX{Ferries \textit{dock} every hour.}
			  \EX{Cargo ships \textit{docked} at the new terminal.}
			  \CO{dock at/in; docking station/berth}
			\end{ExplainCard}

			\begin{ExplainCard}{port city}[n~phr][B2]
			  \EN{A city with a harbour used by ships for trade or transport.}
			  \SY{harbour city}
			  \VI{Thành phố cảng.}
			  \EX{Singapore is a major \textit{port city}.}
			  \EX{\textit{Port cities} thrive on logistics.}
			  \CO{global/international port city; busy port city}
			\end{ExplainCard}

			\begin{ExplainCard}{prosperous}[adj][C1]
			  \EN{Successful and wealthy; flourishing.}
			  \SY{affluent; thriving}
			  \VI{Thịnh vượng, phát đạt.}
			  \EX{\textit{Prosperous} ports attract migration.}
			  \EX{A \textit{prosperous} fishing sector lifted incomes.}
			  \CO{prosperous city/industry/era}
			\end{ExplainCard}

			\begin{ExplainCard}{(be) deemed}[v][C1]
			  \EN{To consider or judge something in a particular way.}
			  \SY{regard as; consider}
			  \VI{Được xem/cho là.}
			  \EX{\textit{Fishery is deemed} a priority sector.}
			  \EX{The route was \textit{deemed} unsafe at night.}
			  \CO{be deemed + Adj/N; deem sth necessary/appropriate}
			\end{ExplainCard}

			\begin{ExplainCard}{synonymous with}[adj~phr][C1]
			  \EN{So closely connected with something that they are almost the same.}
			  \SY{equivalent to; closely associated with}
			  \VI{Đồng nghĩa, gắn liền với.}
			  \EX{The port is \textit{synonymous with} trade.}
			  \EX{Small boats are \textit{synonymous with} the town's image.}
			  \CO{become/virtually synonymous with}
			\end{ExplainCard}

			\begin{ExplainCard}{job opportunities}[n~phr][B2]
			  \EN{Chances of getting employment.}
			  \SY{employment prospects; openings}
			  \VI{Cơ hội việc làm.}
			  \EX{Logistics growth creates \textit{job opportunities}.}
			  \EX{Training lifts \textit{employment opportunities}.}
			  \CO{create/expand job opportunities; equal opportunities}
			\end{ExplainCard}

			\begin{ExplainCard}{follow-up services}[n~phr][C1]
			  \EN{Services provided after an initial sale or activity to support customers or operations.}
			  \SY{after-sales services; downstream services}
			  \VI{Dịch vụ hậu mãi/hậu cần tiếp nối.}
			  \EX{Ports need \textit{follow-up services} like warehousing.}
			  \EX{Healthcare offers \textit{follow-up} appointments and advice.}
			  \CO{provide/arrange follow-up services/support}
			\end{ExplainCard}

			\begin{ExplainCard}{opt for}[phr.v][B2]
			  \EN{To choose or decide in favour of something.}
			  \SY{choose; go for; select}
			  \VI{Chọn, quyết định chọn.}
			  \EX{Many graduates \textit{opt for} maritime jobs.}
			  \EX{Families \textit{opt for} pools during rainy season.}
			  \CO{opt for A over B; opt for a career/option}
			\end{ExplainCard}
			
			\begin{ExplainCard}{logistics}[n][C1]
			  \EN{The planning and coordination of moving and storing goods (and sometimes people or information) from origin to destination—covering transport, warehousing, inventory, and delivery.}
			  \SY{distribution; supply-chain management}
			  \VI{Công tác hậu cần/logistics: vận chuyển, kho bãi, quản lý tồn kho và giao hàng.}
			  \EX{The port's growth has boosted the city's \textit{logistics} sector.}
			  \EX{Efficient \textit{logistics} reduce lead times and costs for exporters.}
			  \CO{logistics hub/industry/chain; handle/organize/streamline logistics; logistics costs/network}
			\end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
		\VH{like no other}{(idiom) very special}{(thành ngữ) rất đặc biệt}
		\VH{(to have) a liking for}{(n) to like something}{(danh từ) thích cái gì}
		\VH{(to have) a fondness for}{(n) to like something}{(danh từ) thích cái gì}
		\VH{to date back to}{(phr. v) to have been made in or to have come into being in a certain time in the past}{(cụm động từ) bắt nguồn từ}
		\VH{aforementioned}{(adj) mentioned before, in earlier sentences}{(tính từ) đã được đề cập ở trên}
		\VH{to ignite}{(v) to start to burn; to make something start to burn}{(động từ) làm cái gì bắt đầu bùng cháy}
		\VH{in one's heyday}{(phrase) in, at, or during the period of one's greatest success, power, vigor, etc}{(cụm từ) trong thời kỳ hoàng kim nhất}
		\VH{unerring}{(adj) always right or accurate}{(tính từ) luôn chuẩn xác}
		\VH{to kindle}{(v) to make something such as an interest, emotion, etc. start to grow in somebody; to start to be felt by somebody}{(động từ) khiến cái gì trỗi dậy}
		\VH{to overhear}{(v) to hear, especially by accident, a conversation in which you are not involved}{(động từ) nghe lóm được}
		\VH{to be taken aback}{(phr. v) to be surprised}{(cụm động từ) ngạc nhiên}
		\VH{to go into raptures}{(idiom) feel great pleasure and happiness about something}{(thành ngữ) sướng quá}
		\VH{to hit the sack}{(idiom) to go to bed}{(thành ngữ) đi ngủ}
		\VH{to chill out}{(phr. v) to relax completely, or not allow things to upset you}{(cụm động từ) thư giãn hoàn toàn}
		\VH{to binge reading}{(v) to read something voraciously}{(động từ) cày truyện}
		\VH{to kick back}{(phr. v) to stop doing things and relax}{(cụm động từ) nghỉ ngơi thư giãn}
		\VH{a shopping spree}{(n) a short period of time in which someone buys a lot of things}{(danh từ) 1 khoảng thời gian mà người mua sắm nhiều và tung tay quá trớn}
		\VH{all and sundry}{(idiom) everyone}{(thành ngữ) mọi người}
		\VH{to be inclined to V-inf}{(p2) to be predisposed to v-ing}{(phần từ 2) có xu hướng làm gì}
		\VH{to keep up with the Joneses}{(idiom) to always want to own the same expensive objects and do the same things as your friends or neighbours}{(thành ngữ) đua đòi}
		\VH{to be off-duty}{(phrase) not off on duty}{(cụm từ) không phải làm việc}
		\VH{take great delight in V-ing}{(phrase) to take great pleasure in, to be happy to do something}{(cụm từ) có nhiều niềm vui trong việc gì}
		\VH{to engage in}{(v) to partake in}{(động từ) tham gia vào}
		\VH{to drop in on}{(phr. v) call informally and briefly as a visitor}{(cụm động từ) ghé qua bất chợt}
		\VH{to cement}{(v) to fortify}{(động từ) giữ vững, củng cố}
		\VH{granted}{(adv) admittedly, it is true that}{(trạng từ) đúng là}
		\VH{to be worthy of}{(v) to deserve V-ing}{(tính từ) đáng làm gì}
		\VH{cutting-edge}{(adj) at the newest, most advanced stage in the development of something}{(tính từ) tối tân nhất}
		\VH{a blockbuster film}{(n) a book or film that is very successful}{(danh từ) phim bom tấn}
		\VH{be blessed with}{(phrase) be lucky to have something by god}{(cụm từ) trời phú}
		\VH{as its name suggests}{(idiom) according to the meaning of the name}{(thành ngữ) đúng như cái tên đã nói}
		\VH{in the heart of}{(idiom) in the center of}{(thành ngữ) trung tâm}
		\VH{rumor has it}{(idiom) It is being rumored that}{(thành ngữ) có đồn rằng}
		\VH{myriads of}{(phrase) a very large number of something}{(cụm từ) rất nhiều}
		\VH{promote health}{(phrase) the process of enabling people to increase control over their health and its determinants, and thereby improve their health}{(cụm từ) tăng cường sức khoẻ}
		\VH{tons of}{(phrase) an extremely large number of}{(cụm từ) số lượng lớn}
		\VH{breathtaking scenery}{(phrase) extremely beautiful natural environment}{(cụm từ) phong cảnh đẹp}
		\VH{stunning views}{(phrase) extremely attractive landscape}{(cụm từ) cảnh đẹp tuyệt vời}
		\VH{during the dog days}{(idiom) the hot sultry weather of summer}{(thành ngữ) thời tiết oi bức của mùa hè}
		\VH{relentless}{(adj) continuing in a severe or extreme way}{(tính từ) không ngừng}
		\VH{commune with}{(phr.v) to get very close to someone}{(cụm động từ) gần gũi với}
		\VH{chill out}{(phr.v) to relax completely, or not allow things to upset you}{(cụm động từ) thư giãn}
		\VH{to put somebody on the spot}{(idiom) to force one to do something instantaneously, often causing them unease or embarrassment}{(thành ngữ) đặt ai vào thế bí, làm khó ai đó}
		\VH{rule of thumb}{(idiom) a broadly accurate guide or principle, based on experience or practice rather than theory}{(thành ngữ) kinh nghiệm thực tế}
		\VH{tranquil}{(adj) quiet and peaceful}{(tính từ) thanh tĩnh; yên bình}
		\VH{a sense of vitality}{(phrase) to feel energetic and enthusiastic}{(cụm từ) tràn đầy sức sống}
		\VH{to go for a dip}{(phrase) swim for pleasure}{(cụm từ) đi nghịch nước}
		\VH{daily routines}{(phrase) comprises the ways in which people typically act, think, and feel on a daily basis}{(cụm từ) lịch trình hàng ngày}
		\VH{to reckon}{(v) to think something or have an opinion about something}{(động từ) cho rằng, đoán rằng}
		\VH{scuba diving}{(noun) the sport or activity of swimming underwater using scuba gear}{(danh từ) bộ môn lặn}
		\VH{water skiing}{(noun) skim the surface of water on waterskis}{(danh từ) bộ môn lướt ván}
		\VH{instrumental}{(adj) important in making something happen}{(tính từ) rất quan trọng}
		\VH{to unwind}{(v) to stop worrying or thinking about problems and start to relax}{(động từ) thư giãn, xả hơi}
		\VH{equipped with}{(v) to be supplied with the necessary items for a particular purpose}{(động từ) được trang bị}
		\VH{perk}{(n) an advantage}{(danh từ) ưu điểm, thế mạnh}
		\VH{azure}{(adj) a bright blue colour, like the sky}{(danh từ) màu xanh da trời}
		\VH{serene ambience}{(phrase) calm peaceful atmosphere}{(cụm từ) không khí yên ả}
		\VH{to be elaborated}{(p2) to develop a plan, an idea, etc. and make it complicated or detailed}{(phần từ 2) làm cho chi tiết, tỉ mỉ hơn}
		\VH{optimum}{(adj) the best possible result, set of conditions, etc}{(tính từ) tối ưu}
		\VH{bulky cargoes}{(phrase) commodity cargo that is transported unpackaged in large quantities}{(cụm từ) hàng hóa cồng kềnh}
		\VH{transcontinentally}{(adv) crossing a continent}{(trạng từ) xuyên lục địa}
		\VH{pivotal}{(adj) of great importance because other things depend on it}{(tính từ) đóng vai trò trụ cột, rất quan trọng}
		\VH{commerce}{(n) trade, especially between countries; the buying and selling of goods and services}{(danh từ) thương mại}
		\VH{a coastal city}{(phrase) the city placed near the coast}{(cụm từ) thành phố ven biển}
		\VH{competitive advantage}{(phrase) an advantage over competitors gained by offering consumers greater value, either by means of lower prices or by providing greater benefits and service that justifies higher prices}{(cụm từ) lợi thế cạnh tranh}
		\VH{to navigate}{(v) to find your position or the position of your ship, plane, car etc. and the direction you need to go in, for example by using a map}{(động từ) điều hướng}
		\VH{dock}{(v) if a ship docks, it sails into a harbour and stays there}{(động từ) thả neo, neo đậu}
		\VH{port cities}{(phrase) cities, towns, or other places where ships load or unload}{(cụm từ) thành phố cảng}
		\VH{prosperous}{(adj) rich and successful}{(tính từ) thịnh vượng, phát đạt}
		\VH{fishery}{(n) a sector related to catching and processing fish}{(danh từ) ngành thủy sản}
		\VH{to deem}{(v) to have a particular opinion about something}{(động từ) coi là}
		\VH{synonymous with}{(adj) having the same, or nearly the same meaning}{(tính từ) đồng nghĩa với}
		\VH{job opportunities}{(phrase) job vacancies}{(cụm từ) cơ hội việc làm}
		\VH{follow-up services}{(phrase) something that is done to finish a previous action or make it more successful}{(cụm từ) dịch vụ đi kèm}
		\VH{logistic}{(adj) connected with the practical organization needed for a complicated plan involving a lot of people and equipment}{(tính từ) thuộc hậu cần, vận tải}
    \end{VocabHighlights}
    \end{test}

    \begin{test}{TEST 4}
    \noindent
    \textbf{Part 1. Your favourite place}
	\begin{qa}{What place do you most like to visit?}
	Well, it is hard to pick one but the first place that crosses my mind is Old Trafford, the home stadium of Manchester United, one of the most successful clubs in the world. I am a Manchester United \textbf{fanatic} so my visiting “The Theatre of Dreams”, the nickname of Old Trafford, was a \textbf{dream come true} for me in 2014.
	\end{qa}

	\begin{qa}{How often do you visit this place?}
	\textbf{Truth be told}, I \textbf{took advantage of} my \textbf{studying abroad} to go to Old Trafford three times. \textbf{For the time being}, I am back to Vietnam after having finished my Master degree so there is \textbf{fat chance} that I will be able to visit Old Trafford again, which gave me \textbf{goosebumps} 4 years ago.
	\end{qa}

	\begin{qa}{Is it popular with many other people?}
	Yes, absolutely. Old Trafford is a \textbf{must-see place} for those \textbf{embarking on} a tour in Manchester. It is frequently visited by millions of supporters \textbf{on a yearly basis}. Tourists may \textbf{seize the opportunity} to understand United's glorious history after having a look at their museum full of \textbf{trophies}. They can also \textbf{marvel at} the magnificence of Old Trafford, with its capacity \textbf{accommodating} 76{,}000 ardent supporters at once.
	\end{qa}

	\begin{qa}{Has it changed very much since you first went there? [In what way?]}
	As I said earlier, the last time I visited Old Trafford was \textbf{half a decade} ago. I have not been able to visit it again so it is impossible for me to \textbf{figure out} any differences. However, according to the \textbf{mass media}, it is \textbf{rumored} that Manchester United will \textbf{expand} Old Trafford to reach the capacity of 88{,}000 supporters instead of 75{,}000 ones. However, \textbf{it remains to be seen} when this would turn into a reality in the near future.
	\end{qa}

        \begin{VocabExplain}[Part 1]
			\begin{ExplainCard}{fanatic}[n][C1]
			\EN{A person extremely enthusiastic about a particular activity, cause, or team.}
			\SY{die-hard; ardent supporter; devotee}
			\VI{Người cuồng nhiệt, fan “cứng”.}
			\EX{He's a United \textit{fanatic} who never misses a match.}
			\EX{Brand communities often include \textit{fanatics} who drive word-of-mouth.}
			\CO{football/music/tech fanatic; a fanatic about sth}
			\end{ExplainCard}

			\begin{ExplainCard}{a dream come true}[idiom][B2]
			\EN{A long-held wish that has finally been realised.}
			\SY{wish fulfilled; long-cherished dream realised}
			\VI{Giấc mơ thành hiện thực.}
			\EX{Meeting my idol was \textit{a dream come true}.}
			\EX{For many scholars, a full scholarship is \textit{a dream come true}.}
			\CO{be/feel like a dream come true; make sb's dream come true}
			\end{ExplainCard}

			\begin{ExplainCard}{truth be told}[discourse][B2]
			\EN{Used to introduce an honest or slightly candid remark.}
			\SY{to be honest; frankly}
			\VI{Nói thật là; thành thật mà nói.}
			\EX{\textit{Truth be told}, I cried on the stadium tour.}
			\EX{\textit{Truth be told}, the plan lacked clear metrics.}
			\CO{Truth be told, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{take advantage of}[phr.v][B2]
			\EN{To use a situation, resource, or chance in a way that benefits you.}
			\SY{make the most of; leverage; capitalize on}
			\VI{Tận dụng (cơ hội/điều kiện).}
			\EX{I \textit{took advantage of} my trip to visit Old Trafford.}
			\EX{Firms \textit{capitalize on} off-peak demand to test pilots.}
			\CO{take full/maximum advantage of; advantage of an opportunity}
			\end{ExplainCard}

			\begin{ExplainCard}{studying abroad}[n~phr][B2]
			\EN{Pursuing education in a foreign country.}
			\SY{overseas study; international study}
			\VI{Du học.}
			\EX{\textit{Studying abroad} broadened my horizons.}
			\EX{Universities promote \textit{overseas study} for intercultural skills.}
			\CO{plan/finance/benefit from studying abroad}
			\end{ExplainCard}

			\begin{ExplainCard}{for the time being}[phrase][B2]
			\EN{For now; temporarily, until the situation changes.}
			\SY{for now; for the moment}
			\VI{Tạm thời; trước mắt.}
			\EX{\textit{For the time being}, I'm back in Viet Nam.}
			\EX{The project is paused \textit{for the time being}.}
			\CO{remain/suspend/operate for the time being}
			\end{ExplainCard}

			\begin{ExplainCard}{fat chance}[idiom][B2]
			\EN{Almost no likelihood (often ironic).}
			\SY{slim chance; hardly likely; not a chance}
			\VI{Khó mà có; hi vọng mong manh (mang tính mỉa).}
			\EX{\textit{Fat chance} I'll get tickets this week!}
			\EX{\textit{Fat chance} of budget approval without data.}
			\CO{there's a fat/slim chance (that) ...}
			\end{ExplainCard}

			\begin{ExplainCard}{goosebumps}[n~pl][B2]
			\EN{Small bumps on the skin caused by cold, fear, or strong emotion; figuratively, a surge of excitement.}
			\SY{chills; shivers}
			\VI{Nổi da gà (vì xúc động/sợ hãi/lạnh).}
			\EX{The anthem gave me \textit{goosebumps}.}
			\EX{Powerful storytelling can trigger \textit{goosebumps} in audiences.}
			\CO{get/have goosebumps; give sb goosebumps}
			\end{ExplainCard}

			\begin{ExplainCard}{must-see (place)}[adj/n][B2]
			\EN{So good or important that you should not miss it.}
			\SY{unmissable; must-visit}
			\VI{Đáng xem/đi; “nhất định phải ghé”.}
			\EX{Old Trafford is a \textit{must-see} for football fans.}
			\EX{The gallery's new wing is \textit{unmissable}.}
			\CO{a must-see attraction/museum/landmark}
			\end{ExplainCard}

			\begin{ExplainCard}{embark on}[phr.v][C1]
			\EN{To begin a major journey, project, or activity.}
			\SY{set out on; commence; launch}
			\VI{Khởi sự; bắt đầu (hành trình/dự án).}
			\EX{They \textit{embarked on} a tour of Manchester.}
			\EX{The firm \textit{embarked on} digital transformation in 2022.}
			\CO{embark on a tour/career/initiative}
			\end{ExplainCard}

			\begin{ExplainCard}{on a yearly basis}[adv~phr][B2]
			\EN{Every year; annually.}
			\SY{annually; each year}
			\VI{Hàng năm.}
			\EX{Millions visit the museum \textit{on a yearly basis}.}
			\EX{We review KPIs \textit{annually}.}
			\CO{increase/review/report on a yearly basis}
			\end{ExplainCard}

			\begin{ExplainCard}{seize the opportunity}[v~phr][B2]
			\EN{To act quickly to take advantage of a chance.}
			\SY{grasp; capitalize on; snap up}
			\VI{Chớp cơ hội; tận dụng thời cơ.}
			\EX{Tourists \textit{seize the opportunity} to see the trophy room.}
			\EX{Start-ups must \textit{capitalize on} market windows.}
			\CO{seize/grasp the opportunity to do sth}
			\end{ExplainCard}

			\begin{ExplainCard}{trophy}[n][B2]
			\EN{A prize such as a cup or shield awarded for victory or achievement.}
			\SY{silverware; award; cup}
			\VI{Cúp/giải thưởng.}
			\EX{The club displays historic \textit{trophies}.}
			\EX{Accumulating \textit{silverware} signals sustained excellence.}
			\CO{win/lift a trophy; trophy cabinet/haul}
			\end{ExplainCard}

			\begin{ExplainCard}{marvel at}[phr.v][C1]
			\EN{To feel great surprise or admiration for something.}
			\SY{be amazed at; be in awe of}
			\VI{Trầm trồ, thán phục.}
			\EX{Visitors \textit{marvel at} the stadium's scale.}
			\EX{Architects \textit{marvel at} its cantilevered roof.}
			\CO{marvel at/over sth; marvel that + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{accommodating (capacity)}[adj (participle)][B2]
			\EN{(Of a venue) able to \textit{accommodate}—i.e., hold or provide space for—a stated number of people.}
			\SY{holding; seating; housing}
			\VI{Chứa/đáp ứng sức chứa (bao nhiêu người).}
			\EX{The ground is \textit{accommodating} 76,000 spectators.}
			\EX{The arena's \textit{seating capacity} accommodates 20,000.}
			\CO{accommodate \# guests/spectators; seating capacity of \#}
			\end{ExplainCard}

			\begin{ExplainCard}{half a decade}[n~phr][B2]
			\EN{A period of five years.}
			\SY{five years}
			\VI{Năm năm; nửa thập kỷ.}
			\EX{I last visited \textit{half a decade} ago.}
			\EX{Results are reviewed over \textit{five-year} cycles.}
			\CO{over/for half a decade; a half-decade gap/trend}
			\end{ExplainCard}

			\begin{ExplainCard}{figure out}[phr.v][B2]
			\EN{To understand or solve something after thinking about it.}
			\SY{work out; determine; decipher}
			\VI{Tìm ra/hiểu ra/giải được.}
			\EX{I couldn't \textit{figure out} what had changed.}
			\EX{Analysts \textit{worked out} the capacity scenarios.}
			\CO{figure out how/why/what; figure sth out}
			\end{ExplainCard}

			\begin{ExplainCard}{mass media}[n][B2]
			\EN{Communication outlets that reach large audiences, e.g., TV, radio, newspapers, major websites.}
			\SY{mainstream media; news media}
			\VI{Phương tiện truyền thông đại chúng.}
			\EX{The \textit{mass media} reported on stadium plans.}
			\EX{\textit{News media} shape fan perceptions of clubs.}
			\CO{coverage in the mass media; mass-media campaign}
			\end{ExplainCard}

			\begin{ExplainCard}{rumoured}[adj][C1]
			\EN{Said to be true by many people but not officially confirmed.}
			\SY{alleged; reported; said to be}
			\VI{Đồn rằng; được cho là.}
			\EX{It's \textit{rumoured} the club will renovate.}
			\EX{\textit{Reported} figures remain unverified.}
			\CO{be rumoured to + V; widely/strongly rumoured}
			\end{ExplainCard}

			\begin{ExplainCard}{expand}[v][B2]
			\EN{To increase in size, number, or scope; to make something larger.}
			\SY{enlarge; extend; scale up}
			\VI{Mở rộng; nới quy mô.}
			\EX{They plan to \textit{expand} the seating to 88,000.}
			\EX{Clubs \textit{expand} capacity to meet demand.}
			\CO{expand capacity/operations/facilities; expansion plan}
			\end{ExplainCard}

			\begin{ExplainCard}{it remains to be seen}[idiom][C1]
			\EN{It is uncertain what the result will be; the outcome will only become clear later.}
			\SY{time will tell; yet to be determined}
			\VI{Còn phải chờ xem; chưa biết kết quả.}
			\EX{\textit{It remains to be seen} whether the upgrade happens.}
			\EX{\textit{It remains to be seen} if funding is secured.}
			\CO{It remains to be seen whether/if + clause}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 2.}
	\begin{qa}{Describe a useful website you have visited}
		You should say:\\
		\textbullet\ What the website was\\
		\textbullet\ How you found the address for this website\\
		\textbullet\ What the website contained\\
		\textbullet\ and explain why it was useful to you.

		In this \textbf{fast-changing world}, \textbf{keeping up with} the latest information is a \textbf{must-do}, and I usually \textbf{keep myself informed} by logging onto Facebook. It is a social networking website that allows registered users to create profiles, upload unlimited images and videos, and send messages to people \textbf{intertwined on its virtual platform}. As far as I’m concerned, it is kind of \textbf{the in-thing} in today’s world, with millions or even billions of users on a global scale.

		\textbf{If my memory serves me correctly}, I started using Facebook when I was at high school. At that time, I was in the middle of the \textbf{final examination}. This exam was crucial to me because it would determine whether I was \textbf{eligible} to compete in the \textbf{national examination for the gifted} or not. In order to provide the class with the latest materials, the \textbf{monitor} of my class set up a group on Facebook and sent me an email inviting me to join. I signed up and I’ve been using it ever since.

		To be honest, Facebook is a very useful tool. Thanks to this website, I can \textbf{keep in touch} with friends. All my friends use Facebook \textbf{on a daily basis}, so connecting them is \textbf{a cakewalk}. One of the most significant components of Facebook is the Wall, where we can \textbf{voice our opinions} about \textbf{any} stuffs in our daily life. It is true that Facebook is a \textbf{mighty tool} in storing photos and videos. Another benefit worth mentioning is that it is \textbf{free of charge}.

		As a student who \textbf{was on a shoestring}, I found it fairly convenient to do everything mentioned above to my friends via this platform. Right now, I am \textbf{employing} Facebook as a marketing tool, which helps to reach my potential customers. I think this social networking website has become an \textbf{indispensable} part of everyday life.
		\end{qa}

        \begin{VocabExplain}[Part 2]
			\begin{ExplainCard}{fast-changing world}[adj~phr][B2]
			\EN{A world where situations and technologies evolve rapidly.}
			\SY{rapidly evolving; fast-paced}
			\VI{Thế giới thay đổi chóng mặt.}
			\EX{In a \textit{fast-changing world}, digital skills age quickly.}
			\EX{Policy must adapt to a \textit{fast-changing} economy.}
			\CO{fast-changing market/landscape/industry}
			\end{ExplainCard}

			\begin{ExplainCard}{keep up with}[phr.v][B2]
			\EN{Stay informed about the latest news, trends, or developments.}
			\SY{stay abreast of; follow}
			\VI{Theo kịp, cập nhật.}
			\EX{I \textit{keep up with} campus news on Facebook.}
			\EX{Researchers must \textit{stay abreast of} new findings.}
			\CO{keep up with trends/news/technology}
			\end{ExplainCard}

			\begin{ExplainCard}{must-do}[n/adj][B2]
			\EN{(Something) essential to do or experience.}
			\SY{essential; not-to-be-missed}
			\VI{Việc/phần không thể bỏ qua.}
			\EX{Regular backups are a \textit{must-do} for creators.}
			\EX{The museum’s new wing is a \textit{must-do} stop.}
			\CO{travel/maintenance must-dos; a must-do activity}
			\end{ExplainCard}

			\begin{ExplainCard}{keep oneself informed}[v~phr][B2]
			\EN{Make an effort to obtain and update necessary information.}
			\SY{stay informed; stay updated}
			\VI{Giữ cho mình luôn được cập nhật thông tin.}
			\EX{I \textit{keep myself informed} via verified sources.}
			\EX{Leaders must \textit{stay informed} about policy shifts.}
			\CO{keep yourself informed about/of sth}
			\end{ExplainCard}

			\begin{ExplainCard}{intertwined (on its virtual platform)}[adj][C1]
			\EN{Closely connected or linked together through the same online network.}
			\SY{interconnected; interlinked}
			\VI{Gắn kết/chằng chịt với nhau trên nền tảng trực tuyến.}
			\EX{User communities are \textit{intertwined} across groups.}
			\EX{Personal and professional circles often become \textit{intertwined} online.}
			\CO{intertwined networks/relationships/communities}
			\end{ExplainCard}

			\begin{ExplainCard}{the in-thing}[idiom][B2]
			\EN{Something very fashionable or popular at the moment.}
			\SY{the craze; trending}
			\VI{Mốt thịnh hành hiện nay.}
			\EX{Short-form videos are \textit{the in-thing} with teens.}
			\EX{Back then, blogging was \textit{the in-thing}.}
			\CO{become/remain the in-thing}
			\end{ExplainCard}

			\begin{ExplainCard}{If my memory serves me correctly}[phrase][B2]
			\EN{Used to introduce a statement you believe you remember accurately.}
			\SY{as far as I remember; to the best of my recollection}
			\VI{Nếu tôi nhớ không lầm.}
			\EX{\textit{If my memory serves me correctly}, we joined in 2012.}
			\EX{\textit{To the best of my recollection}, the fee was waived.}
			\CO{If my memory serves (me) right/correctly, + clause}
			\end{ExplainCard}

			\begin{ExplainCard}{final examination}[n][B2]
			\EN{End-of-course or end-of-level exam that determines achievement.}
			\SY{finals; culminating exam}
			\VI{Kỳ thi cuối kỳ/cuối cấp.}
			\EX{She prepared for the \textit{final examination} in June.}
			\EX{Grades hinge on the \textit{finals}.}
			\CO{sit/take/pass the final examination}
			\end{ExplainCard}

			\begin{ExplainCard}{eligible}[adj][B2]
			\EN{Having the right or qualifications to do or receive something.}
			\SY{qualified; entitled}
			\VI{Đủ điều kiện; đủ tiêu chuẩn.}
			\EX{Only top scorers are \textit{eligible} for the team.}
			\EX{Applicants must be \textit{eligible} for funding.}
			\CO{eligible for/to do; eligibility criteria}
			\end{ExplainCard}

			\begin{ExplainCard}{national examination for the gifted}[n~phr][C1]
			\EN{A selective, nationwide exam for high-achieving students.}
			\SY{national talent exam; selective competition}
			\VI{Kỳ thi học sinh giỏi cấp quốc gia.}
			\EX{She trained a year for the \textit{national examination for the gifted}.}
			\EX{Schools nominate candidates for the \textit{national talent} round.}
			\CO{compete in/qualify for the national exam}
			\end{ExplainCard}

			\begin{ExplainCard}{monitor (of my class)}[n][B2]
			\EN{Student elected or appointed to manage class affairs; class representative.}
			\SY{class rep; class leader}
			\VI{Lớp trưởng/cán sự lớp.}
			\EX{The \textit{class monitor} set up the online group.}
			\EX{Ask the \textit{rep} to circulate the schedule.}
			\CO{class monitor/representative; appoint/elect a monitor}
			\end{ExplainCard}

			\begin{ExplainCard}{keep in touch}[idiom][B1]
			\EN{Maintain communication with someone.}
			\SY{stay in contact; stay connected}
			\VI{Giữ liên lạc.}
			\EX{We \textit{keep in touch} through Facebook Messenger.}
			\EX{Alumni \textit{stay in contact} via a private group.}
			\CO{keep/stay in touch with sb}
			\end{ExplainCard}

			\begin{ExplainCard}{on a daily basis}[adv~phr][B1]
			\EN{Every day; happening each day.}
			\SY{daily; every day}
			\VI{Hằng ngày; mỗi ngày.}
			\EX{She posts updates \textit{on a daily basis}.}
			\EX{The tool is used \textit{daily} by marketers.}
			\CO{track/use/report on a daily basis}
			\end{ExplainCard}

			\begin{ExplainCard}{a cakewalk}[idiom][B2]
			\EN{Something very easy to do.}
			\SY{a breeze; a walk in the park}
			\VI{Dễ ợt; quá đơn giản.}
			\EX{Sharing files is \textit{a cakewalk} on that platform.}
			\EX{For her, algebra was \textit{a breeze}.}
			\CO{be/feel like a cakewalk}
			\end{ExplainCard}

			\begin{ExplainCard}{voice (one’s) opinions}[v~collocation][B2]
			\EN{Express views or thoughts openly.}
			\SY{air; express; articulate}
			\VI{Lên tiếng bày tỏ ý kiến.}
			\EX{Users \textit{voice their opinions} on the Wall.}
			\EX{Employees were urged to \textit{voice concerns}.}
			\CO{voice an opinion/concern/idea}
			\end{ExplainCard}

			\begin{ExplainCard}{any (old) stuff}[determiner][B1]
			\EN{Used informally to mean “whatever/whichever,” without limitation.}
			\SY{whatever; whichever}
			\VI{Bất cứ (cái gì).}
			\EX{People post about \textit{any} topic that interests them.}
			\EX{\textit{Any} updates are welcome in the group.}
			\CO{any topic/issue/time/place}
			\end{ExplainCard}

			\begin{ExplainCard}{mighty (tool)}[adj][B2]
			\EN{Very powerful or effective.}
			\SY{powerful; potent}
			\VI{Mạnh mẽ; hiệu quả.}
			\EX{Search is a \textit{mighty tool} for learning.}
			\EX{A \textit{potent} platform for outreach.}
			\CO{mighty engine/ally/tool; a potent tool}
			\end{ExplainCard}

			\begin{ExplainCard}{free of charge}[adv~phr][B2]
			\EN{Without payment; at no cost.}
			\SY{for free; at no cost}
			\VI{Miễn phí.}
			\EX{Storage is \textit{free of charge} up to 15GB.}
			\EX{Students attend workshops \textit{at no cost}.}
			\CO{offer/provide sth free of charge}
			\end{ExplainCard}

			\begin{ExplainCard}{on a shoestring}[idiom][C1]
			\EN{With very little money; on a tight budget.}
			\SY{on a tight budget; cheaply}
			\VI{Với ngân sách eo hẹp.}
			\EX{As a student \textit{on a shoestring}, I used free tools.}
			\EX{They traveled \textit{on a shoestring} across Asia.}
			\CO{run/operate/travel on a shoestring}
			\end{ExplainCard}

			\begin{ExplainCard}{employ (a tool)}[v][B2]
			\EN{Use something for a particular purpose or effect.}
			\SY{use; leverage; utilize}
			\VI{Sử dụng/vận dụng (công cụ).}
			\EX{We \textit{employ} Facebook for outreach.}
			\EX{Teachers \textit{utilize} forums to flip classes.}
			\CO{employ a method/strategy/platform}
			\end{ExplainCard}

			\begin{ExplainCard}{indispensable}[adj][C1]
			\EN{Absolutely necessary; cannot be done without.}
			\SY{essential; crucial; vital}
			\VI{Thiết yếu; không thể thiếu.}
			\EX{Messaging apps are \textit{indispensable} to remote teams.}
			\EX{Data literacy is \textit{indispensable} in modern jobs.}
			\CO{become/prove indispensable; an indispensable tool/role}
			\end{ExplainCard}
        \end{VocabExplain}

    \noindent
    \textbf{Part 3.}
	\begin{qa}{What effect has the Internet had on the way people generally communicate with each other?}
	Personally, the \textbf{booming} Internet industry is \textbf{an asset} to human communication as it is \textbf{conducive to} \textbf{distance communication}. Digital technology lets people send \textbf{multimedia messages} and videos within seconds. However, a downside is reduced \textbf{physical interaction}: the more time people invest in \textbf{virtual relationships}, the less time they spend on face-to-face conversation. In short, the convenience of e-communication sometimes comes at the expense of in-person talk.
	\end{qa}

	\begin{qa}{Why do you think the Internet is being used more and more for communication?}
	The \textbf{ubiquity} of the Internet can be \textbf{ascribed to} several \textbf{underlying} reasons. Beyond basic chat, users enjoy apps like digital maps to \textbf{navigate} routes or \textbf{keep themselves posted} about weather. More importantly, the Internet \textbf{grants} users access to vast stores of information worldwide, which \textbf{paves the way} for them to expand their knowledge.
	\end{qa}

	\begin{qa}{How reliable do you think information from the Internet is? What about news on the Internet?}
	Admittedly, the Internet is a \textbf{reservoir} of information people can \textbf{tap into} to \textbf{broaden their horizons}. Yet some sources are \textbf{conflicting} or inaccurate because they are not censored. The same applies to online news, which can be \textbf{distorted} to create a \textbf{sensation} and increase \textbf{viewership}.
	\end{qa}

	\begin{qa}{Why do some people use the Internet for shopping? Why doesn’t everyone use it this way?}
	Digital shopping has become \textbf{ubiquitous} thanks to the considerable \textbf{merits} it offers. Compared with in-store buying, it saves travel time without sacrificing \textbf{an array of} choices—shoppers can compare hundreds of items before deciding. That said, concerns about \textbf{internet frauds} and \textbf{online scams} (e.g., \textbf{counterfeit goods}, \textbf{bogus websites}, even credit-card hacking) have \textbf{detrimental} impacts on trust. Not everyone—especially pensioners who aren’t \textbf{techies}—appreciates the benefits.
	\end{qa}

	\begin{qa}{What kinds of things are easy to buy and sell online? Examples?}
	\textbf{Instinctively}, I don’t have a \textbf{knack for} business, but clothes are ideal: although they \textbf{come in all shapes and sizes}, customers can still pick favorites from images. Electronics are a \textbf{child’s play} to sell if prices are \textbf{marked down} and items remain in \textbf{mint condition}. Some goods—like medicines—should be sold only with a \textbf{prescription}.
	\end{qa}

	\begin{qa}{Will shopping on the Internet be more or less popular in the future? Why?}
	In my view, online shopping is \textbf{making a splash} and will keep rising. More customers will \textbf{opt for} it due to lower \textbf{expenses} (special offers, free shipping). Reviews are a key \textbf{contributing factor} helping buyers \textbf{distinguish between} fake and genuine products, boosting satisfaction. Being able to browse thousands of items—trendy or \textbf{one-of-a-kind}, common or rare—at midnight proves that e-commerce is \textbf{head and shoulders above} the \textbf{conventional} method.
	\end{qa}

        \begin{VocabExplain}[Part 3]
			\begin{ExplainCard}{booming}[adj][C1]
			\EN{Growing very quickly and successfully.}
			\SY{thriving; flourishing; surging}
			\VI{Bùng nổ, tăng trưởng mạnh.}
			\EX{The \textit{booming} Internet industry has reshaped media.}
			\EX{A \textit{booming} e-commerce market attracts investors.}
			\CO{booming industry/market/sector; a booming demand}
			\end{ExplainCard}

			\begin{ExplainCard}{an asset (to)}[n][B2]
			\EN{A useful or valuable person or thing.}
			\SY{advantage; strength; boon}
			\VI{Tài sản/lợi thế; điều có ích.}
			\EX{Good writing is \textit{an asset to} communication online.}
			\EX{Multilingual staff are real \textit{assets}.}
			\CO{be/prove an asset to/for; valuable asset}
			\end{ExplainCard}

			\begin{ExplainCard}{conducive to}[adj~phr][C1]
			\EN{Making a certain situation or outcome likely or possible.}
			\SY{favourable to; helpful to}
			\VI{Tạo điều kiện/thuận lợi cho.}
			\EX{Asynchronous tools are \textit{conducive to} remote work.}
			\EX{Quiet rooms are \textit{conducive to} deep focus.}
			\CO{conducive to learning/productivity/collaboration}
			\end{ExplainCard}

			\begin{ExplainCard}{distance communication}[n~phr][B2]
			\EN{Exchanging information when participants are in different places.}
			\SY{remote communication; long-distance communication}
			\VI{Giao tiếp từ xa.}
			\EX{Video calls enable \textit{distance communication} at scale.}
			\EX{Satellites expanded \textit{long-distance} links.}
			\CO{enable/support distance communication}
			\end{ExplainCard}

			\begin{ExplainCard}{multimedia message}[n][B2]
			\EN{A message containing text plus images, audio, or video.}
			\SY{rich media message}
			\VI{Tin nhắn đa phương tiện.}
			\EX{Apps send \textit{multimedia messages} in seconds.}
			\EX{Campaigns rely on \textit{rich media} for impact.}
			\CO{send/share a multimedia message; MMS content}
			\end{ExplainCard}

			\begin{ExplainCard}{physical interaction}[n~phr][B2]
			\EN{Face-to-face contact between people.}
			\SY{in-person interaction; direct contact}
			\VI{Tương tác trực tiếp.}
			\EX{More screen time may reduce \textit{physical interaction}.}
			\EX{Workshops restore \textit{in-person} connections.}
			\CO{increase/reduce physical interaction}
			\end{ExplainCard}

			\begin{ExplainCard}{virtual relationship}[n~phr][B2]
			\EN{A relationship maintained mainly through the Internet.}
			\SY{online relationship; digital connection}
			\VI{Mối quan hệ trực tuyến.}
			\EX{\textit{Virtual relationships} help expats stay connected.}
			\EX{Overreliance on \textit{online ties} can feel isolating.}
			\CO{build/maintain virtual relationships}
			\end{ExplainCard}

			\begin{ExplainCard}{ubiquity}[n][C1]
			\EN{The state of being present everywhere or very common.}
			\SY{pervasiveness; omnipresence}
			\VI{Sự phổ biến khắp nơi.}
			\EX{The \textit{ubiquity} of smartphones changes news habits.}
			\EX{QR codes reached \textit{ubiquity} during the pandemic.}
			\CO{achieve/reach ubiquity; the ubiquity of X}
			\end{ExplainCard}

			\begin{ExplainCard}{ascribe (sth) to}[v][C1]
			\EN{To attribute something to a cause or source.}
			\SY{attribute; put down to}
			\VI{Quy cho; gán cho.}
			\EX{Success is \textit{ascribed to} network effects.}
			\EX{Analysts \textit{ascribed} the outage to a software bug.}
			\CO{ascribe growth/success/failure to}
			\end{ExplainCard}

			\begin{ExplainCard}{underlying}[adj][C1]
			\EN{Basic but not immediately obvious; forming the real cause.}
			\SY{fundamental; root; latent}
			\VI{Nền tảng, ẩn bên dưới.}
			\EX{\textit{Underlying} factors include trust and usability.}
			\EX{Fix the \textit{underlying} cause, not the symptom.}
			\CO{underlying cause/assumption/trend}
			\end{ExplainCard}

			\begin{ExplainCard}{keep (oneself) posted}[v~phr][B2]
			\EN{Stay informed by receiving regular updates.}
			\SY{stay updated; be kept informed}
			\VI{Theo dõi/được cập nhật thường xuyên.}
			\EX{I \textit{keep myself posted} via weather apps.}
			\EX{Please \textit{keep me posted} on delivery.}
			\CO{keep sb posted on/about}
			\end{ExplainCard}

			\begin{ExplainCard}{grant}[v][B2]
			\EN{To give or allow (access/permission) officially.}
			\SY{give; confer; accord}
			\VI{Cấp/cho phép.}
			\EX{The platform \textit{grants} users free cloud storage.}
			\EX{Researchers were \textit{granted} access to the dataset.}
			\CO{grant access/permission/rights}
			\end{ExplainCard}

			\begin{ExplainCard}{pave the way (for)}[idiom][C1]
			\EN{Create the conditions that make something possible.}
			\SY{open the door to; lay the groundwork for}
			\VI{Mở đường, tạo tiền đề.}
			\EX{Open data \textit{paves the way for} new services.}
			\EX{Standards \textit{paved the way} for interoperability.}
			\CO{pave the way for reform/innovation}
			\end{ExplainCard}

			\begin{ExplainCard}{reservoir (of information)}[n][C1]
			\EN{A large supply or store of something useful.}
			\SY{repository; storehouse; trove}
			\VI{Kho, nguồn dự trữ (thông tin).}
			\EX{The web is a \textit{reservoir of information}.}
			\EX{Archives form a vital \textit{repository} for scholars.}
			\CO{a vast/valuable reservoir of data/knowledge}
			\end{ExplainCard}

			\begin{ExplainCard}{tap into}[phr.v][C1]
			\EN{To make use of a resource or supply that already exists.}
			\SY{draw on; leverage}
			\VI{Khai thác, tận dụng.}
			\EX{Learners \textit{tap into} open courses worldwide.}
			\EX{Brands \textit{tap into} user communities for feedback.}
			\CO{tap into markets/networks/resources}
			\end{ExplainCard}

			\begin{ExplainCard}{broaden (one’s) horizon(s)}[v~phr][B2]
			\EN{Increase the range of one’s knowledge or experience.}
			\SY{expand outlook; widen perspective}
			\VI{Mở rộng tầm hiểu biết.}
			\EX{Reading foreign media \textit{broadens horizons}.}
			\EX{Travel \textit{broadened} her perspective on design.}
			\CO{broaden cultural/academic horizons}
			\end{ExplainCard}

			\begin{ExplainCard}{conflicting}[adj][B2]
			\EN{Incompatible; expressing different or opposing views.}
			\SY{contradictory; inconsistent}
			\VI{Mâu thuẫn, trái ngược.}
			\EX{\textit{Conflicting} reports made fact-checking vital.}
			\EX{Data from two sources were \textit{inconsistent}.}
			\CO{conflicting reports/interests/evidence}
			\end{ExplainCard}

			\begin{ExplainCard}{distort}[v][C1]
			\EN{To change the truth or original shape so it is no longer accurate.}
			\SY{twist; skew; misrepresent}
			\VI{Bóp méo, xuyên tạc.}
			\EX{Headlines can \textit{distort} nuanced findings.}
			\EX{Compression \textit{distorted} the image quality.}
			\CO{distort facts/data/perception}
			\end{ExplainCard}

			\begin{ExplainCard}{sensation}[n][C1]
			\EN{A lot of public excitement or interest; a highly talked-about event.}
			\SY{furore; buzz; hype}
			\VI{Hiện tượng gây sốt; cơn sốt truyền thông.}
			\EX{Clickbait aims to create a \textit{sensation}.}
			\EX{The app became an overnight \textit{sensation}.}
			\CO{cause/create a sensation; media sensation}
			\end{ExplainCard}

			\begin{ExplainCard}{viewership}[n][C1]
			\EN{The number or group of people who watch a programme/content.}
			\SY{audience size; ratings}
			\VI{Lượng người xem.}
			\EX{Controversial takes can boost \textit{viewership}.}
			\EX{Live streams saw record \textit{viewership} figures.}
			\CO{high/record/declining viewership}
			\end{ExplainCard}

			\begin{ExplainCard}{merit (of sth)}[n][C1]
			\EN{A good feature that makes something worth having or doing.}
			\SY{advantage; benefit}
			\VI{Ưu điểm, giá trị.}
			\EX{A key \textit{merit} of online shopping is convenience.}
			\EX{Judge proposals on their \textit{merits}.}
			\CO{assess/recognise the merits of}
			\end{ExplainCard}

			\begin{ExplainCard}{an array of}[quant~phr][C1]
			\EN{A wide and impressive range of things.}
			\SY{a host of; a wealth of}
			\VI{Một loạt/đa dạng.}
			\EX{Sites offer \textit{an array of} payment options.}
			\EX{We tested \textit{a host of} UX variants.}
			\CO{an array of choices/features/services}
			\end{ExplainCard}

			\begin{ExplainCard}{internet fraud / online scam}[n][C1]
			\EN{Deceptive schemes conducted online to steal money or data.}
			\SY{cyber-fraud; phishing; swindle}
			\VI{Gian lận/lừa đảo trên mạng.}
			\EX{Report suspected \textit{online scams} immediately.}
			\EX{Banks warn customers about \textit{internet fraud}.}
			\CO{fall for/avoid/report an online scam; fraud ring}
			\end{ExplainCard}

			\begin{ExplainCard}{counterfeit goods}[n~phr][C1]
			\EN{Fake products made to imitate real brands.}
			\SY{fake merchandise; knock-offs}
			\VI{Hàng giả/nhái.}
			\EX{Marketplaces combat \textit{counterfeit goods}.}
			\EX{Labels help detect \textit{knock-offs}.}
			\CO{sell/seize counterfeit goods; counterfeit market}
			\end{ExplainCard}

			\begin{ExplainCard}{bogus website}[n~phr][C1]
			\EN{A fake site designed to deceive users.}
			\SY{fraudulent site; spoof site}
			\VI{Trang web giả mạo/lừa đảo.}
			\EX{Phishing emails link to \textit{bogus websites}.}
			\EX{Check the URL to avoid \textit{spoof} pages.}
			\CO{create/shut down bogus websites}
			\end{ExplainCard}

			\begin{ExplainCard}{detrimental}[adj][C1]
			\EN{Causing harm or damage.}
			\SY{harmful; adverse; damaging}
			\VI{Gây hại, bất lợi.}
			\EX{Leaks can be \textit{detrimental} to user trust.}
			\EX{Excessive ads have \textit{adverse} effects on UX.}
			\CO{detrimental effect/impact/consequence}
			\end{ExplainCard}

			\begin{ExplainCard}{techie}[n][B2]
			\EN{A person who is very knowledgeable about technology.}
			\SY{tech enthusiast; geek}
			\VI{Dân rành công nghệ.}
			\EX{Not all retirees are \textit{techies}.}
			\EX{\textit{Techies} often beta-test new apps.}
			\CO{self-confessed techie; non-techie users}
			\end{ExplainCard}

			\begin{ExplainCard}{instinctively}[adv][B2]
			\EN{In a way that is based on natural feelings rather than thought.}
			\SY{intuitively; by instinct}
			\VI{Theo bản năng.}
			\EX{She \textit{instinctively} distrusted the offer.}
			\EX{Designers \textit{intuitively} spot friction points.}
			\CO{react/feel/know instinctively}
			\end{ExplainCard}

			\begin{ExplainCard}{a knack for}[n~phr][B2]
			\EN{A natural skill or talent for doing something.}
			\SY{flair; gift; aptitude}
			\VI{Năng khiếu; bí quyết.}
			\EX{He has \textit{a knack for} writing catchy copy.}
			\EX{Sellers with \textit{a flair} for styling sell faster.}
			\CO{have/develop a knack for sth}
			\end{ExplainCard}

			\begin{ExplainCard}{come in all shapes and sizes}[idiom][B2]
			\EN{Exist in many different forms or varieties.}
			\SY{be of many kinds; vary widely}
			\VI{Đa dạng muôn hình vạn trạng.}
			\EX{Online products \textit{come in all shapes and sizes}.}
			\EX{Communities \textit{come in all shapes and sizes}.}
			\CO{items/options/users come in all shapes and sizes}
			\end{ExplainCard}

			\begin{ExplainCard}{child’s play}[idiom][B2]
			\EN{Something very easy to do.}
			\SY{a breeze; no-brainer}
			\VI{Quá dễ, trò trẻ con.}
			\EX{Listing items is \textit{child’s play} on this app.}
			\EX{For experts, the fix was \textit{a breeze}.}
			\CO{be/seem like child’s play}
			\end{ExplainCard}

			\begin{ExplainCard}{mark (prices) down}[phr.v][B2]
			\EN{Reduce the price of goods.}
			\SY{discount; cut; slash}
			\VI{Giảm giá, hạ giá.}
			\EX{Electronics were \textit{marked down} by 30\%.}
			\EX{Retailers \textit{slash} prices during clearance.}
			\CO{mark down by/to; markdown sale}
			\end{ExplainCard}

			\begin{ExplainCard}{mint condition}[n~phr][B2]
			\EN{Perfect, like new condition.}
			\SY{pristine; as-new}
			\VI{Tình trạng như mới.}
			\EX{The phone was in \textit{mint condition}.}
			\EX{Collectors pay more for \textit{pristine} items.}
			\CO{keep/restore to mint condition}
			\end{ExplainCard}

			\begin{ExplainCard}{prescription}[n][B2]
			\EN{A doctor’s written instruction for a medicine or treatment.}
			\SY{script; medical order}
			\VI{Đơn thuốc.}
			\EX{Some drugs require a \textit{prescription}.}
			\EX{Upload a \textit{script} to order online.}
			\CO{fill/write a prescription; prescription-only medicine}
			\end{ExplainCard}

			\begin{ExplainCard}{make a splash}[idiom][C1]
			\EN{Attract a lot of attention and interest.}
			\SY{cause a stir; create buzz}
			\VI{Gây tiếng vang; nổi bật.}
			\EX{The new marketplace \textit{made a splash} with free shipping.}
			\EX{A bold redesign can \textit{cause a stir}.}
			\CO{make a splash in/with}
			\end{ExplainCard}

			\begin{ExplainCard}{opt for}[phr.v][B2]
			\EN{Choose one thing rather than another.}
			\SY{choose; go for; select}
			\VI{Chọn, thiên về.}
			\EX{More buyers \textit{opt for} online checkout.}
			\EX{We \textit{opted for} curbside pickup.}
			\CO{opt for A over B; opt for convenience/speed}
			\end{ExplainCard}

			\begin{ExplainCard}{expenses}[n~pl][B2]
			\EN{Money spent to buy or do something.}
			\SY{costs; outlays}
			\VI{Chi phí; khoản chi.}
			\EX{Online promotions lower \textit{expenses} for shoppers.}
			\EX{Track recurring \textit{expenses} monthly.}
			\CO{cut/offset/claim expenses; living/operating expenses}
			\end{ExplainCard}

			\begin{ExplainCard}{contributing factor}[n~phr][B2]
			\EN{One of the causes that helps produce a result.}
			\SY{driver; determinant; cause}
			\VI{Yếu tố góp phần.}
			\EX{Reviews are a key \textit{contributing factor} to sales.}
			\EX{Trust was the main \textit{driver} of adoption.}
			\CO{a major/significant contributing factor}
			\end{ExplainCard}

			\begin{ExplainCard}{distinguish between}[v~phr][B2]
			\EN{Recognise or show the difference between things.}
			\SY{differentiate; tell apart}
			\VI{Phân biệt giữa (các thứ).}
			\EX{Guides help buyers \textit{distinguish between} fakes and originals.}
			\EX{Hard to \textit{tell apart} identical listings.}
			\CO{distinguish between A and B; clearly distinguish}
			\end{ExplainCard}

			\begin{ExplainCard}{one-of-a-kind}[adj][B2]
			\EN{Unique; unlike anything else.}
			\SY{unique; singular}
			\VI{Độc nhất vô nhị.}
			\EX{Collectors hunt for \textit{one-of-a-kind} pieces.}
			\EX{A \textit{unique} artisan bag sold out fast.}
			\CO{a one-of-a-kind product/design/gift}
			\end{ExplainCard}

			\begin{ExplainCard}{head and shoulders above}[idiom][C1]
			\EN{Much better than others of the same kind.}
			\SY{far superior to; outclass}
			\VI{Vượt trội hơn hẳn.}
			\EX{Customer support is \textit{head and shoulders above} rivals.}
			\EX{This UX is \textit{far superior} to the old site.}
			\CO{be head and shoulders above the competition}
			\end{ExplainCard}

			\begin{ExplainCard}{conventional}[adj][B2]
			\EN{Usual or traditional; not new or different.}
			\SY{traditional; standard; orthodox}
			\VI{Thông thường, truyền thống.}
			\EX{Online buying outpaces \textit{conventional} retail.}
			\EX{\textit{Conventional} methods still work for basics.}
			\CO{conventional retail/approach/wisdom}
			\end{ExplainCard}
        \end{VocabExplain}

    \begin{VocabHighlights}
		\VH{fanatic}{(n) a person who is extremely interested in something, to a degree that some people find unreasonable}{(danh từ) người hâm mộ quá cuồng tín}
		\VH{a dream come true}{(n) something you have wanted very much for a long time that has now happened}{(danh từ) giấc mơ đã thành sự thực}
		\VH{there is fat chance}{(phrase) there is no chance of that happening}{(cụm từ) khó mà có được}
		\VH{goosebump}{(n) small raised areas that appear on the skin because of cold, fear, or excitement}{(danh từ) sự nổi da gà}
		\VH{must-see place}{(n) a place considered to be essential to visit or see}{(danh từ) nơi phải đến}
		\VH{to embark on}{(v) to start something new or important}{(động từ) bắt đầu làm gì mới, quan trọng}
		\VH{on a yearly basis}{(adv) annually}{(trạng từ) hàng năm}
		\VH{trophy}{(n) a prize, such as a gold or silver cup, that is given to the winner of a competition or race, and often returned after a year to be given to the winner of the competition in the following year}{(danh từ) danh hiệu}
		\VH{to marvel at}{(v) to show or experience great surprise or admiration}{(động từ) trầm trồ trước}
		\VH{to figure out}{(v) to solve, to understand}{(động từ) giải quyết, hiểu ra}
		\VH{it remains to be seen}{(phrase) used to express the notion that something is not yet known or certain}{(cụm từ) còn cần xem xét}
		\VH{fast-changing world}{(phrase) marked by continuous change or effective action}{(cụm từ) thế giới thay đổi nhanh chóng, không ngừng}
		\VH{to keep up with}{(phr.v) to continue to do or pay something}{(cụm động từ) theo kịp}
		\VH{must-do}{(n) something that is so good, you must do it}{(danh từ) điều phải làm}
		\VH{to keep oneself informed}{(phrase) to receive regularly of the latest news}{(cụm từ) giúp bản thân cập nhật thông tin}
		\VH{to be intertwined on its virtual platform}{(phrase) be blended into a thing}{(cụm từ) được kết hợp vào một môi trường tương tác ảo}
		\VH{the in-thing}{(idiom) something popular at the moment}{(thành ngữ) một thứ phổ biến, ưa chuộng}
		\VH{a cakewalk}{(idiom) something that is very easy to do}{(thành ngữ) dễ như ăn kẹo}
		\VH{voice our opinions}{(phrase) you say what you think or feel}{(cụm từ) nói lên ý kiến cá nhân}
		\VH{mighty}{(adj) very large, powerful or important}{(tính từ) hùng mạnh}
		\VH{free of charge}{(phrase) without having to pay}{(cụm từ) miễn phí}
		\VH{to be on a shoestring}{(adj) very small amount of money}{(tính từ) ngân sách hạn hẹp}
		\VH{employ}{(v) use something}{(động từ) sử dụng}
		\VH{indispensable}{(adj) necessary}{(tính từ) không thể thiếu}
		\VH{booming}{(adj) having a period of great prosperity or rapid economic growth}{(tính từ) sự bùng nổ, thịnh vượng}
		\VH{an asset}{(n) a person or thing that is valuable or useful to somebody/something}{(danh từ) tài sản, có giá trị}
		\VH{conducive}{(adj) making it easy, possible or likely for something to happen}{(tính từ) có ích, có giá trị}
		\VH{distance communication}{(phrase) to communicate from distance}{(cụm từ) giao tiếp từ xa}
		\VH{multimedia messages}{(n) the use of sound, pictures and film in addition to text message on a screen}{(danh từ) tin nhắn đa phương tiện}
		\VH{physical interaction}{(phrase) face-to-face interaction}{(cụm từ) tương tác trực tiếp}
		\VH{to be ascribed}{(p2) to consider something to be caused, created, or owned by someone or something}{(phần từ 2) được gán cho; quy cho}
		\VH{underlying}{(adj) important in a situation but not always easily noticed or stated clearly}{(tính từ) căn bản, cơ bản}
		\VH{to grant}{(v) to agree or give somebody what they ask for, especially formal or legal permission to do something}{(động từ) cho phép, tạo điều kiện}
		\VH{to pave the way for}{(phrase) it makes the other thing possible}{(cụm từ) tạo điều kiện}
		\VH{a reservoir}{(n) a large amount of something that is available to be used}{(danh từ) kho tàng, kho dự trữ}
		\VH{broaden their horizon}{(phrase) to increase the range of things that someone knows about or has experienced}{(cụm từ) mở mang kiến thức}
		\VH{conflicting}{(adj) incompatible or at variance; contradictory}{(tính từ) đối lập; mâu thuẫn}
		\VH{distorted}{(p2) to twist or change facts, ideas, etc. so that they are no longer correct or true}{(phần từ 2) bị bóp méo}
		\VH{sensation}{(n) very great surprise, excitement, or interest among a lot of people}{(danh từ) sự giật gân}
		\VH{viewership}{(n) the number or type of people who watch a particular television programme or television channel}{(danh từ) tỉ lệ người xem chương trình}
		\VH{ubiquitous}{(adj) seeming to be everywhere or in several places at the same time; very common}{(tính từ) có mặt ở khắp nơi; đại trà; phổ biến}
		\VH{merits}{(n) the quality of being good and of deserving praise, reward or admiration}{(danh từ) ưu điểm}
		\VH{an array of}{(n) a group or collection of things or people, often one that is large or impressive}{(danh từ) một loạt}
		\VH{internet frauds}{(phrase) the crime of cheating somebody in order to get money or goods illegally on internet}{(cụm từ) lừa đảo trên internet}
		\VH{online scams}{(phrase) a clever and dishonest plan for making money online}{(cụm từ) lừa đảo trực tuyến}
		\VH{instinctively}{(adv) by using instinct rather than thought or training}{(trạng từ) dựa trên bản năng}
		\VH{a knack for}{(phrase) a special skill or ability that you have naturally or can learn}{(cụm từ) sở trường; tài năng}
		\VH{to come in all shapes and sizes}{(idiom) various and diversified}{(thành ngữ) đa dạng, phong phú}
		\VH{prescription}{(n) an official piece of paper on which a doctor writes the type of medicine you should have, and which enables you to get it from a chemist’s shop/drugstore}{(danh từ) đơn thuốc}
		\VH{to make a splash}{(phrase) attract a great deal of attention}{(cụm từ) thu hút nhiều mối quan tâm}
		\VH{expenses}{(n) the money that you spend on something}{(danh từ) chi phí}
		\VH{to opt for}{(v) to choose to take or not to take a particular course of action}{(động từ) lựa chọn}
		\VH{to distinguish}{(v) to recognize the difference between two people or things}{(động từ) phân biệt}
		\VH{to be head and shoulders above}{(idiom) a lot better than others}{(thành ngữ) vượt trội hẳn}
	\end{VocabHighlights}

    \end{test}
\end{glossarymc}